### 2021-05-08 docs/manuscript.tex
add files for manuscript

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  jou]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Increased perceptions of autonomy through choice fail to enhance motor skill retention},
  pdfauthor={Laura St.~Germain1, Allison Williams1, Noura Balbaa1, Andrew Poskus1, Olena Leshchyshen1, Keith R. Lohse2, \& Michael J. Carter1},
  pdflang={en-EN},
  pdfkeywords={Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Autonomy-support not beneficial for learning}
\keywords{Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing\newline\indent Word count: X}
\usepackage{dblfloatfix}

\usepackage{csquotes}
\raggedbottom
\leftheader{St. Germain et al. 2021}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Increased perceptions of autonomy through choice fail to enhance motor skill retention}
\author{Laura St.~Germain\textsuperscript{1}, Allison Williams\textsuperscript{1}, Noura Balbaa\textsuperscript{1}, Andrew Poskus\textsuperscript{1}, Olena Leshchyshen\textsuperscript{1}, Keith R. Lohse\textsuperscript{2}, \& Michael J. Carter\textsuperscript{1}}
\date{}

\authornote{

\addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}

We have outlined author contributions using CRediT (Contributor Roles Taxonomy - \url{https://casrai.org/credit/}).

The authors made the following contributions. Laura St.~Germain: Conceptualization, Data curation, Formal analysis, Investigation - Performed the experiment, Methodology, Project administration, Software - Task Programming, Validation, Visualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Allison Williams: Investigation - Performed the experiment, Writing - Original Draft Preparation, Writing - Review \& Editing; Noura Balbaa: Investigation - Performed the experiment, Writing - Original Draft Preparation, Writing - Review \& Editing; Andrew Poskus: Investigation - Performed the experiment, Writing - Review \& Editing; Olena Leshchyshen: Investigation - Performed the experiment, Writing - Review \& Editing; Keith R. Lohse: Conceptualization, Data curation, Formal analysis, Methodology, Validation, Writing - Original Draft Preparation, Writing - Review \& Editing; Michael J. Carter: Conceptualization, Data curation, Formal analysis, Funding acquisition, Methodology, Project administration, Resources, Software - Task Programming, Supervision, Validation, Visualization, Writing - Original Draft Preparation, Writing - Review \& Editing.

Correspondence concerning this article should be addressed to Michael J. Carter, 1280 Main Street West, Ivor Wynne Centre Room 203, McMaster University, Hamilton ON Canada, L8S 4K1. E-mail: \href{mailto:michaelcarter@mcmaster.ca}{\nolinkurl{michaelcarter@mcmaster.ca}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Kinesiology, McMaster University\\\textsuperscript{2} Program in Physical Therapy, Washington University School of Medicine in Saint Louis}

\abstract{
There has been growing research interest in the effects that motivation plays in motor learning, and specifically how different manipulations that affect autonomy, perceptions of competence, and social relatedness may directly benefit the learning process. In the present study, we present a well-powered (80\%, N = 150) pre-registered manipulation of autonomy support by providing learners with choice during the practice of a speed cup-stacking skill. One group was given control over when a video demonstration was provided and the speed with which the demonstration was played. A yoked control group received an identical schedule of the demonstrations, but no choice (as their schedule was matched to a participant with choice). Critically, we also address a gap in the literature by adding a yoked control group who was explicitly told that they were being denied choice and that their schedule was chosen by another participant. (In the traditional yoked group, participants are merely told the schedule is determined in advance.) We found no statistically significant differences between groups in their learning of the cup-stacking skill, despite finding evidence that providing choice increased perceived autonomy (internally validating the manipulation). The two-one-side-test procedure further showed that although the groups were not statistically equivalent, the effect size is likely too small to practically study the effects of autonomy-support through choice in most motor learning labs. The current study not only adds to a growing body of research that questions the direct causal role that autonomy-support has on learning, but also the robustness of the so-called self-controlled learning advantage.
}

\begin{document}
\maketitle

A popular recommendation in recent years for creating an effective environment for motor skill learning has been to allow the learner to take control over an element of their practice that is traditionally controlled by a coach, therapist, or teacher (Sanli et al., 2013; Ste-Marie et al., 2019). This recommendation is based on the consistent finding that participants in a self-controlled (i.e., choice) group perform with higher proficiency compared to participants in a yoked (i.e., control) group on delayed retention and/or transfer tests. Participants in the yoked group do not experience the same choice opportunity provided to those in the self-controlled group. Instead, they are linked to a self-controlled participant and experience this participant's self-selected practice schedule. This so-called self-controlled learning advantage has been shown when participants are given the opportunity to schedule task difficulty \emph{()}, the order that multiple tasks are practiced \emph{()}, the frequency of watching a modeled demonstration \emph{()}, and when to receive augmented feedback \emph{()}.

Over the years, this manipulation has been described using a variety of names \emph{()}, but more recently it has been subsumed by autonomy-support. In fact, autonomy-support is considered such a robust learning variable that it is one of three key pillars in the recently proposed ``OPTIMAL'' theory of motor learning \emph{()}. Wulf and Lewthwaite argued that providing learners with opportunities for choice---considered an autonomy-supportive practice manipulation---can facilitate motor performance and learning by enhancing learner's expectancies for success, and by allowing the learner to maintain their attentional focus on the task by reducing the need for self-regulatory activity \emph{()}. In other words, these psychological and attentional benefits, and concomitant increases in performance and learning are a by-product of experiencing choice opportunities during practice. Overall, autonomy-support is seen as a means to efficient goal-action coupling \emph{()} and also links the ``OPTIMAL'' theory with Self-Determination theory \emph{()}.

Despite its prominent role within the ``OPTIMAL'' theory of motor learning, there are numerous reasons to doubt the importance of autonomy-support through the provision of choice during practice. First, if the benefits are the result of having opportunities for choice then learning differences should not emerge between different self-controlled groups. However, in experiments where different groups of participants have choice over their feedback schedule, such learning differences have been found when this choice is made after rather than before a performance attempt \emph{()}, when different criteria for success are provided to participants \emph{()}, and when the absolute number of feedback choice opportunities are limited compared to unlimited at the outset of practice \emph{()}. Second, there has been little-to-no support for the notion that practicing in a self-controlled group is perceived as more autonomy-supportive than being in a yoked group. Ste-Marie and colleagues \emph{()}, for example, had participants in the self-controlled and yoked groups complete the perceived choice subscale of the Intrinsic Motivation Inventory and failed to find the expected effect of higher self-reported scores during practice in the self-controlled group. Similar findings have been reported by others \emph{()}; however, McKay \& Ste-Marie \emph{()} recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group. This increased perceived autonomy-support did not, however, translate into enhanced learning compared to the yoked group. Although the available literature does not provide substantial evidence that self-controlled practice is autonomy-supportive, this does not necessarily mean such a manipulation is not autonomy-supportive \emph{()}. For instance, this effect may in fact be quite small and require much larger sample sizes to detect \emph{()} than those commonly used in motor learning experiments \emph{()}.

There are at least two other methodological issues that warrant consideration. The first of these is that in self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component (e.g., feedback or when to watch a modeled demonstration) of their practice and participants in the yoked group are not given choice over this component. However, within the context of practice itself there are many other opportunities for choice that participants may explore, independent of their assigned group. Target-based tasks such as basketball free throws or bean-bag tossing are a popular choice in motor learning experiments and have been used in self-controlled learning experiments \emph{()}. While a participant in the yoked group may not be permitted choice over their feedback schedule (or some other practice variable) with such tasks, this does not preclude them from being able to experience choice opportunities---and thus experience autonomy-support---when trying different throwing techniques, speeds, or release points. Thus, labeling yoked groups as being devoid of choice opportunities may be a misnomer. The other consideration relates to the instructions that are provided to participants in the yoked group. In the context of feedback\footnote{While feedback is used in this example, this issue surrounding instructions is also relevant to other practice variables commonly used in self-controlled learning experiments.}, these participants are typically informed that during practice they may or may not receive feedback after a given trial \emph{()}. This means that participants in yoked groups are not even aware that they have been denied an opportunity for choice, nor that their feedback schedule was created by another participant who was given choice over when feedback was or was not provided. Either of these in isolation, or both simultaneously could contribute to the consistent finding that participants in self-controlled and yoked groups report similar perceived autonomy scores when asked about their opportunities for choices with respect to the motor task \emph{()} or about their practice environment in general \emph{()}.

Here we investigated the effects of making participants in a yoked group explicitly aware of not only being denied opportunities for choice over their frequency of watching and the playback speed of video demonstrations, but also that the schedule they would experience during practice was created by another participant in the experiment. The addition of this novel yoked group allowed us to address one of the previously identified methodological limitations regarding experimental group instructions of previous self-controlled research. We compared the performance of this explicit yoked group with traditional self-controlled and yoked groups on a speed cup-stacking task in practice and in a delayed retention test.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study \emph{()}. The experimental design and analyses were preregistered using AsPredicted.org and is available here: \textbf{ADD URL}.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-sanli2013}{}%
Sanli, E. A., Patterson, J. T., Bray, S. R., \& Lee, T. D. (2013). Understanding self-controlled motor learning protocols through the self-determination theory. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00611}

\leavevmode\hypertarget{ref-ste-marie2019}{}%
Ste-Marie, D. M., Carter, M. J., \& Yantha, Z. D. (2019). \emph{Self-controlled learning: Current findings, theoretical perspectives, and future directions} (3rd ed.). Routledge.

\end{CSLReferences}

\endgroup

\end{document}

### 2021-05-08 docs/manuscript.Rmd
add files for manuscript

---
title             : "Increased perceptions of autonomy through choice fail to enhance motor skill retention"
shorttitle        : "Autonomy-support not beneficial for learning"

author: 
  - name          : "Laura St. Germain"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation - Performed the experiment
      - Methodology
      - Project administration
      - Software - Task Programming
      - Validation
      - Visualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Allison Williams"
    affiliation   : "1"
    role:
      - Investigation - Performed the experiment
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Noura Balbaa"
    affiliation   : "1"
    role:
      - Investigation - Performed the experiment
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Andrew Poskus"
    affiliation   : "1"
    role:
      - Investigation - Performed the experiment
      - Writing - Review & Editing
  - name          : "Olena Leshchyshen"
    affiliation   : "1"
    role:
      - Investigation - Performed the experiment
      - Writing - Review & Editing
  - name          : "Keith R. Lohse"
    affiliation   : "2"
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Methodology
      - Validation
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Michael J. Carter"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1280 Main Street West, Ivor Wynne Centre Room 203, McMaster University, Hamilton ON Canada, L8S 4K1"
    email         : "michaelcarter@mcmaster.ca"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Data curation
      - Formal analysis
      - Funding acquisition
      - Methodology
      - Project administration
      - Resources
      - Software - Task Programming
      - Supervision
      - Validation
      - Visualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Department of Kinesiology, McMaster University"
  - id            : "2"
    institution   : "Program in Physical Therapy, Washington University School of Medicine in Saint Louis"

authornote: |
  \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}

  We have outlined author contributions using CRediT (Contributor Roles Taxonomy - https://casrai.org/credit/).

abstract: |
  There has been growing research interest in the effects that motivation plays in motor learning, and specifically how different manipulations that affect autonomy, perceptions of competence, and social relatedness may directly benefit the learning process. In the present study, we present a well-powered (80%, N = 150) pre-registered manipulation of autonomy support by providing learners with choice during the practice of a speed cup-stacking skill. One group was given control over when a video demonstration was provided and the speed with which the demonstration was played. A yoked control group received an identical schedule of the demonstrations, but no choice (as their schedule was matched to a participant with choice). Critically, we also address a gap in the literature by adding a yoked control group who was explicitly told that they were being denied choice and that their schedule was chosen by another participant. (In the traditional yoked group, participants are merely told the schedule is determined in advance.) We found no statistically significant differences between groups in their learning of the cup-stacking skill, despite finding evidence that providing choice increased perceived autonomy (internally validating the manipulation). The two-one-side-test procedure further showed that although the groups were not statistically equivalent, the effect size is likely too small to practically study the effects of autonomy-support through choice in most motor learning labs. The current study not only adds to a growing body of research that questions the direct causal role that autonomy-support has on learning, but also the robustness of the so-called self-controlled learning advantage.

keywords          : "Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing"
wordcount         : "X"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

csl               : "apa-single-spaced.csl"
documentclass     : "apa7"
classoption       : "jou" # man for manuscript & jou for journal
output            : papaja::apa6_pdf
header-includes   :
  - \raggedbottom
  - \leftheader{St. Germain et al. 2021}
#   - \usepackage{lineno}
#   - \pagewiselinenumbers
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

A popular recommendation in recent years for creating an effective environment for motor skill learning has been to allow the learner to take control over an element of their practice that is traditionally controlled by a coach, therapist, or teacher [@sanli2013; @ste-marie2019]. This recommendation is based on the consistent finding that participants in a self-controlled (i.e., choice) group perform with higher proficiency compared to participants in a yoked (i.e., control) group on delayed retention and/or transfer tests. Participants in the yoked group do not experience the same choice opportunity provided to those in the self-controlled group. Instead, they are linked to a self-controlled participant and experience this participant's self-selected practice schedule. This so-called self-controlled learning advantage has been shown when participants are given the opportunity to schedule task difficulty *()*, the order that multiple tasks are practiced *()*, the frequency of watching a modeled demonstration *()*, and when to receive augmented feedback *()*.

Over the years, this manipulation has been described using a variety of names *()*, but more recently it has been subsumed by autonomy-support. In fact, autonomy-support is considered such a robust learning variable that it is one of three key pillars in the recently proposed "OPTIMAL" theory of motor learning *()*. Wulf and Lewthwaite argued that providing learners with opportunities for choice---considered an autonomy-supportive practice manipulation---can facilitate motor performance and learning by enhancing learner's expectancies for success, and by allowing the learner to maintain their attentional focus on the task by reducing the need for self-regulatory activity *()*. In other words, these psychological and attentional benefits, and concomitant increases in performance and learning are a by-product of experiencing choice opportunities during practice. Overall, autonomy-support is seen as a means to efficient goal-action coupling *()* and also links the "OPTIMAL" theory with Self-Determination theory *()*.

Despite its prominent role within the "OPTIMAL" theory of motor learning, there are numerous reasons to doubt the importance of autonomy-support through the provision of choice during practice. First, if the benefits are the result of having opportunities for choice then learning differences should not emerge between different self-controlled groups. However, in experiments where different groups of participants have choice over their feedback schedule, such learning differences have been found when this choice is made after rather than before a performance attempt *()*, when different criteria for success are provided to participants *()*, and when the absolute number of feedback choice opportunities are limited compared to unlimited at the outset of practice *()*. Second, there has been little-to-no support for the notion that practicing in a self-controlled group is perceived as more autonomy-supportive than being in a yoked group. Ste-Marie and colleagues *()*, for example, had participants in the self-controlled and yoked groups complete the perceived choice subscale of the Intrinsic Motivation Inventory and failed to find the expected effect of higher self-reported scores during practice in the self-controlled group. Similar findings have been reported by others *()*; however, McKay & Ste-Marie *()* recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group. This increased perceived autonomy-support did not, however, translate into enhanced learning compared to the yoked group. Although the available literature does not provide substantial evidence that self-controlled practice is autonomy-supportive, this does not necessarily mean such a manipulation is not autonomy-supportive *()*. For instance, this effect may in fact be quite small and require much larger sample sizes to detect *()* than those commonly used in motor learning experiments *()*.

There are at least two other methodological issues that warrant consideration. The first of these is that in self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component (e.g., feedback or when to watch a modeled demonstration) of their practice and participants in the yoked group are not given choice over this component. However, within the context of practice itself there are many other opportunities for choice that participants may explore, independent of their assigned group. Target-based tasks such as basketball free throws or bean-bag tossing are a popular choice in motor learning experiments and have been used in self-controlled learning experiments *()*. While a participant in the yoked group may not be permitted choice over their feedback schedule (or some other practice variable) with such tasks, this does not preclude them from being able to experience choice opportunities---and thus experience autonomy-support---when trying different throwing techniques, speeds, or release points. Thus, labeling yoked groups as being devoid of choice opportunities may be a misnomer. The other consideration relates to the instructions that are provided to participants in the yoked group. In the context of feedback[^1], these participants are typically informed that during practice they may or may not receive feedback after a given trial *()*. This means that participants in yoked groups are not even aware that they have been denied an opportunity for choice, nor that their feedback schedule was created by another participant who was given choice over when feedback was or was not provided. Either of these in isolation, or both simultaneously could contribute to the consistent finding that participants in self-controlled and yoked groups report similar perceived autonomy scores when asked about their opportunities for choices with respect to the motor task *()* or about their practice environment in general *()*.

[^1]: While feedback is used in this example, this issue surrounding instructions is also relevant to other practice variables commonly used in self-controlled learning experiments.

Here we investigated the effects of making participants in a yoked group explicitly aware of not only being denied opportunities for choice over their frequency of watching and the playback speed of video demonstrations, but also that the schedule they would experience during practice was created by another participant in the experiment. The addition of this novel yoked group allowed us to address one of the previously identified methodological limitations regarding experimental group instructions of previous self-controlled research. We compared the performance of this explicit yoked group with traditional self-controlled and yoked groups on a speed cup-stacking task in practice and in a delayed retention test.

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study *()*. The experimental design and analyses were preregistered using AsPredicted.org and is available here: **ADD URL**.

## Participants

## Material

## Procedure

## Data analysis

<!-- We used `r cite_r("r-references.bib")` for all our analyses. -->

# Results

# Discussion

\newpage

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

\endgroup

### 2021-05-08 docs/manuscript.Rmd
minor update of files

@@
   - \leftheader{St. Germain et al. 2021}
-#   - \usepackage{lineno}
-#   - \pagewiselinenumbers
+  - \usepackage{lineno}
+  - \pagewiselinenumbers
 ---
@@
 ## Participants
+One-hundred and fifty participants completed the experiment.
+Sample size was determined by an a priori power calculation based on our smallest comparison of interest.
+An early estimate for the effect of self-controlled over yoked practice was a Hedges’ $g = 0.63$ *()* and while planning this experiment this effect was estimated to be $g = 0.52$ *()*.
+Based on this effect, a positive correlation of $r = 0.6$ between retention and pre-test as the covariate, and 80% power to detect a difference between the self-controlled and traditional yoked groups, the required number of participants was 31 per group.
+Considering the novelty of our explicit yoked group, we assumed a smaller effect, $g = 0.4$, between it and the traditional yoked group.
+With the same parameters as above, this resulted in our final sample of 50 participants per group.
+Participants completed the experiment in either the Self-Controlled group $(M_{age} = 18.0, SD = 0.34)$, the Traditional Yoked group $(M_{age} = 19.5, SD = 1.89)$, or the Explicit Yoked group $(M_{age} = 19.2, SD = 1.55)$.
+We collected the Self-Controlled group first as their self-selected observation schedule was required for the yoking procedure for the two other groups.
+Once the Self-Controlled group had been collected, participants were randomly assigned to one of the two Yoked groups.
+All participants provided written informed consent approved by and conducted in accordance with the University’s Research Ethics Board.
+Participants received either $15 or a course bonus for their participation.
 
 ## Material
+Participants were tasked with learning the 3-6-3 speed cup stacking sequence based on the rules of the World Sport Stacking Association [(https://www.thewssa.com/)](https://www.thewssa.com/).
+The sequence consisted of an upstack phase and a downstack phase using official Speed Stacks cups [(https://www.speedstacks.com/)](https://www.speedstacks.com/).
+Participants performed the task using both their hands and had to complete an upstacking and a downstacking phase.
+The upstacking phase began by completing the first 3 cup pyramid, followed by the 6 cup pyramid, and then the other 3 cup pyramid.
+The downstacking phase began by returning to and collapsing the 3 cup pyramid that was upstacked first, then the 6 cup pyramid, and finally the last 3 cup pyramid.
 
 ## Procedure
+Participants completed two data collection sessions separated by approximately 24 hours.
+Session 1 consisted of a pre-test and an acquisition phase.
+Session 2 consisted of a delayed retention test.
+At the start of each phase of the experiment, all participants received phase-specific instructions **(see Table 1)**.
+Group specific instructions were provided prior to the acquisition phase.
+The instructions appeared on a 22-inch computer monitor (1920x1080 resolution) positioned to the right of the participant.
+Participants followed along as the instructions were read aloud by the researcher.
+
+Each trial began with participants standing at a standard height table with their hands on marked positions on the table in front of them.
+The 12 cups were located in upside down stacks of 3-6-3 in front of the participant.
+Following a "Get Ready!" prompt displayed for 1 s and a constant foreperiod of 1 s, an audiovisual "Go-signal" (green square and a beep tone) was presented.
+Participants were instructed to start stacking as quickly as possible following the "Go-signal" as its presentation initiated the timer.
+Once the upstack and downstack phases were completed, participants were instructed to press the spacebar on a keyboard located in front of them to stop the timer.
+If an error occurred (e.g., only completed the upstack phase then stopped the timer, forgot to hit the timer, etc), the experimenter recorded the trial number for later removal.
+The pre-test and delayed retention test both consisted of five no-feedback trials.
+The acquisition phase had 25 trials and was the only phase where the video demonstration could be watched based on group assignment.
+Participants in the Self-Controlled group could decide at the start of each trial if they wanted to watch the video demonstration.
+If they chose to watch the video, they were then asked whether they wanted to watch it in real-time or slow motion (35% of real-time).
+Participants in the Traditional Yoked and Explicit Yoked groups received the demonstration schedule created by a participant in the Self-Controlled group with the exception that participants in the Explicit Yoked group were made aware that this schedule was created by another participant **(see Table 1)**.
+Feedback about the participant’s stacking time was provided after every trial in acquisition.
+The timeline of a typical trial is illustrated in **Figure 1**.
+
+To test predictions based on the "OPTIMAL" theory regarding the role of motivation, enhanced expectancies, and autonomy-support, participants completed the interest/enjoyment and perceived competence subscales from the Intrinsic Motivation Inventory *()* and a custom scale regarding choice used in previous self-controlled motor learning experiments *()*.
+The order of questions from each scale were randomized and each question was rated using a 7-point Likert scale.
+Participants answered these questions after the pre-test, after trials five and 25 of acquisition, and before the delayed retention test.
+
+A custom LabVIEW (National Instruments Inc.) program was created that controlled the presentation of all instructions, the video demonstrations, the timing of the experimental protocol, and recorded and stored the data for later analysis.
 
 ## Data analysis
-
-<!-- We used `r cite_r("r-references.bib")` for all our analyses. -->
+Our primary outcome measure was stacking time (i.e., response time) in seconds.
+Trials recorded as errors $(76/5250 = 1.45\%)$ during data collection were manually removed prior to data analysis.
+For each participant, pre-test and delayed retention trials were aggregated into one block of five trials and acquisition was aggregated into five blocks of five trials.
+Significance level was set to 0.05 for all statistical tests.
+Effect sizes for omnibus tests are reported using generalized eta squared $(\eta^2_{G})$ or eta squared $(\eta^2)$.
+Hedges’ $g$ values were calculated to gauge the effect size of the post hoc comparisons using Holm’s correction.
+A Cook’s distance of $\geq 1$ was used to identify any influential cases.
 
 # Results
+## Pre-registered analysis
+To test whether delayed retention was differentially impacted by the experimental group (i.e., Self-Controlled, Traditional Yoked, Explicit Yoked) experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test **(Fig 2C)**.
+As can be seen, the Self-Controlled group $(M = 9.99, \,95\% \,CI = [9.68, \,10.31])$, the Traditional Yoked group $(M = 10.18, \,95\% \,CI = [9.86, \,10.50])$, and the Explicit Yoked group $(M = 10.12, \,95\% \,CI = [9.81, \,10.44])$ all had similar stacking times in retention (means are shown as the adjusted means controlling for pre-test).
+The effect of Group was not significant, $F(2, 146) = .335, \,p = .716, \,\eta^2 = .002$.
+
+##Non pre-registered analyses
+###Traditional self-controlled learning advantage
+To investigate whether a traditional self-controlled learning advantage existed&mdash;that is a comparison between the Self-Controlled and Traditional Yoked groups&mdash;we analyzed the non-adjusted retention scores using a Welch’s t-test.
+The analysis revealed that the Self-Controlled group $(M = 9.77, \,95\% \,CI = [9.55, \,9.99])$ and the Traditional Yoked group $(M = 10.20, \,95\% \,CI = [9.92, \,10.49])$ were not statistically different, $t(88.10) = 1.45, \,p = .15, \,g = .29$.
 

### 2021-05-08 docs/manuscript.tex
minor update of files

@@
 \leftheader{St. Germain et al. 2021}
+\usepackage{lineno}
+\pagewiselinenumbers
 \ifxetex
@@
 
+One-hundred and fifty participants completed the experiment.
+Sample size was determined by an a priori power calculation based on our smallest comparison of interest.
+An early estimate for the effect of self-controlled over yoked practice was a Hedges' \(g = 0.63\) \emph{()} and while planning this experiment this effect was estimated to be \(g = 0.52\) \emph{()}.
+Based on this effect, a positive correlation of \(r = 0.6\) between retention and pre-test as the covariate, and 80\% power to detect a difference between the self-controlled and traditional yoked groups, the required number of participants was 31 per group.
+Considering the novelty of our explicit yoked group, we assumed a smaller effect, \(g = 0.4\), between it and the traditional yoked group.
+With the same parameters as above, this resulted in our final sample of 50 participants per group.
+Participants completed the experiment in either the Self-Controlled group \((M_{age} = 18.0, SD = 0.34)\), the Traditional Yoked group \((M_{age} = 19.5, SD = 1.89)\), or the Explicit Yoked group \((M_{age} = 19.2, SD = 1.55)\).
+We collected the Self-Controlled group first as their self-selected observation schedule was required for the yoking procedure for the two other groups.
+Once the Self-Controlled group had been collected, participants were randomly assigned to one of the two Yoked groups.
+All participants provided written informed consent approved by and conducted in accordance with the University's Research Ethics Board.
+Participants received either \$15 or a course bonus for their participation.
+
 \hypertarget{material}{%
 \subsection{Material}\label{material}}
+
+Participants were tasked with learning the 3-6-3 speed cup stacking sequence based on the rules of the World Sport Stacking Association \href{https://www.thewssa.com/}{(https://www.thewssa.com/)}.
+The sequence consisted of an upstack phase and a downstack phase using official Speed Stacks cups \href{https://www.speedstacks.com/}{(https://www.speedstacks.com/)}.
+Participants performed the task using both their hands and had to complete an upstacking and a downstacking phase.
+The upstacking phase began by completing the first 3 cup pyramid, followed by the 6 cup pyramid, and then the other 3 cup pyramid.
+The downstacking phase began by returning to and collapsing the 3 cup pyramid that was upstacked first, then the 6 cup pyramid, and finally the last 3 cup pyramid.
 
@@
 
+Participants completed two data collection sessions separated by approximately 24 hours.
+Session 1 consisted of a pre-test and an acquisition phase.
+Session 2 consisted of a delayed retention test.
+At the start of each phase of the experiment, all participants received phase-specific instructions \textbf{(see Table 1)}.
+Group specific instructions were provided prior to the acquisition phase.
+The instructions appeared on a 22-inch computer monitor (1920x1080 resolution) positioned to the right of the participant.
+Participants followed along as the instructions were read aloud by the researcher.
+
+Each trial began with participants standing at a standard height table with their hands on marked positions on the table in front of them.
+The 12 cups were located in upside down stacks of 3-6-3 in front of the participant.
+Following a ``Get Ready!'' prompt displayed for 1 s and a constant foreperiod of 1 s, an audiovisual ``Go-signal'' (green square and a beep tone) was presented.
+Participants were instructed to start stacking as quickly as possible following the ``Go-signal'' as its presentation initiated the timer.
+Once the upstack and downstack phases were completed, participants were instructed to press the spacebar on a keyboard located in front of them to stop the timer.
+If an error occurred (e.g., only completed the upstack phase then stopped the timer, forgot to hit the timer, etc), the experimenter recorded the trial number for later removal.
+The pre-test and delayed retention test both consisted of five no-feedback trials.
+The acquisition phase had 25 trials and was the only phase where the video demonstration could be watched based on group assignment.
+Participants in the Self-Controlled group could decide at the start of each trial if they wanted to watch the video demonstration.
+If they chose to watch the video, they were then asked whether they wanted to watch it in real-time or slow motion (35\% of real-time).
+Participants in the Traditional Yoked and Explicit Yoked groups received the demonstration schedule created by a participant in the Self-Controlled group with the exception that participants in the Explicit Yoked group were made aware that this schedule was created by another participant \textbf{(see Table 1)}.
+Feedback about the participant's stacking time was provided after every trial in acquisition.
+The timeline of a typical trial is illustrated in \textbf{Figure 1}.
+
+To test predictions based on the ``OPTIMAL'' theory regarding the role of motivation, enhanced expectancies, and autonomy-support, participants completed the interest/enjoyment and perceived competence subscales from the Intrinsic Motivation Inventory \emph{()} and a custom scale regarding choice used in previous self-controlled motor learning experiments \emph{()}.
+The order of questions from each scale were randomized and each question was rated using a 7-point Likert scale.
+Participants answered these questions after the pre-test, after trials five and 25 of acquisition, and before the delayed retention test.
+
+A custom LabVIEW (National Instruments Inc.) program was created that controlled the presentation of all instructions, the video demonstrations, the timing of the experimental protocol, and recorded and stored the data for later analysis.
+
 \hypertarget{data-analysis}{%
@@
 
+Our primary outcome measure was stacking time (i.e., response time) in seconds.
+Trials recorded as errors \((76/5250 = 1.45\%)\) during data collection were manually removed prior to data analysis.
+For each participant, pre-test and delayed retention trials were aggregated into one block of five trials and acquisition was aggregated into five blocks of five trials.
+Significance level was set to 0.05 for all statistical tests.
+Effect sizes for omnibus tests are reported using generalized eta squared \((\eta^2_{G})\) or eta squared \((\eta^2)\).
+Hedges' \(g\) values were calculated to gauge the effect size of the post hoc comparisons using Holm's correction.
+A Cook's distance of \(\geq 1\) was used to identify any influential cases.
+
 \hypertarget{results}{%
 \section{Results}\label{results}}
+
+\hypertarget{pre-registered-analysis}{%
+\subsection{Pre-registered analysis}\label{pre-registered-analysis}}
+
+To test whether delayed retention was differentially impacted by the experimental group (i.e., Self-Controlled, Traditional Yoked, Explicit Yoked) experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test \textbf{(Fig 2C)}.
+As can be seen, the Self-Controlled group \((M = 9.99, \,95\% \,CI = [9.68, \,10.31])\), the Traditional Yoked group \((M = 10.18, \,95\% \,CI = [9.86, \,10.50])\), and the Explicit Yoked group \((M = 10.12, \,95\% \,CI = [9.81, \,10.44])\) all had similar stacking times in retention (means are shown as the adjusted means controlling for pre-test).
+The effect of Group was not significant, \(F(2, 146) = .335, \,p = .716, \,\eta^2 = .002\).
+
+\#\#Non pre-registered analyses
+\#\#\#Traditional self-controlled learning advantage
+To investigate whether a traditional self-controlled learning advantage existed---that is a comparison between the Self-Controlled and Traditional Yoked groups---we analyzed the non-adjusted retention scores using a Welch's t-test.
+The analysis revealed that the Self-Controlled group \((M = 9.77, \,95\% \,CI = [9.55, \,9.99])\) and the Traditional Yoked group \((M = 10.20, \,95\% \,CI = [9.92, \,10.49])\) were not statistically different, \(t(88.10) = 1.45, \,p = .15, \,g = .29\).
 

### 2021-05-08 docs/manuscript.Rmd
update manuscript files

@@
 footnotelist      : no
-linenumbers       : no
+linenumbers       : yes
 mask              : no
@@
 header-includes   :
+  - \pagewiselinenumbers
   - \raggedbottom
   - \leftheader{St. Germain et al. 2021}
-  - \usepackage{lineno}
-  - \pagewiselinenumbers
 ---
@@
 # Results
+
 ## Pre-registered analysis
 To test whether delayed retention was differentially impacted by the experimental group (i.e., Self-Controlled, Traditional Yoked, Explicit Yoked) experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test **(Fig 2C)**.
-As can be seen, the Self-Controlled group $(M = 9.99, \,95\% \,CI = [9.68, \,10.31])$, the Traditional Yoked group $(M = 10.18, \,95\% \,CI = [9.86, \,10.50])$, and the Explicit Yoked group $(M = 10.12, \,95\% \,CI = [9.81, \,10.44])$ all had similar stacking times in retention (means are shown as the adjusted means controlling for pre-test).
-The effect of Group was not significant, $F(2, 146) = .335, \,p = .716, \,\eta^2 = .002$.
+As can be seen, the Self-Controlled group $(M = 9.99, \,95\%CI = [9.68,10.31])$, the Traditional Yoked group $(M = 10.18, \,95\%CI = [9.86,10.50])$, and the Explicit Yoked group $(M = 10.12, \,95\%CI = [9.81,10.44])$ all had similar stacking times in retention (means are shown as the adjusted means controlling for pre-test).
+The effect of Group was not significant, $F(2,146) = .335, \,p = .716, \,\eta^2 = .002$.
 
-##Non pre-registered analyses
-###Traditional self-controlled learning advantage
+## Non pre-registered analyses
+
+### Traditional self-controlled learning advantage
 To investigate whether a traditional self-controlled learning advantage existed&mdash;that is a comparison between the Self-Controlled and Traditional Yoked groups&mdash;we analyzed the non-adjusted retention scores using a Welch’s t-test.
-The analysis revealed that the Self-Controlled group $(M = 9.77, \,95\% \,CI = [9.55, \,9.99])$ and the Traditional Yoked group $(M = 10.20, \,95\% \,CI = [9.92, \,10.49])$ were not statistically different, $t(88.10) = 1.45, \,p = .15, \,g = .29$.
+The analysis revealed that the Self-Controlled group $(M = 9.77, \,95\%CI = [9.55,9.99])$ and the Traditional Yoked group $(M = 10.20, \,95\%CI = [9.92,10.49])$ were not statistically different, $t(88.10) = 1.45, \,p = .15, \,g = .29$.
+
+### Acquisition phase
+Stacking time for each Group decreased across acquisition blocks **(Fig 2B)**, suggesting participants became more proficient at the 3-6-3 speed stacking task.
+A 3 Group x 5 Block mixed ANOVA with repeated measures on Block revealed a significant Block effect, $F(3.63,533.79) = 116.73, \,p < .001, \,\eta^2_{G} = .133$.
+Post hoc comparisons revealed all acquisition blocks were significantly different from each other.
+Both the Group effect, $F(2,147) = .738, p = .48, \,\eta^2_{G} = .008$, and Group x Block interaction, $F(7.26,533.79) = .543, \,p = .802, \,\eta^2_{G} = .001$, were not statistically significant.
+
+### Perceived autonomy
+Self-reported perceived autonomy scores are displayed in **Fig 3A** where it can be seen that the Self-Controlled group reported slightly higher scores compared to the two Yoked groups at all time points following the pre-test.
+A 3 Group x 3 Time ANCOVA controlling for pre-test revealed a significant Group effect, $F(2,146) = 8.04, \,p < .001, \,\eta^2_{G} = .083.$ Post hoc comparisons on the adjusted means revealed that the Self-Controlled group $(M = 5.61, \,95\%CI =[5.42,5.80])$ had significantly higher perceptions of autonomy compared to both the Traditional Yoked group $(M = 5.13, \,95\%CI = [4.94,5.32])$ and the Explicit Yoked group $(M = 5.13, \,95\%CI = [4.94,5.32])$, which did not differ from each other (and were, in fact, identical to two decimal places).
+Both the Time effect, $F(1.61,234.98) = .867, \,p = .400, \,\eta^2_{G} = .001$, and Group x Time interaction, $F(3.22,234.98) = 2.10, \,p = .096, \,\eta^2_{G} = .005$, were not significant.
+
+### Intrinsic motivation
+Self-reported intrinsic motivation scores can be found in **Fig 3B**.
+At each time point, all groups reported similar scores on the interest/enjoyment subscale.
+A 3 Group x 3 Time ANCOVA controlling for pre-test revealed non-significant effects for Group, $F(2,146) = 2.08, \,p = .129, \,\eta^2_{G} = .024$, Time, $F(1.68,245.73) = .563, \,p = .541, \,\eta^2_{G} = .001$, and the Group x Time interaction, $F(3.37,245.73) = .333, \,p = .824, \,\eta^2_{G} = .001$.
+
+### Perceived competence
+The scores from the perceived competence subscale at each time point are displayed in **Fig 3C**.
+As can be seen, perceived competence scores showed a modest increase over time followed by a slight decrease before the delayed retention test.
+A 3 Group x 3 Time ANCOVA controlling for pre-test showed an effect of Time, $F(1.75,255.22) = 10.60, \,p < .001, \,\eta^2_{G} = .015$.
+Post hoc tests on adjusted means revealed that scores were rated as significantly higher at the end of acquisition $(M = 3.98, \,95\%CI = [3.67,3.89])$ and before retention $(M = 3.78, \,95\%CI = [3.67,3.89])$ compared to after trial 5 $(M = 3.60, \,95\%CI = [3.49,3.71])$.
+However, perceived competence was significantly lower before retention compared to the end of acquisition.
+No significant effect of Group, $F(2,146) = 2.65, \,p = .074, \,\eta^2_{G} = .028$, or Group x Time interaction, $F(3.50,255.22) = .549, \,p = .677, \,\eta^2_{G} = .002$, was found.
+
+### Equivalence tests
+To further probe our null effects related to our main predictions *()*, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure *()*.
+To establish our smallest effect size of interest *()*, we used Simonsohn’s *()* recommendation of setting your smallest effect size of interest to what a design had 33% power to detect.
+Our current design had 33% power to detect a Cohen’s $d_{s} = .31$.
+The Self-Controlled and Traditional Yoked groups were not statistically different, $t(97.99) = -0.830, \,p = 0.409$, and not statistically equivalent, $t(97.99) = 0.720, \,p = 0.237$, given equivalence bounds of **GET RAW SCALE VALUES**.
+Similarly, the Traditional Yoked and Explicit yoked groups were not statistically different, $t(97.99) = 0.262, \,p = 0.794$, and not statistically equivalent, $t(97.99) = -1.288, \,p = 0.100$, given equivalence bounds of **GET RAW SCALE**.
 
 # Discussion
+It has been argued that self-controlled practice conditions are effective for motor learning because they are autonomy-supportive in nature *()*.
+Yet, this claim has largely been assumed *()* and when tested, has received little to not support in the motor learning literature to date *()*.
+Here, we addressed a possible methodological limitation for this lack of support.
+That is, in previous self-controlled motor learning research, participants in the yoked group are not made aware that they have been denied opportunities to exercise choice over a practice variable such as feedback or watching a modeled demonstration.
+In the present experiment we introduced a novel yoked group that was explicitly told that the observation schedule—frequency and speed of video—they would receive during practice was actually one created by another participant in the experiment.
+Contrary to our prediction, the Explicit Yoked group did not report significantly lower perceived autonomy scores than the Traditional Yoked group, which was only informed their observation schedule was predetermined.
+In line with the "OPTIMAL" theory *()*, the Self-Controlled group reported significantly higher perceived autonomy-support than both the Traditional and Explicit Yoked groups.
+However, this boost in perceived autonomy did not lead to enhanced motor performance or learning.
+These findings from a well-powered experiment are difficult to reconcile with a core pillar of the "OPTIMAL" theory of motor learning *()*.
+
+## Self-controlled practice conditions as autonomy-supportive
+A common problem with many of the self-controlled or choice motor learning literature claiming autonomy-support as an underlying mechanism for self-controlled learning advantages is a failure to include measures that actually test this claim *()*.
+Instead, this link to autonomy-support is merely assumed based on the provision of choice to one group of participants versus not giving the same choice to another group of participants.
+As noted earlier, an issue with this assumption is that within the practice environment itself, there are myriad opportunities for participants, independent of group, to exercise choice.
+In throwing tasks common to motor learning, participants can explore the task workspace by attempting different throwing techniques.
+In more lab-based tasks that consist of multiple spatial and timing goals (e.g., waveform matching), participants can choose a single goal to focus on and master before shifting their attention to another goal.
+Commensurate with this idea, Ste-Marie et al.
+*()* found no differences in perceived choice regarding the motor task being learned between their self-controlled and yoked groups, despite the self-controlled group showing enhanced retention.
+This may explain why research has consistently reported perceived autonomy scores that do not differ significantly between self-controlled and yoked groups *()*.
+
+Another possible explanation for the finding that being in a self-controlled group has not been perceived as more autonomy-supportive than being in a yoked group is that choice is typically provided over a single element of the practice variable, such as the frequency of receiving feedback *()* or the level of task difficulty *()*.
+Control or choice over a single dimension may not be strong enough to elicit a large enough boost in perceived autonomy above and beyond that of being able to explore one’s task workspace as mentioned above.
+Thus, to increase the saliency of the self-controlled manipulation in the present experiment, we gave the self-controlled participants control over two elements of their observation schedule: viewing frequency and video playback speed.
+Having control of these two dimensions resulted in higher perceptions of autonomy in our Self-Controlled group compared to the Traditional and Explicit Yoked groups **(Fig 3A)** and may explain the inconsistency with past research failing to find this effect *()* However, McKay and Ste-Marie *()* recently found that choice over a single element increased perceived autonomy but similar to our data, they also did not find this led to increased learning.
+Thus, it is unclear whether the higher autonomy scores in the present experiment can in fact be attributed to having control over multiple elements of one’s observation schedule.
+
+In a similar vein, past research has also suggested that self-controlled learning benefits are not dependent on the amount of choice opportunities over a single element *()*.
+Given these findings, we argue that the most likely explanation for the inconsistency surrounding the effect of self-controlled practice being autonomy-supportive is that this effect is quite small, and the designs of previous experiments have lacked the statistical power to reliability detect this effect *()*.
+These experiments have had sample sizes of 20 participants or less per group, whereas there were 50 participants in each group in the present experiment and 64 per group (when collapsed across constant and variable practice schedules) in McKay and Ste-Marie *()*.
+Collapsing across our two yoked groups, we estimate an effect of autonomy-support of $g = .197$ whereas the estimate from McKay and Ste-Marie was $g = .57$.
+Regardless of the estimated size of the effect for autonomy-support through a self-controlled practice condition, a larger issue and challenge to the OPTIMAL theory *()* is that significantly higher perceptions of autonomy did not result in superior performance in either acquisition or delayed retention *()*.
+
+## No learning advantage from a self-controlled observation schedule
+The delayed retention results in the present experiment not only are inconsistent with numerous past experiments reporting a self-controlled motor learning benefit *()*, but also the general consensus that the self-controlled learning advantage is a robust effect *()*.
+Of late, however, there has been an increase in the number of papers reporting a failure to detect the so-called self-controlled learning advantage *()*.
+This recent lack of support may arise from the self-controlled learning advantage being a much smaller effect than originally estimated (g = 0.63 *)*.
+A more recent estimate of this effect from a meta-analysis using a weight-function model was g = .11, 95% CI = [.047, .18] *()*.
+This estimate was further reduced to g = .054 after controlling for publication bias using the precision-effect estimate with standard error (PEESE) method.
+Thus, both models seem to suggest a fairly trivial effect.
+Additional simulations included in the meta-analysis provided plausible effect size estimates ranging from g = -.11 to .26.
+In our experiment, the estimated effect size of self-controlled versus yoked (collapsed across our Traditional and Explicit Yoked groups) was g = 0.22.
+While this estimate is much larger than those from the weight-function model and PEESE method, it does fall within the range of plausible effect sizes.
+When the lack of a self-controlled advantage in previous work and our current experiment are contextualized within the findings of the self-controlled meta-analysis, it is not as surprising that the so-called self-controlled learning benefit was not replicated.
+Additionally, despite the large sample size of the present experiment (*n*/group = 50) versus the typical self-controlled motor learning experiment (median *n*/group = 18 *)*, the results of the primary analysis and the equivalence test remain inconclusive.
+This, along with the effect size estimates in the recent meta-analysis, suggest enormous sample sizes are required to reliably detect an effect of a self-controlled learning advantage.
+Using the upper bound, g = .26, of the range of plausible effects, 253 participants are required to have 80% power to detect this effect in retention using an independent-samples t-test.
+The number of participants jumps to 1300 per group, if for instance the estimate from the weight-function model, g = .11, is accurate *()*.
+Given the field of motor learning suffers from a lack of adequately powered designs *()*.
+and that underpowered designs are more likely to produce false positives and overestimated effect sizes *()*, we are skeptical of the replicability of the previous overwhelming support for the self-controlled learning advantage.
+
+## Lack of support for key predictions of the OPTIMAL theory of motor learning
+Within the "OPTIMAL" theory *()*, it is predicted that practice conditions that promote autonomy-support and enhance expectancies contribute to a virtuous cycle that leads to superior motor learning.
+In other words, significant group differences between self-controlled and yoked groups would be expected on measures related to these psychological constructs.
+As mentioned earlier, we found higher perceptions of autonomy-support in our Self-Controlled group relative to the Traditional and Explicit Yoked groups; however, this did not enhance motor learning as predicted by the virtuous cycle of the OPTIMAL theory.
+Contrary to the "OPTIMAL" theory, we did not find an effect of group for perceived competence (i.e., enhanced expectancies) or intrinsic motivation.
+Perceived competence scores did increase across acquisition blocks, which mirrors the improved motor performance seen throughout acquisition.
+These results are in line with results of a path analysis that suggested self-efficacy (i.e., enhanced expectancies) and intrinsic motivation were insufficient to explain self-controlled learning benefits *()*.
+Overall, these data are inconsistent with predictions of the "OPTIMAL" theory regarding autonomy-support and enhanced expectancies, and further question the causal role such manipulations play in motor learning.
+
+In sum, we found that being able to control two aspects of one’s observation schedule during practice was perceived as autonomy-supportive relative to not having this same control opportunity.
+However, making participants in an Explicit yoked group aware they would be denied a control opportunity during practice did not decrease perceptions of autonomy relative to participants in the Traditional Yoked group.
+Furthermore, no reliable group differences were found in a delayed retention test and we also failed to replicate the typical self-controlled learning advantage.
+These results add to a growing body of evidence that questions if manipulations of autonomy support directly affect learning *()*.
+One explanation for this lack of replicability is that the *"true"* effect of autonomy-support on motor learning is much smaller than previously estimated.
+Given the resources required (in terms of sample size) to reliably detect these tiny effects, we encourage motor learning scientists to invest their limited resources carefully&mdash;either studying practice conditions that have much bigger effects or devising ways to reduce variability and increase power through clever experimental design *()*.
 
@@
 ```
-::: {#refs custom-style="Bibliography"}
-:::
+<!-- ::: {#refs custom-style="Bibliography"} -->
+<!-- ::: -->
 

### 2021-05-08 docs/manuscript.tex
update manuscript files

@@
 
+\usepackage{lineno}
+
+\linenumbers
 \usepackage{csquotes}
+\pagewiselinenumbers
 \raggedbottom
 \leftheader{St. Germain et al. 2021}
-\usepackage{lineno}
-\pagewiselinenumbers
 \ifxetex
@@
 To test whether delayed retention was differentially impacted by the experimental group (i.e., Self-Controlled, Traditional Yoked, Explicit Yoked) experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test \textbf{(Fig 2C)}.
-As can be seen, the Self-Controlled group \((M = 9.99, \,95\% \,CI = [9.68, \,10.31])\), the Traditional Yoked group \((M = 10.18, \,95\% \,CI = [9.86, \,10.50])\), and the Explicit Yoked group \((M = 10.12, \,95\% \,CI = [9.81, \,10.44])\) all had similar stacking times in retention (means are shown as the adjusted means controlling for pre-test).
-The effect of Group was not significant, \(F(2, 146) = .335, \,p = .716, \,\eta^2 = .002\).
+As can be seen, the Self-Controlled group \((M = 9.99, \,95\%CI = [9.68,10.31])\), the Traditional Yoked group \((M = 10.18, \,95\%CI = [9.86,10.50])\), and the Explicit Yoked group \((M = 10.12, \,95\%CI = [9.81,10.44])\) all had similar stacking times in retention (means are shown as the adjusted means controlling for pre-test).
+The effect of Group was not significant, \(F(2,146) = .335, \,p = .716, \,\eta^2 = .002\).
 
-\#\#Non pre-registered analyses
-\#\#\#Traditional self-controlled learning advantage
+\hypertarget{non-pre-registered-analyses}{%
+\subsection{Non pre-registered analyses}\label{non-pre-registered-analyses}}
+
+\hypertarget{traditional-self-controlled-learning-advantage}{%
+\subsubsection{Traditional self-controlled learning advantage}\label{traditional-self-controlled-learning-advantage}}
+
 To investigate whether a traditional self-controlled learning advantage existed---that is a comparison between the Self-Controlled and Traditional Yoked groups---we analyzed the non-adjusted retention scores using a Welch's t-test.
-The analysis revealed that the Self-Controlled group \((M = 9.77, \,95\% \,CI = [9.55, \,9.99])\) and the Traditional Yoked group \((M = 10.20, \,95\% \,CI = [9.92, \,10.49])\) were not statistically different, \(t(88.10) = 1.45, \,p = .15, \,g = .29\).
+The analysis revealed that the Self-Controlled group \((M = 9.77, \,95\%CI = [9.55,9.99])\) and the Traditional Yoked group \((M = 10.20, \,95\%CI = [9.92,10.49])\) were not statistically different, \(t(88.10) = 1.45, \,p = .15, \,g = .29\).
+
+\hypertarget{acquisition-phase}{%
+\subsubsection{Acquisition phase}\label{acquisition-phase}}
+
+Stacking time for each Group decreased across acquisition blocks \textbf{(Fig 2B)}, suggesting participants became more proficient at the 3-6-3 speed stacking task.
+A 3 Group x 5 Block mixed ANOVA with repeated measures on Block revealed a significant Block effect, \(F(3.63,533.79) = 116.73, \,p < .001, \,\eta^2_{G} = .133\).
+Post hoc comparisons revealed all acquisition blocks were significantly different from each other.
+Both the Group effect, \(F(2,147) = .738, p = .48, \,\eta^2_{G} = .008\), and Group x Block interaction, \(F(7.26,533.79) = .543, \,p = .802, \,\eta^2_{G} = .001\), were not statistically significant.
+
+\hypertarget{perceived-autonomy}{%
+\subsubsection{Perceived autonomy}\label{perceived-autonomy}}
+
+Self-reported perceived autonomy scores are displayed in \textbf{Fig 3A} where it can be seen that the Self-Controlled group reported slightly higher scores compared to the two Yoked groups at all time points following the pre-test.
+A 3 Group x 3 Time ANCOVA controlling for pre-test revealed a significant Group effect, \(F(2,146) = 8.04, \,p < .001, \,\eta^2_{G} = .083.\) Post hoc comparisons on the adjusted means revealed that the Self-Controlled group \((M = 5.61, \,95\%CI =[5.42,5.80])\) had significantly higher perceptions of autonomy compared to both the Traditional Yoked group \((M = 5.13, \,95\%CI = [4.94,5.32])\) and the Explicit Yoked group \((M = 5.13, \,95\%CI = [4.94,5.32])\), which did not differ from each other (and were, in fact, identical to two decimal places).
+Both the Time effect, \(F(1.61,234.98) = .867, \,p = .400, \,\eta^2_{G} = .001\), and Group x Time interaction, \(F(3.22,234.98) = 2.10, \,p = .096, \,\eta^2_{G} = .005\), were not significant.
+
+\hypertarget{intrinsic-motivation}{%
+\subsubsection{Intrinsic motivation}\label{intrinsic-motivation}}
+
+Self-reported intrinsic motivation scores can be found in \textbf{Fig 3B}.
+At each time point, all groups reported similar scores on the interest/enjoyment subscale.
+A 3 Group x 3 Time ANCOVA controlling for pre-test revealed non-significant effects for Group, \(F(2,146) = 2.08, \,p = .129, \,\eta^2_{G} = .024\), Time, \(F(1.68,245.73) = .563, \,p = .541, \,\eta^2_{G} = .001\), and the Group x Time interaction, \(F(3.37,245.73) = .333, \,p = .824, \,\eta^2_{G} = .001\).
+
+\hypertarget{perceived-competence}{%
+\subsubsection{Perceived competence}\label{perceived-competence}}
+
+The scores from the perceived competence subscale at each time point are displayed in \textbf{Fig 3C}.
+As can be seen, perceived competence scores showed a modest increase over time followed by a slight decrease before the delayed retention test.
+A 3 Group x 3 Time ANCOVA controlling for pre-test showed an effect of Time, \(F(1.75,255.22) = 10.60, \,p < .001, \,\eta^2_{G} = .015\).
+Post hoc tests on adjusted means revealed that scores were rated as significantly higher at the end of acquisition \((M = 3.98, \,95\%CI = [3.67,3.89])\) and before retention \((M = 3.78, \,95\%CI = [3.67,3.89])\) compared to after trial 5 \((M = 3.60, \,95\%CI = [3.49,3.71])\).
+However, perceived competence was significantly lower before retention compared to the end of acquisition.
+No significant effect of Group, \(F(2,146) = 2.65, \,p = .074, \,\eta^2_{G} = .028\), or Group x Time interaction, \(F(3.50,255.22) = .549, \,p = .677, \,\eta^2_{G} = .002\), was found.
+
+\hypertarget{equivalence-tests}{%
+\subsubsection{Equivalence tests}\label{equivalence-tests}}
+
+To further probe our null effects related to our main predictions \emph{()}, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure \emph{()}.
+To establish our smallest effect size of interest \emph{()}, we used Simonsohn's \emph{()} recommendation of setting your smallest effect size of interest to what a design had 33\% power to detect.
+Our current design had 33\% power to detect a Cohen's \(d_{s} = .31\).
+The Self-Controlled and Traditional Yoked groups were not statistically different, \(t(97.99) = -0.830, \,p = 0.409\), and not statistically equivalent, \(t(97.99) = 0.720, \,p = 0.237\), given equivalence bounds of \textbf{GET RAW SCALE VALUES}.
+Similarly, the Traditional Yoked and Explicit yoked groups were not statistically different, \(t(97.99) = 0.262, \,p = 0.794\), and not statistically equivalent, \(t(97.99) = -1.288, \,p = 0.100\), given equivalence bounds of \textbf{GET RAW SCALE}.
 
@@
 \section{Discussion}\label{discussion}}
+
+It has been argued that self-controlled practice conditions are effective for motor learning because they are autonomy-supportive in nature \emph{()}.
+Yet, this claim has largely been assumed \emph{()} and when tested, has received little to not support in the motor learning literature to date \emph{()}.
+Here, we addressed a possible methodological limitation for this lack of support.
+That is, in previous self-controlled motor learning research, participants in the yoked group are not made aware that they have been denied opportunities to exercise choice over a practice variable such as feedback or watching a modeled demonstration.
+In the present experiment we introduced a novel yoked group that was explicitly told that the observation schedule---frequency and speed of video---they would receive during practice was actually one created by another participant in the experiment.
+Contrary to our prediction, the Explicit Yoked group did not report significantly lower perceived autonomy scores than the Traditional Yoked group, which was only informed their observation schedule was predetermined.
+In line with the ``OPTIMAL'' theory \emph{()}, the Self-Controlled group reported significantly higher perceived autonomy-support than both the Traditional and Explicit Yoked groups.
+However, this boost in perceived autonomy did not lead to enhanced motor performance or learning.
+These findings from a well-powered experiment are difficult to reconcile with a core pillar of the ``OPTIMAL'' theory of motor learning \emph{()}.
+
+\hypertarget{self-controlled-practice-conditions-as-autonomy-supportive}{%
+\subsection{Self-controlled practice conditions as autonomy-supportive}\label{self-controlled-practice-conditions-as-autonomy-supportive}}
+
+A common problem with many of the self-controlled or choice motor learning literature claiming autonomy-support as an underlying mechanism for self-controlled learning advantages is a failure to include measures that actually test this claim \emph{()}.
+Instead, this link to autonomy-support is merely assumed based on the provision of choice to one group of participants versus not giving the same choice to another group of participants.
+As noted earlier, an issue with this assumption is that within the practice environment itself, there are myriad opportunities for participants, independent of group, to exercise choice.
+In throwing tasks common to motor learning, participants can explore the task workspace by attempting different throwing techniques.
+In more lab-based tasks that consist of multiple spatial and timing goals (e.g., waveform matching), participants can choose a single goal to focus on and master before shifting their attention to another goal.
+Commensurate with this idea, Ste-Marie et al.~\emph{()} found no differences in perceived choice regarding the motor task being learned between their self-controlled and yoked groups, despite the self-controlled group showing enhanced retention.
+This may explain why research has consistently reported perceived autonomy scores that do not differ significantly between self-controlled and yoked groups \emph{()}.
+
+Another possible explanation for the finding that being in a self-controlled group has not been perceived as more autonomy-supportive than being in a yoked group is that choice is typically provided over a single element of the practice variable, such as the frequency of receiving feedback \emph{()} or the level of task difficulty \emph{()}.
+Control or choice over a single dimension may not be strong enough to elicit a large enough boost in perceived autonomy above and beyond that of being able to explore one's task workspace as mentioned above.
+Thus, to increase the saliency of the self-controlled manipulation in the present experiment, we gave the self-controlled participants control over two elements of their observation schedule: viewing frequency and video playback speed.
+Having control of these two dimensions resulted in higher perceptions of autonomy in our Self-Controlled group compared to the Traditional and Explicit Yoked groups \textbf{(Fig 3A)} and may explain the inconsistency with past research failing to find this effect \emph{()} However, McKay and Ste-Marie \emph{()} recently found that choice over a single element increased perceived autonomy but similar to our data, they also did not find this led to increased learning.
+Thus, it is unclear whether the higher autonomy scores in the present experiment can in fact be attributed to having control over multiple elements of one's observation schedule.
+
+In a similar vein, past research has also suggested that self-controlled learning benefits are not dependent on the amount of choice opportunities over a single element \emph{()}.
+Given these findings, we argue that the most likely explanation for the inconsistency surrounding the effect of self-controlled practice being autonomy-supportive is that this effect is quite small, and the designs of previous experiments have lacked the statistical power to reliability detect this effect \emph{()}.
+These experiments have had sample sizes of 20 participants or less per group, whereas there were 50 participants in each group in the present experiment and 64 per group (when collapsed across constant and variable practice schedules) in McKay and Ste-Marie \emph{()}.
+Collapsing across our two yoked groups, we estimate an effect of autonomy-support of \(g = .197\) whereas the estimate from McKay and Ste-Marie was \(g = .57\).
+Regardless of the estimated size of the effect for autonomy-support through a self-controlled practice condition, a larger issue and challenge to the OPTIMAL theory \emph{()} is that significantly higher perceptions of autonomy did not result in superior performance in either acquisition or delayed retention \emph{()}.
+
+\hypertarget{no-learning-advantage-from-a-self-controlled-observation-schedule}{%
+\subsection{No learning advantage from a self-controlled observation schedule}\label{no-learning-advantage-from-a-self-controlled-observation-schedule}}
+
+The delayed retention results in the present experiment not only are inconsistent with numerous past experiments reporting a self-controlled motor learning benefit \emph{()}, but also the general consensus that the self-controlled learning advantage is a robust effect \emph{()}.
+Of late, however, there has been an increase in the number of papers reporting a failure to detect the so-called self-controlled learning advantage \emph{()}.
+This recent lack of support may arise from the self-controlled learning advantage being a much smaller effect than originally estimated (g = 0.63 \emph{)}.
+A more recent estimate of this effect from a meta-analysis using a weight-function model was g = .11, 95\% CI = {[}.047, .18{]} \emph{()}.
+This estimate was further reduced to g = .054 after controlling for publication bias using the precision-effect estimate with standard error (PEESE) method.
+Thus, both models seem to suggest a fairly trivial effect.
+Additional simulations included in the meta-analysis provided plausible effect size estimates ranging from g = -.11 to .26.
+In our experiment, the estimated effect size of self-controlled versus yoked (collapsed across our Traditional and Explicit Yoked groups) was g = 0.22.
+While this estimate is much larger than those from the weight-function model and PEESE method, it does fall within the range of plausible effect sizes.
+When the lack of a self-controlled advantage in previous work and our current experiment are contextualized within the findings of the self-controlled meta-analysis, it is not as surprising that the so-called self-controlled learning benefit was not replicated.
+Additionally, despite the large sample size of the present experiment (\emph{n}/group = 50) versus the typical self-controlled motor learning experiment (median \emph{n}/group = 18 \emph{)}, the results of the primary analysis and the equivalence test remain inconclusive.
+This, along with the effect size estimates in the recent meta-analysis, suggest enormous sample sizes are required to reliably detect an effect of a self-controlled learning advantage.
+Using the upper bound, g = .26, of the range of plausible effects, 253 participants are required to have 80\% power to detect this effect in retention using an independent-samples t-test.
+The number of participants jumps to 1300 per group, if for instance the estimate from the weight-function model, g = .11, is accurate \emph{()}.
+Given the field of motor learning suffers from a lack of adequately powered designs \emph{()}.
+and that underpowered designs are more likely to produce false positives and overestimated effect sizes \emph{()}, we are skeptical of the replicability of the previous overwhelming support for the self-controlled learning advantage.
+
+\hypertarget{lack-of-support-for-key-predictions-of-the-optimal-theory-of-motor-learning}{%
+\subsection{Lack of support for key predictions of the OPTIMAL theory of motor learning}\label{lack-of-support-for-key-predictions-of-the-optimal-theory-of-motor-learning}}
+
+Within the ``OPTIMAL'' theory \emph{()}, it is predicted that practice conditions that promote autonomy-support and enhance expectancies contribute to a virtuous cycle that leads to superior motor learning.
+In other words, significant group differences between self-controlled and yoked groups would be expected on measures related to these psychological constructs.
+As mentioned earlier, we found higher perceptions of autonomy-support in our Self-Controlled group relative to the Traditional and Explicit Yoked groups; however, this did not enhance motor learning as predicted by the virtuous cycle of the OPTIMAL theory.
+Contrary to the ``OPTIMAL'' theory, we did not find an effect of group for perceived competence (i.e., enhanced expectancies) or intrinsic motivation.
+Perceived competence scores did increase across acquisition blocks, which mirrors the improved motor performance seen throughout acquisition.
+These results are in line with results of a path analysis that suggested self-efficacy (i.e., enhanced expectancies) and intrinsic motivation were insufficient to explain self-controlled learning benefits \emph{()}.
+Overall, these data are inconsistent with predictions of the ``OPTIMAL'' theory regarding autonomy-support and enhanced expectancies, and further question the causal role such manipulations play in motor learning.
+
+In sum, we found that being able to control two aspects of one's observation schedule during practice was perceived as autonomy-supportive relative to not having this same control opportunity.
+However, making participants in an Explicit yoked group aware they would be denied a control opportunity during practice did not decrease perceptions of autonomy relative to participants in the Traditional Yoked group.
+Furthermore, no reliable group differences were found in a delayed retention test and we also failed to replicate the typical self-controlled learning advantage.
+These results add to a growing body of evidence that questions if manipulations of autonomy support directly affect learning \emph{()}.
+One explanation for this lack of replicability is that the \emph{``true''} effect of autonomy-support on motor learning is much smaller than previously estimated.
+Given the resources required (in terms of sample size) to reliably detect these tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either studying practice conditions that have much bigger effects or devising ways to reduce variability and increase power through clever experimental design \emph{()}.
 
@@
 \setlength{\leftskip}{0.5in}
+
+\endgroup
 
@@
 
-\endgroup
-
 \end{document}

### 2021-05-20 docs/preprint/preprint.tex
init

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  jou]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Increased perceptions of autonomy through choice fail to enhance motor skill retention},
  pdfauthor={Laura St.~Germain1, Allison Williams1, Noura Balbaa1, Andrew Poskus1, Olena Leshchyshen1, Keith R. Lohse2, \& Michael J. Carter1},
  pdflang={en-EN},
  pdfkeywords={Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Autonomy-support does not benefit motor learning}
\keywords{Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing}
\usepackage{dblfloatfix}

\usepackage{csquotes}
\raggedbottom
\leftheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
\rightheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Increased perceptions of autonomy through choice fail to enhance motor skill retention}
\author{Laura St.~Germain\textsuperscript{1}, Allison Williams\textsuperscript{1}, Noura Balbaa\textsuperscript{1}, Andrew Poskus\textsuperscript{1}, Olena Leshchyshen\textsuperscript{1}, Keith R. Lohse\textsuperscript{2}, \& Michael J. Carter\textsuperscript{1}}
\date{}

\authornote{

\addORCIDlink{Laura St. Germain}{0000-0002-5513-4183}; \addORCIDlink{Keith R. Lohse}{0000-0002-7643-3887}; \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}

We have outlined author contributions using CRediT (Contributor Roles Taxonomy - \url{https://casrai.org/credit/}).

The authors made the following contributions. Laura St.~Germain: Conceptualization, Data curation, Formal analysis, Investigation - Performed the experiment, Methodology, Project administration, Software - Task Programming, Validation, Visualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Allison Williams: Investigation - Performed the experiment, Writing - Original Draft Preparation, Writing - Review \& Editing; Noura Balbaa: Investigation - Performed the experiment, Writing - Original Draft Preparation, Writing - Review \& Editing; Andrew Poskus: Investigation - Performed the experiment, Writing - Review \& Editing; Olena Leshchyshen: Investigation - Performed the experiment, Writing - Review \& Editing; Keith R. Lohse: Conceptualization, Data curation, Formal analysis, Methodology, Validation, Writing - Original Draft Preparation, Writing - Review \& Editing; Michael J. Carter: Conceptualization, Data curation, Formal analysis, Funding acquisition, Methodology, Project administration, Resources, Software - Task Programming, Supervision, Validation, Visualization, Writing - Original Draft Preparation, Writing - Review \& Editing.

Correspondence concerning this article should be addressed to Michael J. Carter, 1280 Main Street West, Ivor Wynne Centre Room 203, McMaster University, Hamilton ON Canada, L8S 4K1. E-mail: \href{mailto:michaelcarter@mcmaster.ca}{\nolinkurl{michaelcarter@mcmaster.ca}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Kinesiology, McMaster University\\\textsuperscript{2} Program in Physical Therapy, Washington University School of Medicine in Saint Louis}

\abstract{
There has been growing research interest in the effects that motivation plays in motor learning, and specifically how autonomy, competence, and social relatedness may directly benefit the learning process. Here, we present a preregistered manipulation of autonomy-support by providing learners with choice during the practice of a speed cup-stacking skill. One group was given control over when a video demonstration was provided and the viewing speed. A yoked control group received an identical demonstration schedule, but without choice (as their schedule was matched to a participant with choice). Critically, we addressed a gap in the literature by adding a yoked group who was explicitly told that they were being denied choice and that their schedule was chosen by another participant. We found no statistically significant learning differences between groups, despite finding evidence that providing choice increased perceived autonomy. Equivalence tests further showed that although the groups were not statistically equivalent, the effect size is likely too small to practically study the effects of autonomy-support through choice in most motor learning labs. These findings add to a growing body of research that questions a causal role of autonomy-support on motor learning, and the robustness of the so-called self-controlled learning advantage.
}

\begin{document}
\maketitle

A popular recommendation in recent years for creating an effective environment for motor skill learning has been to allow the learner to take control over an element of their practice that is traditionally controlled by a coach, therapist, or teacher (Sanli et al., 2013; Ste-Marie et al., 2019). This recommendation is based on the consistent finding that participants in a self-controlled (i.e., choice) group perform with higher proficiency compared to participants in a yoked (i.e., control) group on delayed retention and/or transfer tests. Participants in the yoked group do not experience the same choice opportunity provided to those in the self-controlled group. Instead, they are linked to a self-controlled participant and experience this participant's self-selected practice schedule. This so-called self-controlled learning advantage has been shown when participants are given the opportunity to schedule task difficulty (e.g., Andrieux et al., 2012; Leiker et al., 2016), the order that multiple tasks are practiced (e.g., Wu \& Magill, 2011), the frequency of watching a modeled demonstration (e.g. Wulf et al., 2005), and when to receive augmented feedback (e.g., Janelle et al., 1997; Patterson \& Carter, 2010).

Over the years, this manipulation has been described using a variety of names (e.g., self- and/or learner-controlled; -regulated; -directed; -selected), but more recently it has been subsumed by autonomy-support. In fact, autonomy-support is considered such a robust learning variable that it is one of three key pillars in the recently proposed ``OPTIMAL'' theory of motor learning (Wulf \& Lewthwaite, 2016). Wulf and Lewthwaite (2016) argued that providing learners with opportunities for choice---considered an autonomy-supportive practice manipulation---can facilitate motor performance and learning by enhancing learner's expectancies for success, and by allowing the learner to maintain their attentional focus on the task by reducing the need for self-regulatory activity (Abdollahipour et al., 2017; Chua et al., 2018; Wulf et al., 2018). In other words, these psychological and attentional benefits, and concomitant increases in performance and learning are a by-product of exercising choice during practice. Overall, autonomy-support is seen as a means to efficient goal-action coupling (Wulf \& Lewthwaite, 2016) and also links the ``OPTIMAL'' theory with Self-Determination theory (Deci \& Ryan, 2000).

Despite its prominent role within the ``OPTIMAL'' theory of motor learning, there are numerous reasons to doubt the importance of autonomy-support through the provision of choice during practice. First, if the benefits are the result of having opportunities for choice then learning differences should not emerge between different self-controlled groups. However, in experiments where different groups of participants have choice over their feedback schedule, such learning differences have been found, but not limited to, when this choice is made \emph{after} rather than before a performance attempt (Carter et al., 2014; Chiviacowsky \& Wulf, 2005), when different criteria for success are provided to participants (Chiviacowsky et al., 2012), and when the absolute number of feedback choice opportunities are limited compared to unlimited at the outset of practice (Hansen et al., 2011; Patterson et al., 2011). Second, there has been little-to-no support for the notion that practicing in a self-controlled group is perceived as more autonomy-supportive than being in a yoked group. Ste-Marie et al. (2013), for example, had participants in the self-controlled and yoked groups complete the perceived choice subscale of the Intrinsic Motivation Inventory and failed to find the expected effect of higher self-reported scores during practice in the self-controlled group. Similar findings have been reported by others (Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020b). However, McKay and Ste-Marie (2020a) recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group. This increased perceived autonomy-support did not, however, translate into enhanced learning compared to the yoked group. Although the available literature does not provide substantial evidence that self-controlled practice is autonomy-supportive, this does not necessarily mean such a manipulation is not autonomy-supportive (Altman \& Bland, 1995). For instance, this effect may in fact be quite small and require much larger sample sizes to detect than those commonly used in motor learning experiments (Lohse et al., 2016).

There are at least two other methodological issues that warrant consideration. The first of these is that in self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component (e.g., feedback or when to watch a modeled demonstration) of their practice and participants in the yoked group are not given choice over this component. However, within the context of practice itself there are many other opportunities for choice that participants may explore, independent of their assigned group. Target-based tasks such as basketball free throws (e.g., Aiken et al., 2012) or bean-bag tossing (Grand et al., 2015) are a popular choice in motor learning experiments and have been used in self-controlled learning experiments. While a participant in the yoked group may not be permitted choice over their feedback schedule (or some other practice variable) in these experiments, this does not preclude them from opportunities for choice---and thus autonomy-support---when deciding to try different throwing techniques, speeds, and/or release points. Thus, labeling yoked groups as being devoid of choice opportunities may be a misnomer. The other consideration relates to the instructions that are provided to participants in the yoked group. In the context of feedback\footnote{While feedback is used in this example, this issue surrounding instructions is also relevant to other practice variables commonly used in self-controlled learning experiments.}, these participants are typically informed that during practice they may or may not receive feedback after a given trial (e.g., Chiviacowsky \& Wulf, 2002; Patterson \& Carter, 2010). This means that participants in yoked groups are not even aware that they have been denied an opportunity for choice, nor that their feedback schedule was created by another participant who was given choice over when feedback was or was not provided. Either of these in isolation, or both simultaneously could contribute to the consistent finding that participants in self-controlled and yoked groups report similar perceived autonomy scores when asked about their opportunities for choices with respect to the motor task (Ste-Marie et al., 2013) or about their practice environment in general (Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020b).

\begin{table*}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:table1}Group specific instructions detailing the observation schedule that would be experienced during Acquisition.}

\begin{tabular}{ll}
\toprule
  & Acquisition instructions\\
\midrule
Self-Controlled & Before each trial, you will be asked whether you wish to watch a modeled demonstration of the task.\\
 & If you choose YES, you will then be asked whether you want to watch the video in real-time or in\\
 & slow-motion.\\
Traditional Yoked & Before each trial, you may or may not watch a modeled demonstration of the task based on a pre-\\
 & determined schedule. If you observe a model, it might be presented in real-time or in slow-motion\\
 & based on the pre-determined schedule.\\
Explicit Yoked & Before each trial, you may or may not watch a modeled demonstration of the task based on the\\
 & schedule another participant selected. If you observe a model, it might be presented in real-time or in\\
 & slow-motion based on what that participant selected.\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table*}

Here we investigated the effects of making participants in a yoked group explicitly aware of not only being denied opportunities for choice over their frequency of watching and the playback speed of video demonstrations, but also that the schedule they would experience during practice was created by another participant in the experiment. The addition of this novel yoked group allowed us to address one of the previously identified methodological limitations regarding experimental group instructions in past self-controlled research. We compared the performance of this explicit yoked group with traditional self-controlled and yoked groups on a speed cup-stacking task in practice and in a delayed retention test.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study (Simmons et al., 2012). The experimental design and analyses were preregistered using AsPredicted.org and can be viewed here: \url{https://aspredicted.org/ze8cj.pdf}.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

One-hundred and fifty participants completed the experiment. Sample size was determined by an a priori power calculation based on our smallest comparison of interest. An early estimate for the effect of self-controlled over yoked practice was a Hedges' \(g = 0.63\) (McKay et al., 2014) and while planning this experiment this effect was estimated to be \(g = 0.52\) (Z. Yantha, personal communication, October 2019). Based on this effect, a positive correlation of \(r = 0.6\) between retention and pre-test as the covariate, and 80\% power to detect a difference between the self-controlled and traditional yoked groups, the required number of participants was 31 per group. Considering the novelty of our Explicit Yoked group, we assumed a smaller effect, \(g = 0.4\), between it and the Traditional Yoked group. With the same parameters as above, this resulted in our final sample of 50 participants per group.

Participants completed the experiment in either the Self-Controlled group \((M_{age} = 18.0\), \emph{SD} = 0.34), the Traditional Yoked group \((M_{age} = 19.5\), \emph{SD} = 1.89), or the Explicit Yoked group \((M_{age} = 19.2\), \emph{SD} = 1.55). We collected the Self-Controlled group first as their self-selected observation schedule was required for the yoking procedure for the two other groups. Once the Self-Controlled group had been collected, participants were randomly assigned to one of the two Yoked groups. All participants provided written informed consent approved by and conducted in accordance with the University's Research Ethics Board. Participants received either \$15 or a course bonus for their participation.

\hypertarget{material}{%
\subsection{Material}\label{material}}

Participants were tasked with learning the 3-6-3 speed cup stacking sequence based on the rules of the World Sport Stacking Association \href{https://www.thewssa.com/}{(https://www.thewssa.com/)}. The sequence consisted of an upstack phase and a downstack phase using official Speed Stacks cups \href{https://www.speedstacks.com/}{(https://www.speedstacks.com/)}. Participants performed the task using both their hands and had to complete an upstacking and a downstacking phase. The upstacking phase began by completing the first 3 cup pyramid, followed by the 6 cup pyramid, and then the other 3 cup pyramid. The downstacking phase began by returning to and collapsing the 3 cup pyramid that was upstacked first, then the 6 cup pyramid, and finally the last 3 cup pyramid.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

Participants completed two data collection sessions separated by approximately 24 hours. Session 1 consisted of a pre-test and an acquisition phase. Session 2 consisted of a delayed retention test. At the start of each phase of the experiment, all participants received phase-specific instructions (see Data and code availability section). Group specific instructions were provided prior to the acquisition phase (see Table \ref{tab:table1}). The instructions appeared on a 22-inch computer monitor (1920x1080 resolution) positioned to the right of the participant. Participants followed along as the instructions were read aloud by the researcher.

Each trial began with participants standing at a standard height table with their hands on marked positions on the table in front of them. The 12 cups were located in upside down stacks of 3-6-3 in front of the participant. Following a ``Get Ready!'' prompt displayed for 1 s on the monitor and a constant foreperiod of 1 s, an audiovisual ``Go-signal'' (green square and a beep tone) was presented. Participants were instructed to start stacking as quickly as possible following the ``Go-signal'' as its presentation initiated the timer. Once the upstack and downstack phases were completed, participants were instructed to press the spacebar on a keyboard located in front of them to stop the timer. If an error occurred (e.g., only completed the upstack phase then stopped the timer, forgot to hit the timer, etc), the experimenter recorded the trial number for later removal.

The pre-test and delayed retention test both consisted of five no-feedback trials. The acquisition phase had 25 trials and was the only phase where the video demonstration could be watched based on group assignment. Participants in the Self-Controlled group could decide at the start of each trial if they wanted to watch the video demonstration. If they chose to watch the video, they were then asked whether they wanted to watch it in real-time or slow motion (35\% of real-time). The real-time video was 6 s in duration and the slow motion version was 18 s. To ensure a constant viewing period of 18 s, a blank screen was shown for 12 s following the end of the real-time video. If they chose not to watch the video, a blank screen was shown for 18 s. Participants in the Traditional Yoked and Explicit Yoked groups received the demonstration schedule created by a participant in the Self-Controlled group with the exception that participants in the Explicit Yoked group were made aware that this schedule was created by another participant. Feedback about stacking time (s) was displayed for 2 s after every acquisition trial.

To test predictions based on the ``OPTIMAL'' theory regarding the role of motivation, enhanced expectancies, and autonomy-support, participants completed the interest/enjoyment and perceived competence subscales from the Intrinsic Motivation Inventory (McAuley et al., 1989) and a custom scale regarding choice used in previous self-controlled motor learning experiments (Barros et al., 2019; Carter \& Ste-Marie, 2017b). The order of questions from each scale were randomized and each question was rated using a 7-point Likert scale. Participants answered these questions after the pre-test, after trials five and 25 of acquisition, and before the delayed retention test.

A custom LabVIEW (National Instruments Inc.) program was created that controlled the presentation of all instructions, the video demonstrations, the timing of the experimental protocol, and recorded and stored the data for later analysis.

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

Our primary outcome measure was stacking time (i.e., response time) in seconds. Trials recorded as errors \((76/5250 = 1.45\%)\) during data collection were manually removed prior to data analysis. For each participant, pre-test and delayed retention trials were aggregated into one block of five trials and acquisition was aggregated into five blocks of five trials. Significance level was set to 0.05 for all statistical tests. Effect sizes for omnibus tests are reported using generalized eta squared \((\eta^2_{G})\) or eta squared \((\eta^2)\). Post hoc comparisons were conducted using Holm's correction. A Cook's distance of \(\geq 1\) was used to identify any influential cases.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{pre-registered-analysis}{%
\subsection{Pre-registered analysis}\label{pre-registered-analysis}}

To test whether delayed retention (Figure \ref{fig:fig1}C) was differentially impacted by the experimental group (i.e., Self-Controlled, Traditional Yoked, Explicit Yoked) experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test. As can be seen, the Self-Controlled group \((M = 9.99\), \(95\%CI = [9.68,10.31])\), the Traditional Yoked group \((M = 10.18\), \(95\%CI = [9.86,10.50])\), and the Explicit Yoked group \((M = 10.12\), \(95\%CI = [9.81,10.44])\) all had similar stacking times in retention (means are shown as the adjusted means controlling for pre-test). The effect of Group was not significant, \(F(2,146) = .335\), \(p = .716\), \(\eta^2 = .002\).

\begin{figure*}

{\centering \includegraphics[width=1\linewidth,height=1\textheight]{../../figs/fig1}

}

\caption{Physical performance data of the experiment. The Self-Controlled group is shown in red with solid lines and/or circles, the Traditional Yoked group is shown in blue with dotted and/or triangles, and the Explicit Yoked group is shown in orange with dashed and/or squares. \textbf{A}. Trial-by-trial stacking time (s) data averaged across participants within each group (shaded area represents standard error). Splits between line segments denote the end of one phase and the start of the next. Pre-test (Trials 1 to 5) and Acquisition (Trials 6 to 30) occurred on Day 1 and Retention (Trials 31 to 35) occurred on Day 2, approximately 24-hours later. \textbf{B}. Mean stacking time (s) for each group was computed by averaging the data from \textbf{A} into 7 blocks of trials. Error bars represent 95\% confidence intervals. Splits between line segments denote the end of one phase and the start of the next. \textbf{C}. Mean stacking time (s) adjusted for pre-test for each group. Error bars represent 95\% confidence intervals. \textbf{D}. Scatterplot showing the relationship between each participant's mean stacking time (s) in pre-test and retention.}\label{fig:fig1}
\end{figure*}

\begin{table*}[t]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:table2}The mean frequencies for each acquisition block of requesting to watch the video demonstration and choosing the regular viewing speed.}

\begin{tabular}{llllll}
\toprule
  & Block 1 & Block 2 & Block 3 & Block 4 & Block 5\\
\midrule
Model viewing frequency & 32.6\% & 16.9\% & 12.0\% & 12.9\% & 9.3\%\\
 &  &  &  &  & \\
Regular speed frequency & 33.8\% & 38.1\% & 50.0\% & 34.4\% & 30.4\%\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table*}

\hypertarget{non-pre-registered-analyses}{%
\subsection{Non pre-registered analyses}\label{non-pre-registered-analyses}}

\hypertarget{traditional-self-controlled-learning-advantage}{%
\subsubsection{Traditional self-controlled learning advantage}\label{traditional-self-controlled-learning-advantage}}

To investigate whether a traditional self-controlled learning advantage existed---that is a comparison between the Self-Controlled and Traditional Yoked groups---we analyzed the non-adjusted retention scores using a Welch's \emph{t}-test. The analysis revealed that the Self-Controlled group \((M = 9.77\), \(95\%CI = [9.55,9.99])\) and the Traditional Yoked group \((M = 10.20\), \(95\%CI = [9.92,10.49])\) were not statistically different, \(t(88.10) = 1.45\), \(p = .15\), \(g = .29\).

\hypertarget{acquisition-phase}{%
\subsubsection{Acquisition phase}\label{acquisition-phase}}

Model frequency and the video speed request data are reported in Table \ref{tab:table2}. The mean frequency of viewing the video demonstration during acquisition was \(16.7\%\). When a video demonstration was selected, the mean frequency that the regular speed was selected was \(37.3\%\). Stacking time for each Group decreased across acquisition trials (Figure \ref{fig:fig1}A) and blocks (Figure \ref{fig:fig1}B). A 3 Group x 5 Block mixed ANOVA with repeated measures on Block revealed a significant Block effect, \(F(3.63,533.79) = 116.73\), \(p < .001\), \(\eta^2_{G} = .133\). Post hoc comparisons revealed all acquisition blocks were significantly different from each other. Both the Group effect, \(F(2,147) = .738\), \(p = .48\), \(\eta^2_{G} = .008\), and Group x Block interaction, \(F(7.26,533.79) = .543\), \(p = .802\), \(\eta^2_{G} = .001\), were not statistically significant.

\hypertarget{perceived-autonomy}{%
\subsubsection{Perceived autonomy}\label{perceived-autonomy}}

Self-reported perceived autonomy scores are displayed in Figure \ref{fig:fig2}A where it can be seen that the Self-Controlled group reported slightly higher scores compared to the two Yoked groups at all time points following the pre-test. A 3 Group x 3 Time ANCOVA controlling for pre-test revealed a significant Group effect, \(F(2,146) = 8.04\), \(p < .001\), \(\eta^2_{G} = .083.\) Post hoc comparisons on the adjusted means revealed that the Self-Controlled group \((M = 5.61\), \(95\%CI =[5.42,5.80])\) had significantly higher perceptions of autonomy compared to both the Traditional Yoked group \((M = 5.13\), \(95\%CI = [4.94,5.32])\) and the Explicit Yoked group \((M = 5.13\), \(95\%CI = [4.94,5.32])\), which did not differ from each other (and were, in fact, identical to two decimal places). Both the Time effect, \(F(1.61,234.98) = .867\), \(p = .400\), \(\eta^2_{G} = .001\), and Group x Time interaction, \(F(3.22,234.98) = 2.10\), \(p = .096\), \(\eta^2_{G} = .005\), were not significant.

\hypertarget{intrinsic-motivation}{%
\subsubsection{Intrinsic motivation}\label{intrinsic-motivation}}

Self-reported intrinsic motivation scores can be found in Figure \ref{fig:fig2}B. At each time point, all groups reported similar scores on the interest/enjoyment subscale. A 3 Group x 3 Time ANCOVA controlling for pre-test revealed non-significant effects for Group, \(F(2,146) = 2.08\), \(p = .129\), \(\eta^2_{G} = .024\), Time, \(F(1.68,245.73) = .563\), \(p = .541\), \(\eta^2_{G} = .001\), and the Group x Time interaction, \(F(3.37,245.73) = .333\), \(p = .824\), \(\eta^2_{G} = .001\).

\hypertarget{perceived-competence}{%
\subsubsection{Perceived competence}\label{perceived-competence}}

The scores from the perceived competence subscale at each time point are displayed in Figure \ref{fig:fig2}C. As can be seen, perceived competence scores showed a modest increase over time followed by a slight decrease before the delayed retention test. A 3 Group x 3 Time ANCOVA controlling for pre-test showed an effect of Time, \(F(1.75,255.22) = 10.60\), \(p < .001\), \(\eta^2_{G} = .015\). Post hoc tests on adjusted means revealed that scores were rated as significantly higher at the end of acquisition \((M = 3.98\), \(95\%CI = [3.67,3.89])\) and before retention \((M = 3.78\), \(95\%CI = [3.67,3.89])\) compared to after trial 5 \((M = 3.60\), \(95\%CI = [3.49,3.71])\). However, perceived competence was significantly lower before retention compared to the end of acquisition. No significant effect of Group, \(F(2,146) = 2.65\), \(p = .074\), \(\eta^2_{G} = .028\), or Group x Time interaction, \(F(3.50,255.22) = .549\), \(p = .677\), \(\eta^2_{G} = .002\), was found.

\hypertarget{equivalence-tests}{%
\subsubsection{Equivalence tests}\label{equivalence-tests}}

To further probe our null effects (Harms \& Lakens, 2018) related to our main predictions, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure (Lakens et al., 2018; Schuirmann, 1987). To establish our smallest effect size of interest (Lakens, 2021) we calculated the effect size our design had 33\% power to detect (Simonsohn, 2015), which was \(d_{s} = .31\). The Self-Controlled and Traditional Yoked groups were not statistically different, \(t(97.99) = -0.830\), \(p = 0.409\), and not statistically equivalent, \(t(97.99) = 0.720\), \(p = 0.237\), given equivalence bounds of \(-.355\) and \(.355\) (on a raw scale). Similarly, the Traditional Yoked and Explicit Yoked groups were not statistically different, \(t(97.99) = 0.262\), \(p = 0.794\), and not statistically equivalent, \(t(97.99) = -1.288\), \(p = 0.100\), given equivalence bounds of \(-.355\) and \(.355\) (on a raw scale).

\begin{figure*}

{\centering \includegraphics[width=0.85\linewidth,height=0.85\textheight]{../../figs/fig2}

}

\caption{Questionnaire data. Groups means for \textbf{A} perceived autonomy, \textbf{B} intrinsic motivation, and \textbf{C} perceived competence after pre-test, trial 5, and trial 25 on Day 1, and before retention on Day 2. The Self-Controlled group is shown in red circles, the Traditional Yoked group is shown in blue triangles, and the Explicit Yoked group is shown in orange squares. Dots represent individual participants in each group. Scores could range from 1 (Strongly disagree) to 7 (Strongly agree). Error bars represent 95\% confidence intervals.}\label{fig:fig2}
\end{figure*}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

It has been argued that self-controlled practice conditions are effective for motor learning because they are autonomy-supportive in nature (Wulf \& Lewthwaite, 2016). Yet, this claim has received, at best, modest support in the motor learning literature (e.g., McKay \& Ste-Marie, 2020a; but see Barros et al., 2019; Carter \& Ste-Marie, 2017b; Ste-Marie et al., 2013 for non-support). Here, we addressed a possible methodological limitation for this lack of support. That is, in previous self-controlled motor learning research, participants in the yoked group are not made aware that they have been denied opportunities to exercise choice over a practice variable such as feedback or watching a modeled demonstration. In the present experiment we introduced a novel yoked group that was explicitly told that the observation schedule---frequency and speed of video---they would receive during practice was actually one created by another participant in the experiment. Contrary to our prediction, the Explicit Yoked group did not report significantly lower perceived autonomy scores than the Traditional Yoked group, which was only informed their observation schedule was predetermined. In line with the ``OPTIMAL'' theory (Wulf \& Lewthwaite, 2016), the Self-Controlled group reported significantly higher perceived autonomy-support than both the Traditional and Explicit Yoked groups. However, this boost in perceived autonomy did not lead to enhanced motor performance or learning. These findings from a well-powered experiment are difficult to reconcile with a core pillar of the ``OPTIMAL'' theory of motor learning.

\hypertarget{self-controlled-practice-conditions-as-autonomy-supportive}{%
\subsection{Self-controlled practice conditions as autonomy-supportive}\label{self-controlled-practice-conditions-as-autonomy-supportive}}

A common problem with many of the self-controlled or choice motor learning literature claiming autonomy-support as an underlying mechanism for self-controlled learning advantages is a failure to include measures that actually test this claim (e.g., Chiviacowsky, 2014; Chiviacowsky et al., 2012; Lewthwaite et al., 2015). Instead, this link to autonomy-support is merely assumed based on the provision of choice to one group of participants versus not giving the same choice to another group of participants. As noted earlier, an issue with this assumption is that within the practice environment itself, there are myriad opportunities for participants, independent of group, to exercise choice. In throwing tasks common to motor learning, participants can explore the task workspace by attempting different throwing techniques. In more lab-based tasks that consist of multiple spatial and timing goals (e.g., waveform matching), participants can choose a single goal to focus on and master before shifting their attention to another goal. Commensurate with this idea, Ste-Marie et al. (2013) found no differences in perceived choice regarding the motor task being learned between their self-controlled and yoked groups, despite the self-controlled group showing enhanced retention. This may explain why research has consistently reported perceived autonomy scores that do not differ significantly between self-controlled and yoked groups (Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020b).

Another possible explanation for the finding that being in a self-controlled group has not been perceived as more autonomy-supportive than being in a yoked group is that choice is typically provided over a single element of the practice variable, such as the frequency of receiving feedback (e.g., Aiken et al., 2012; Carter \& Ste-Marie, 2017a) or the level of task difficulty (Andrieux et al., 2012; Leiker et al., 2016). Control or choice over a single dimension may not be strong enough to elicit a large enough boost in perceived autonomy above and beyond that of being able to explore one's task workspace as mentioned above. Thus, to increase the saliency of the self-controlled manipulation in the present experiment, we gave the self-controlled participants control over two elements of their observation schedule: viewing frequency and video playback speed. Having control of these two dimensions resulted in higher perceptions of autonomy in our Self-Controlled group compared to the Traditional and Explicit Yoked groups. This may explain the inconsistency with past research failing to find this effect (Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020b; Ste-Marie et al., 2013). However, McKay and Ste-Marie (2020a) recently found that choice over a single element increased perceived autonomy, but similar to our data they also did not find this led to increased learning. Thus, it is unclear whether the higher autonomy scores in the present experiment can in fact be attributed to having control over multiple elements of one's observation schedule.

In a similar vein, past research has also suggested that self-controlled learning benefits are not dependent on the amount of choice opportunities over a single element (Patterson et al., 2011). Given these findings, we argue that the most likely explanation for the inconsistency surrounding the effect of self-controlled practice being autonomy-supportive is that this effect is quite small, and the designs of previous experiments have lacked the statistical power to reliability detect this effect. These experiments have had sample sizes of 20 participants or less per group, whereas there were 50 participants in each group in the present experiment and 64 per group (when collapsed across constant and variable practice schedules) in McKay and Ste-Marie (2020a). Collapsing across our two yoked groups, we estimate an effect of autonomy-support of \(g = .197\) whereas the estimate from McKay and Ste-Marie (2020a) was \(g = .57\). Regardless of the estimated size of the effect for autonomy-support through a self-controlled practice condition, a larger issue and challenge to the ``OPTIMAL'' theory is that significantly higher perceptions of autonomy did not result in superior performance in either acquisition or delayed retention (Wulf \& Lewthwaite, 2016).

\hypertarget{no-learning-advantage-from-a-self-controlled-observation-schedule}{%
\subsection{No learning advantage from a self-controlled observation schedule}\label{no-learning-advantage-from-a-self-controlled-observation-schedule}}

The delayed retention results in the present experiment not only are inconsistent with numerous past experiments reporting a self-controlled motor learning benefit (for a review see Ste-Marie et al., 2019), but also the general consensus that the self-controlled learning advantage is a robust effect (Wulf \& Lewthwaite, 2016). Of late, however, there has been an increase in the number of papers reporting a failure to detect the so-called self-controlled learning advantage (e.g., Barros et al., 2019; Grand et al., 2017; McKay \& Ste-Marie, 2020a, 2020b). This recent lack of support may arise from the self-controlled learning advantage being a much smaller effect than originally estimated (\(g = 0.63\) by McKay et al.~2014). A more recent estimate of this effect from a meta-analysis using a weight-function model was \(g = .11, \,95\% CI = [.047, .18]\) (McKay et al., 2021). This estimate was further reduced to \(g = .054\) after controlling for publication bias using the precision-effect estimate with standard error (PEESE) method. Thus, both models seem to suggest a trivial effect for self-controlled learning. Additional simulations included in the meta-analysis provided plausible effect size estimates ranging from \(g = -.11\) to \(.26\) (i.e., it could even favour being in the yoked group). In our experiment, the estimated effect size of self-controlled versus yoked (collapsed across our Traditional and Explicit Yoked groups) was \(g = 0.22\). While this estimate is larger than those from the weight-function model and PEESE method, it does fall within the range of plausible effect sizes (McKay et al., 2021). When the lack of a self-controlled advantage in previous work and our current experiment are contextualized within the findings of this recent meta-analysis, it is not as surprising that the so-called self-controlled learning benefit was not replicated.

Despite the large sample size of the present experiment (\emph{n}/group = 50) versus the typical self-controlled motor learning experiment (median \emph{n}/group = 18 based on the experiments included in the meta-analysis by McKay et al.~2021), the results of the primary analysis and the equivalence tests remain inconclusive. This, along with the effect size estimates in the recent meta-analysis, suggest enormous sample sizes are required to reliably detect an effect of a self-controlled learning advantage. Using the upper bound, \(g = .26\), of the range of plausible effects, \emph{253 participants} are required to have 80\% power to detect this effect in retention using an independent-samples \emph{t}-test. The number of participants jumps to \emph{1300 per group}, if for instance the estimate from the weight-function model, \(g = .11\), is accurate (McKay et al., 2021). Given the field of motor learning suffers from a lack of adequately powered designs (Lohse et al., 2016) and that underpowered designs are more likely to produce false positives and overestimated effect sizes (Button et al., 2013), we are skeptical of the replicability of the previous overwhelming support for the self-controlled learning advantage.

\hypertarget{lack-of-support-for-key-predictions-of-the-optimal-theory-of-motor-learning}{%
\subsection{Lack of support for key predictions of the ``OPTIMAL'' theory of motor learning}\label{lack-of-support-for-key-predictions-of-the-optimal-theory-of-motor-learning}}

Within the ``OPTIMAL'' theory (Wulf \& Lewthwaite, 2016), it is predicted that practice conditions that promote autonomy-support and enhance expectancies contribute to a virtuous cycle that leads to superior motor performance and learning. In other words, significant group differences between self-controlled and yoked groups would be expected on measures related to these psychological constructs. As mentioned earlier, we found higher perceptions of autonomy-support in our Self-Controlled group relative to the Traditional and Explicit Yoked groups; however, this did not enhance motor learning as predicted within the virtuous cycle. Contrary to the ``OPTIMAL'' theory, we did not find an effect of group for perceived competence (i.e., enhanced expectancies) or intrinsic motivation. Perceived competence scores did increase across acquisition blocks, which mirrors the improved motor performance seen throughout acquisition. These results are in line with results of a path analysis that suggested self-efficacy (i.e., enhanced expectancies) and intrinsic motivation were insufficient to explain self-controlled learning benefits (Ste-Marie et al., 2016). Overall, our results are inconsistent with key predictions of the ``OPTIMAL'' theory regarding autonomy-support and enhanced expectancies, and further question the causal role such manipulations play in motor learning.

In sum, we found that being able to control two aspects of one's observation schedule during practice was perceived as autonomy-supportive relative to not having this same control opportunity. However, making participants in an Explicit Yoked group aware they would be denied a control opportunity during practice did not decrease perceptions of autonomy relative to participants in the Traditional Yoked group. Furthermore, we did not find evidence than an autonomy-supportive manipulation had any direct causal effect on learning and we also failed to replicate the typical self-controlled learning advantage. It is worth noting that in some situations autonomy-support in and of itself might be a desired affective outcome (Ste-Marie et al., 2020). In such circumstance, providing learners with choice opportunities may be a useful motivationally-protective outcome. However, such a tool should be used judiciously as it is typically motor outcomes in the form of relatively permanent performance changes that is the true goal of any motor learning intervention (Ste-Marie et al., 2020). Ultimately, our results add to a growing body of evidence that questions whether autonomy-supportive manipulations directly affect learning. One explanation for this lack of replicability is that the \emph{``true''} effect of such manipulations are much smaller than previously estimated (McKay et al., 2021). Given the resources required (in terms of sample size) to reliably detect the tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either studying practice conditions that have much bigger effects or devising ways to reduce variability and increase power through clever experimental design (McClelland, 2000).

\hypertarget{conflict-of-interest}{%
\section{Conflict of interest}\label{conflict-of-interest}}

The authors declare no competing interests.

\hypertarget{funding}{%
\section{Funding}\label{funding}}

This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC). LSG was also supported by an NSERC PGS-D scholarship.

\hypertarget{data-and-code-availability}{%
\section{Data and code availability}\label{data-and-code-availability}}

All material, data, and scripts to reproduce our analyses and figures can be accessed here: \url{https://github.com/cartermaclab/expt_explicit-yoked}.

\hypertarget{r-packages-used-in-this-project}{%
\section{R packages used in this project}\label{r-packages-used-in-this-project}}

R {[}Version 4.0.5; R Core Team (2021){]} and the R-packages \emph{cowplot} {[}Version 1.1.1; Wilke (2020){]}, \emph{jmv} {[}Version 1.2.23; Selker et al. (2020){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{pwr} {[}Version 1.3.0; Champely (2020){]}, \emph{tidyverse} {[}Version 1.3.1; Wickham et al. (2019){]}, and \emph{TOSTER} {[}Version 0.3.4; Lakens (2017){]}.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\interlinepenalty = 10000
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\endgroup

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-abdollahipour2017}{}%
Abdollahipour, R., Palomo Nieto, M., Psotta, R., \& Wulf, G. (2017). External focus of attention and autonomy support have additive benefits for motor performance in children. \emph{Psychology of Sport and Exercise}, \emph{32}, 17--24. \url{https://doi.org/10.1016/j.psychsport.2017.05.004}

\leavevmode\hypertarget{ref-aiken2012}{}%
Aiken, C. A., Fairbrother, J. T., \& Post, P. G. (2012). The effects of self-controlled video feedback on the learning of the basketball set shot. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00338}

\leavevmode\hypertarget{ref-altman1995}{}%
Altman, D. G., \& Bland, J. M. (1995). Statistics notes: Absence of evidence is not evidence of absence. \emph{BMJ}, \emph{311}(7003), 485. \url{https://doi.org/10.1136/bmj.311.7003.485}

\leavevmode\hypertarget{ref-andrieux2012}{}%
Andrieux, M., Danna, J., \& Thon, B. (2012). Self-control of task difficulty during training enhances motor learning of a complex coincidence-anticipation task. \emph{Research Quarterly for Exercise and Sport}, \emph{83}(1), 27--35. \url{https://doi.org/10.1080/02701367.2012.10599822}

\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-barros2019}{}%
Barros, J. A. C., Yantha, Z. D., Carter, M. J., Hussien, J., \& Ste-Marie, D. M. (2019). Examining the impact of error estimation on the effects of self-controlled feedback. \emph{Human Movement Science}, \emph{63}, 182--198. \url{https://doi.org/10.1016/j.humov.2018.12.002}

\leavevmode\hypertarget{ref-button2013}{}%
Button, K. S., Ioannidis, J. P. A., Mokrysz, C., Nosek, B. A., Flint, J., Robinson, E. S. J., \& Munafò, M. R. (2013). Power failure: why small sample size undermines the reliability of neuroscience. \emph{Nature Reviews Neuroscience}, \emph{14}(5), 365--376. \url{https://doi.org/10.1038/nrn3475}

\leavevmode\hypertarget{ref-carter2014}{}%
Carter, M. J., Carlsen, A. N., \& Ste-Marie, D. M. (2014). Self-controlled feedback is effective if it is based on the learner{'}s performance: A replication and extension of chiviacowsky and wulf (2005). \emph{Frontiers in Psychology}, \emph{5}. \url{https://doi.org/10.3389/fpsyg.2014.01325}

\leavevmode\hypertarget{ref-carter2017b}{}%
Carter, M. J., \& Ste-Marie, D. M. (2017a). An interpolated activity during the knowledge-of-results delay interval eliminates the learning advantages of self-controlled feedback schedules. \emph{Psychological Research}, \emph{81}(2), 399--406. \url{https://doi.org/10.1007/s00426-016-0757-2}

\leavevmode\hypertarget{ref-carter2017a}{}%
Carter, M. J., \& Ste-Marie, D. M. (2017b). Not all choices are created equal: Task-relevant choices enhance motor learning compared to task-irrelevant choices. \emph{Psychonomic Bulletin \& Review}, \emph{24}(6), 1879--1888. \url{https://doi.org/10.3758/s13423-017-1250-7}

\leavevmode\hypertarget{ref-R-pwr}{}%
Champely, S. (2020). \emph{Pwr: Basic functions for power analysis}. \url{https://CRAN.R-project.org/package=pwr}

\leavevmode\hypertarget{ref-chiviacowsky2014}{}%
Chiviacowsky, S. (2014). Self-controlled practice: Autonomy protects perceptions of competence and enhances motor learning. \emph{Psychology of Sport and Exercise}, \emph{15}(5), 505--510. \url{https://doi.org/10.1016/j.psychsport.2014.05.003}

\leavevmode\hypertarget{ref-chiviacowsky2005}{}%
Chiviacowsky, S., \& Wulf, G. (2005). Self-controlled feedback is effective if it is based on the learner's performance. \emph{Research Quarterly for Exercise and Sport}, \emph{76}(1), 42--48. \url{https://doi.org/10.1080/02701367.2005.10599260}

\leavevmode\hypertarget{ref-chiviacowsky2002}{}%
Chiviacowsky, S., \& Wulf, G. (2002). Self-controlled feedback: Does it enhance learning because performers get feedback when they need it? \emph{Research Quarterly for Exercise and Sport}, \emph{73}(4), 408--415. \url{https://doi.org/10.1080/02701367.2002.10609040}

\leavevmode\hypertarget{ref-chiviacowsky2012}{}%
Chiviacowsky, S., Wulf, G., \& Lewthwaite, R. (2012). Self-controlled learning: The importance of protecting perceptions of competence. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00458}

\leavevmode\hypertarget{ref-chua2018}{}%
Chua, L.-K., Wulf, G., \& Lewthwaite, R. (2018). Onward and upward: Optimizing motor performance. \emph{Human Movement Science}, \emph{60}, 107--114. \url{https://doi.org/10.1016/j.humov.2018.05.006}

\leavevmode\hypertarget{ref-deci2000}{}%
Deci, E. L., \& Ryan, R. M. (2000). The {"}what{"} and {"}why{"} of goal pursuits: Human needs and the self-determination of behavior. \emph{Psychological Inquiry}, \emph{11}(4), 227--268. \url{https://doi.org/10.1207/S15327965PLI1104_01}

\leavevmode\hypertarget{ref-grand2015}{}%
Grand, K. F., Bruzi, A. T., Dyke, F. B., Godwin, M. M., Leiker, A. M., Thompson, A. G., Buchanan, T. L., \& Miller, M. W. (2015). Why self-controlled feedback enhances motor learning: Answers from electroencephalography and indices of motivation. \emph{Human Movement Science}, \emph{43}, 23--32. \url{https://doi.org/10.1016/j.humov.2015.06.013}

\leavevmode\hypertarget{ref-grand2017}{}%
Grand, K. F., Daou, M., Lohse, K. R., \& Miller, M. W. (2017). Investigating the Mechanisms Underlying the Effects of an Incidental Choice on Motor Learning. \emph{Journal of Motor Learning and Development}, \emph{5}(2), 207--226. \url{https://doi.org/10.1123/jmld.2016-0041}

\leavevmode\hypertarget{ref-hansen2011}{}%
Hansen, S., Pfeiffer, J., \& Patterson, J. T. (2011). Self-control of feedback during motor learning: Accounting for the absolute amount of feedback using a yoked group with self-control over feedback. \emph{Journal of Motor Behavior}, \emph{43}(2), 113--119. \url{https://doi.org/10.1080/00222895.2010.548421}

\leavevmode\hypertarget{ref-harms2018}{}%
Harms, C., \& Lakens, D. (2018). Making 'null effects' informative: Statistical techniques and inferential frameworks. \emph{Journal of Clinical and Translational Research}. \url{https://doi.org/10.18053/jctres.03.2017S2.007}

\leavevmode\hypertarget{ref-janelle1997}{}%
Janelle, C. M., Barba, D. A., Frehlich, S. G., Tennant, L. K., \& Cauraugh, J. H. (1997). Maximizing performance feedback effectiveness through videotape replay and a self-controlled learning environment. \emph{Research Quarterly for Exercise and Sport}, \emph{68}(4), 269--279. \url{https://doi.org/10.1080/02701367.1997.10608008}

\leavevmode\hypertarget{ref-lakens2021}{}%
Lakens, D. (2021). \emph{Sample size justification}. \url{https://doi.org/10.31234/osf.io/9d3yf}

\leavevmode\hypertarget{ref-R-TOSTER}{}%
Lakens, D. (2017). Equivalence tests: A practical primer for t-tests, correlations, and meta-analyses. \emph{Social Psychological and Personality Science}, \emph{1}, 1--8. \url{https://doi.org/10.1177/1948550617697177}

\leavevmode\hypertarget{ref-lakens2018}{}%
Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence Testing for Psychological Research: A Tutorial. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269. \url{https://doi.org/10.1177/2515245918770963}

\leavevmode\hypertarget{ref-leiker2016}{}%
Leiker, A. M., Bruzi, A. T., Miller, M. W., Nelson, M., Wegman, R., \& Lohse, K. R. (2016). The effects of autonomous difficulty selection on engagement, motivation, and learning in a motion-controlled video game task. \emph{Human Movement Science}, \emph{49}, 326--335. \url{https://doi.org/10.1016/j.humov.2016.08.005}

\leavevmode\hypertarget{ref-lewthwaite2015}{}%
Lewthwaite, R., Chiviacowsky, S., Drews, R., \& Wulf, G. (2015). Choose to move: The motivational impact of autonomy support on motor learning. \emph{Psychonomic Bulletin \& Review}, \emph{22}(5), 1383--1388. \url{https://doi.org/10.3758/s13423-015-0814-7}

\leavevmode\hypertarget{ref-lohse2016}{}%
Lohse, K., Buchanan, T., \& Miller, M. (2016). Underpowered and Overworked: Problems With Data Analysis in Motor Learning Studies. \emph{Journal of Motor Learning and Development}, \emph{4}(1), 37--58. \url{https://doi.org/10.1123/jmld.2015-0010}

\leavevmode\hypertarget{ref-mcauley1989}{}%
McAuley, E., Duncan, T., \& Tammen, V. V. (1989). Psychometric properties of the intrinsic motivation inventory in a competitive sport setting: A confirmatory factor analysis. \emph{Research Quarterly for Exercise and Sport}, \emph{60}(1), 48--58. \url{https://doi.org/10.1080/02701367.1989.10607413}

\leavevmode\hypertarget{ref-mcclelland2000}{}%
McClelland, G. H. (2000). Increasing statistical power without increasing sample size. \emph{American Psychologist}, \emph{55}(8), 963--964. https://doi.org/\url{https://psycnet.apa.org/doi/10.1037/0003-066X.55.8.963}

\leavevmode\hypertarget{ref-mckay2014}{}%
McKay, B., Carter, M. J., \& Ste-Marie, D. M. (2014). Self-controlledlearning: A meta-analysis. \emph{Journal of Sport \& Exercise Psychology,} \emph{36}, S43.

\leavevmode\hypertarget{ref-mckay2020a}{}%
McKay, B., \& Ste-Marie, D. M. (2020a). Autonomy support via instructionally irrelevant choice not beneficial for motor performance or learning. \emph{Research Quarterly for Exercise and Sport}, \emph{0}(0), 1--13. \url{https://doi.org/10.1080/02701367.2020.1795056}

\leavevmode\hypertarget{ref-mckay2020b}{}%
McKay, B., \& Ste-Marie, D. M. (2020b). Autonomy support and reduced feedback frequency have trivial effects on learning and performance of a golf putting task. \emph{Human Movement Science}, \emph{71}(1026124). \url{https://doi.org/10.1016/j.humov.2020.102612}

\leavevmode\hypertarget{ref-mckay2021}{}%
McKay, B., Yantha, Z. D., Hussien, J., Carter, M. J., \& Ste-Marie, D. M. (2021). \emph{Meta-analytic findings in the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value}. \url{https://doi.org/10.31234/osf.io/8d3nb}

\leavevmode\hypertarget{ref-patterson2010}{}%
Patterson, J. T., \& Carter, M. (2010). Learner regulated knowledge of results during the acquisition of multiple timing goals. \emph{Human Movement Science}, \emph{29}(2), 214--227. \url{https://doi.org/10.1016/j.humov.2009.12.003}

\leavevmode\hypertarget{ref-patterson2011}{}%
Patterson, J. T., Carter, M., \& Sanli, E. (2011). Decreasing the proportion of self-control trials during the acquisition period does not compromise the learning advantages in a self-controlled context. \emph{Research Quarterly for Exercise and Sport}, \emph{82}(4), 624--633. \url{https://doi.org/10.1080/02701367.2011.10599799}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2021). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-sanli2013}{}%
Sanli, E. A., Patterson, J. T., Bray, S. R., \& Lee, T. D. (2013). Understanding self-controlled motor learning protocols through the self-determination theory. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00611}

\leavevmode\hypertarget{ref-schuirmann1987}{}%
Schuirmann, D. J. (1987). A comparison of the Two One-Sided Tests Procedure and the Power Approach for assessing the equivalence of average bioavailability. \emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{15}(6), 657--680. \url{https://doi.org/10.1007/BF01068419}

\leavevmode\hypertarget{ref-R-jmv}{}%
Selker, R., Love, J., \& Dropmann, D. (2020). \emph{Jmv: The 'jamovi' analyses}. \url{https://CRAN.R-project.org/package=jmv}

\leavevmode\hypertarget{ref-simmons2012}{}%
Simmons, J. P., Nelson, L. D., \& Simonsohn, U. (2012). \emph{A 21 Word Solution}. \url{https://doi.org/10.2139/ssrn.2160588}

\leavevmode\hypertarget{ref-simonsohn2015}{}%
Simonsohn, U. (2015). Small Telescopes: Detectability and the Evaluation of Replication Results. \emph{Psychological Science}, \emph{26}(5), 559--569. \url{https://doi.org/10.1177/0956797614567341}

\leavevmode\hypertarget{ref-ste-marie2016}{}%
Ste-Marie, D. M., Carter, M. J., Law, B., Vertes, K., \& Smith, V. (2016). Self-controlled learning benefits: Exploring contributions of self-efficacy and intrinsic motivation via path analysis. \emph{Journal of Sports Sciences}, \emph{34}(17), 1650--1656. \url{https://doi.org/10.1080/02640414.2015.1130236}

\leavevmode\hypertarget{ref-ste-marie2019}{}%
Ste-Marie, D. M., Carter, M. J., \& Yantha, Z. D. (2019). \emph{Self-controlled learning: Current findings, theoretical perspectives, and future directions} (3rd ed.). Routledge.

\leavevmode\hypertarget{ref-ste-marie2020}{}%
Ste-Marie, D. M., Lelievre, N., \& Germain, L. S. (2020). Revisiting the applied model for the use of observation: A review of articles spanning 2011{{}}2018. \emph{Research Quarterly for Exercise and Sport}, \emph{91}(4), 594--617. \url{https://doi.org/10.1080/02701367.2019.1693489}

\leavevmode\hypertarget{ref-ste-marie2013}{}%
Ste-Marie, D. M., Vertes, K. A., Law, B., \& Rymal, A. M. (2013). Learner-controlled self-observation is advantageous for motor skill acquisition. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00556}

\leavevmode\hypertarget{ref-R-tidyverse}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T. L., Miller, E., Bache, S. M., Müller, K., Ooms, J., Robinson, D., Seidel, D. P., Spinu, V., \ldots{} Yutani, H. (2019). Welcome to the {tidyverse}. \emph{Journal of Open Source Software}, \emph{4}(43), 1686. \url{https://doi.org/10.21105/joss.01686}

\leavevmode\hypertarget{ref-R-cowplot}{}%
Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. \url{https://CRAN.R-project.org/package=cowplot}

\leavevmode\hypertarget{ref-wu2011}{}%
Wu, W. F. W., \& Magill, R. A. (2011). Allowing learners to choose. \emph{Research Quarterly for Exercise and Sport}, \emph{82}(3), 449--457. \url{https://doi.org/10.1080/02701367.2011.10599777}

\leavevmode\hypertarget{ref-wulf2016}{}%
Wulf, G., \& Lewthwaite, R. (2016). Optimizing performance through intrinsic motivation and attention for learning: The OPTIMAL theory of motor learning. \emph{Psychonomic Bulletin \& Review}, \emph{23}(5), 1382--1414. \url{https://doi.org/10.3758/s13423-015-0999-9}

\leavevmode\hypertarget{ref-wulf2018}{}%
Wulf, G., Lewthwaite, R., Cardozo, P., \& Chiviacowsky, S. (2018). Triple play: Additive contributions of enhanced expectancies, autonomy support, and external attentional focus to motor learning. \emph{Quarterly Journal of Experimental Psychology}, \emph{71}(4), 824--831. \url{https://doi.org/10.1080/17470218.2016.1276204}

\leavevmode\hypertarget{ref-wulf2005}{}%
Wulf, G., Raupach, M., \& Pfeiffer, F. (2005). Self-controlled observational practice enhances learning. \emph{Research Quarterly for Exercise and Sport}, \emph{76}(1), 107--111. \url{https://doi.org/10.1080/02701367.2005.10599266}

\end{CSLReferences}

\end{document}

### 2021-05-20 docs/submission/manuscript.Rmd
init

---
title             : "Increased perceptions of autonomy through choice fail to enhance motor skill retention"
shorttitle        : "Autonomy-support does not benefit motor learning"
author: 
  - name          : "Laura St. Germain"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation - Performed the experiment
      - Methodology
      - Project administration
      - Software - Task Programming
      - Validation
      - Visualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Allison Williams"
    affiliation   : "1"
    role:
      - Investigation - Performed the experiment
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Noura Balbaa"
    affiliation   : "1"
    role:
      - Investigation - Performed the experiment
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Andrew Poskus"
    affiliation   : "1"
    role:
      - Investigation - Performed the experiment
      - Writing - Review & Editing
  - name          : "Olena Leshchyshen"
    affiliation   : "1"
    role:
      - Investigation - Performed the experiment
      - Writing - Review & Editing
  - name          : "Keith R. Lohse"
    affiliation   : "2"
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Methodology
      - Validation
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Michael J. Carter"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1280 Main Street West, Ivor Wynne Centre Room 203, McMaster University, Hamilton ON Canada, L8S 4K1"
    email         : "michaelcarter@mcmaster.ca"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Data curation
      - Formal analysis
      - Funding acquisition
      - Methodology
      - Project administration
      - Resources
      - Software - Task Programming
      - Supervision
      - Validation
      - Visualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Department of Kinesiology, McMaster University"
  - id            : "2"
    institution   : "Program in Physical Therapy, Washington University School of Medicine in Saint Louis"

authornote: |
  \addORCIDlink{Laura St. Germain}{0000-0002-5513-4183}

  \addORCIDlink{Keith R. Lohse}{0000-0002-7643-3887}

  \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}

  We have outlined author contributions using CRediT (Contributor Roles Taxonomy - https://casrai.org/credit/).

abstract: |
  There has been growing research interest in the effects that motivation plays in motor learning, and specifically how autonomy, competence, and social relatedness may directly benefit the learning process. Here, we present a preregistered manipulation of autonomy-support by providing learners with choice during the practice of a speed cup-stacking skill. One group was given control over when a video demonstration was provided and the viewing speed. A yoked control group received an identical demonstration schedule, but without choice (as their schedule was matched to a participant with choice). Critically, we addressed a gap in the literature by adding a yoked group who was explicitly told that they were being denied choice and that their schedule was chosen by another participant. We found no statistically significant learning differences between groups, despite finding evidence that providing choice increased perceived autonomy. Equivalence tests further showed that although the groups were not statistically equivalent, the effect size is likely too small to practically study the effects of autonomy-support through choice in most motor learning labs. These findings add to a growing body of research that questions a causal role of autonomy-support on motor learning, and the robustness of the so-called self-controlled learning advantage.

keywords          : "Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing"
#wordcount         : "4926"
bibliography      : ["../references.bib", "../r-references.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

csl               : "../apa-single-spaced.csl"
documentclass     : "apa7"
classoption       : "man" # man for manuscript & jou for journal
output            : papaja::apa6_pdf
header-includes   :
  - \pagewiselinenumbers
  - \raggedbottom
  - \leftheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
  - \rightheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
  #- \hypersetup{draft} # comment out after but right now will prevent error message about some link spanning multiple pages
---

```{r setup, include = FALSE}
library(papaja)
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

A popular recommendation in recent years for creating an effective environment for motor skill learning has been to allow the learner to take control over an element of their practice that is traditionally controlled by a coach, therapist, or teacher [@sanli2013; @ste-marie2019]. This recommendation is based on the consistent finding that participants in a self-controlled (i.e., choice) group perform with higher proficiency compared to participants in a yoked (i.e., control) group on delayed retention and/or transfer tests. Participants in the yoked group do not experience the same choice opportunity provided to those in the self-controlled group. Instead, they are linked to a self-controlled participant and experience this participant's self-selected practice schedule. This so-called self-controlled learning advantage has been shown when participants are given the opportunity to schedule task difficulty [e.g., @andrieux2012; @leiker2016], the order that multiple tasks are practiced [e.g., @wu2011], the frequency of watching a modeled demonstration [e.g. @wulf2005], and when to receive augmented feedback [e.g., @janelle1997; @patterson2010].

Over the years, this manipulation has been described using a variety of names (e.g., self- and/or learner-controlled; -regulated; -directed; -selected), but more recently it has been subsumed by autonomy-support. In fact, autonomy-support is considered such a robust learning variable that it is one of three key pillars in the recently proposed "OPTIMAL" theory of motor learning [@wulf2016]. @wulf2016 argued that providing learners with opportunities for choice---considered an autonomy-supportive practice manipulation---can facilitate motor performance and learning by enhancing learner's expectancies for success, and by allowing the learner to maintain their attentional focus on the task by reducing the need for self-regulatory activity [@abdollahipour2017; @chua2018; @wulf2018]. In other words, these psychological and attentional benefits, and concomitant increases in performance and learning are a by-product of exercising choice during practice. Overall, autonomy-support is seen as a means to efficient goal-action coupling [@wulf2016] and also links the "OPTIMAL" theory with Self-Determination theory [@deci2000].

Despite its prominent role within the "OPTIMAL" theory of motor learning, there are numerous reasons to doubt the importance of autonomy-support through the provision of choice during practice. First, if the benefits are the result of having opportunities for choice then learning differences should not emerge between different self-controlled groups. However, in experiments where different groups of participants have choice over their feedback schedule, such learning differences have been found, but not limited to, when this choice is made *after* rather than before a performance attempt [@chiviacowsky2005; @carter2014], when different criteria for success are provided to participants [@chiviacowsky2012], and when the absolute number of feedback choice opportunities are limited compared to unlimited at the outset of practice [@hansen2011; @patterson2011]. Second, there has been little-to-no support for the notion that practicing in a self-controlled group is perceived as more autonomy-supportive than being in a yoked group. @ste-marie2013, for example, had participants in the self-controlled and yoked groups complete the perceived choice subscale of the Intrinsic Motivation Inventory and failed to find the expected effect of higher self-reported scores during practice in the self-controlled group. Similar findings have been reported by others [@barros2019; @carter2017a; @mckay2020b]. However, @mckay2020a recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group. This increased perceived autonomy-support did not, however, translate into enhanced learning compared to the yoked group. Although the available literature does not provide substantial evidence that self-controlled practice is autonomy-supportive, this does not necessarily mean such a manipulation is not autonomy-supportive [@altman1995]. For instance, this effect may in fact be quite small and require much larger sample sizes to detect than those commonly used in motor learning experiments [@lohse2016].

There are at least two other methodological issues that warrant consideration. The first of these is that in self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component (e.g., feedback or when to watch a modeled demonstration) of their practice and participants in the yoked group are not given choice over this component. However, within the context of practice itself there are many other opportunities for choice that participants may explore, independent of their assigned group. Target-based tasks such as basketball free throws [e.g., @aiken2012] or bean-bag tossing [@grand2015] are a popular choice in motor learning experiments and have been used in self-controlled learning experiments. While a participant in the yoked group may not be permitted choice over their feedback schedule (or some other practice variable) in these experiments, this does not preclude them from opportunities for choice---and thus autonomy-support---when deciding to try different throwing techniques, speeds, and/or release points. Thus, labeling yoked groups as being devoid of choice opportunities may be a misnomer. The other consideration relates to the instructions that are provided to participants in the yoked group. In the context of feedback[^1], these participants are typically informed that during practice they may or may not receive feedback after a given trial [e.g., @chiviacowsky2002; @patterson2010]. This means that participants in yoked groups are not even aware that they have been denied an opportunity for choice, nor that their feedback schedule was created by another participant who was given choice over when feedback was or was not provided. Either of these in isolation, or both simultaneously could contribute to the consistent finding that participants in self-controlled and yoked groups report similar perceived autonomy scores when asked about their opportunities for choices with respect to the motor task [@ste-marie2013] or about their practice environment in general [@barros2019; @carter2017a; @mckay2020b].

[^1]: While feedback is used in this example, this issue surrounding instructions is also relevant to other practice variables commonly used in self-controlled learning experiments.

```{r table1, echo = FALSE, results = "asis"}

table_1 <- data.frame(c(
  "Self-Controlled",
  "", "",
  "Traditional Yoked",
  "", "",
  "Explicit Yoked", 
  "", ""),
  c(
    "Before each trial, you will be asked whether you wish to watch a modeled demonstration of the task.",
    "If you choose YES, you will then be asked whether you want to watch the video in real-time or in",
    "slow-motion.",

    "Before each trial, you may or may not watch a modeled demonstration of the task based on a pre-",
    "determined schedule. If you observe a model, it might be presented in real-time or in slow-motion",
    "based on the pre-determined schedule.",

    "Before each trial, you may or may not watch a modeled demonstration of the task based on the", 
    "schedule another participant selected. If you observe a model, it might be presented in real-time or in",
    "slow-motion based on what that participant selected."
  )
)

apa_table(table_1, font_size = "scriptsize", col.names = c(" ", "Acquisition instructions"), booktabs = TRUE, span_text_columns = TRUE, caption = "Group specific instructions detailing the observation schedule that would be experienced during Acquisition.")

```

Here we investigated the effects of making participants in a yoked group explicitly aware of not only being denied opportunities for choice over their frequency of watching and the playback speed of video demonstrations, but also that the schedule they would experience during practice was created by another participant in the experiment. The addition of this novel yoked group allowed us to address one of the previously identified methodological limitations regarding experimental group instructions in past self-controlled research. We compared the performance of this explicit yoked group with traditional self-controlled and yoked groups on a speed cup-stacking task in practice and in a delayed retention test.

# Methods

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@simmons2012]. The experimental design and analyses were preregistered using AsPredicted.org and can be viewed here: https://aspredicted.org/ze8cj.pdf.

## Participants

One-hundred and fifty participants completed the experiment. Sample size was determined by an a priori power calculation based on our smallest comparison of interest. An early estimate for the effect of self-controlled over yoked practice was a Hedges' $g = 0.63$ [@mckay2014] and while planning this experiment this effect was estimated to be $g = 0.52$ (Z. Yantha, personal communication, October 2019). Based on this effect, a positive correlation of $r = 0.6$ between retention and pre-test as the covariate, and 80% power to detect a difference between the self-controlled and traditional yoked groups, the required number of participants was 31 per group. Considering the novelty of our Explicit Yoked group, we assumed a smaller effect, $g = 0.4$, between it and the Traditional Yoked group. With the same parameters as above, this resulted in our final sample of 50 participants per group.

Participants completed the experiment in either the Self-Controlled group $(M_{age} = 18.0$, *SD* = 0.34), the Traditional Yoked group $(M_{age} = 19.5$, *SD* = 1.89), or the Explicit Yoked group $(M_{age} = 19.2$, *SD* = 1.55). We collected the Self-Controlled group first as their self-selected observation schedule was required for the yoking procedure for the two other groups. Once the Self-Controlled group had been collected, participants were randomly assigned to one of the two Yoked groups. All participants provided written informed consent approved by and conducted in accordance with the University's Research Ethics Board. Participants received either \$15 or a course bonus for their participation.

## Material

Participants were tasked with learning the 3-6-3 speed cup stacking sequence based on the rules of the World Sport Stacking Association [(https://www.thewssa.com/)](https://www.thewssa.com/). The sequence consisted of an upstack phase and a downstack phase using official Speed Stacks cups [(https://www.speedstacks.com/)](https://www.speedstacks.com/). Participants performed the task using both their hands and had to complete an upstacking and a downstacking phase. The upstacking phase began by completing the first 3 cup pyramid, followed by the 6 cup pyramid, and then the other 3 cup pyramid. The downstacking phase began by returning to and collapsing the 3 cup pyramid that was upstacked first, then the 6 cup pyramid, and finally the last 3 cup pyramid.

## Procedure

Participants completed two data collection sessions separated by approximately 24 hours. Session 1 consisted of a pre-test and an acquisition phase. Session 2 consisted of a delayed retention test. At the start of each phase of the experiment, all participants received phase-specific instructions (see Data and code availability section). Group specific instructions were provided prior to the acquisition phase (see Table \@ref(tab:table1)). The instructions appeared on a 22-inch computer monitor (1920x1080 resolution) positioned to the right of the participant. Participants followed along as the instructions were read aloud by the researcher.

Each trial began with participants standing at a standard height table with their hands on marked positions on the table in front of them. The 12 cups were located in upside down stacks of 3-6-3 in front of the participant. Following a "Get Ready!" prompt displayed for 1 s on the monitor and a constant foreperiod of 1 s, an audiovisual "Go-signal" (green square and a beep tone) was presented. Participants were instructed to start stacking as quickly as possible following the "Go-signal" as its presentation initiated the timer. Once the upstack and downstack phases were completed, participants were instructed to press the spacebar on a keyboard located in front of them to stop the timer. If an error occurred (e.g., only completed the upstack phase then stopped the timer, forgot to hit the timer, etc), the experimenter recorded the trial number for later removal.

The pre-test and delayed retention test both consisted of five no-feedback trials. The acquisition phase had 25 trials and was the only phase where the video demonstration could be watched based on group assignment. Participants in the Self-Controlled group could decide at the start of each trial if they wanted to watch the video demonstration. If they chose to watch the video, they were then asked whether they wanted to watch it in real-time or slow motion (35% of real-time). The real-time video was 6 s in duration and the slow motion version was 18 s. To ensure a constant viewing period of 18 s, a blank screen was shown for 12 s following the end of the real-time video. If they chose not to watch the video, a blank screen was shown for 18 s. Participants in the Traditional Yoked and Explicit Yoked groups received the demonstration schedule created by a participant in the Self-Controlled group with the exception that participants in the Explicit Yoked group were made aware that this schedule was created by another participant. Feedback about stacking time (s) was displayed for 2 s after every acquisition trial.

To test predictions based on the "OPTIMAL" theory regarding the role of motivation, enhanced expectancies, and autonomy-support, participants completed the interest/enjoyment and perceived competence subscales from the Intrinsic Motivation Inventory [@mcauley1989] and a custom scale regarding choice used in previous self-controlled motor learning experiments [@barros2019; @carter2017a]. The order of questions from each scale were randomized and each question was rated using a 7-point Likert scale. Participants answered these questions after the pre-test, after trials five and 25 of acquisition, and before the delayed retention test.

A custom LabVIEW (National Instruments Inc.) program was created that controlled the presentation of all instructions, the video demonstrations, the timing of the experimental protocol, and recorded and stored the data for later analysis.

## Data analysis

Our primary outcome measure was stacking time (i.e., response time) in seconds. Trials recorded as errors $(76/5250 = 1.45\%)$ during data collection were manually removed prior to data analysis. For each participant, pre-test and delayed retention trials were aggregated into one block of five trials and acquisition was aggregated into five blocks of five trials. Significance level was set to 0.05 for all statistical tests. Effect sizes for omnibus tests are reported using generalized eta squared $(\eta^2_{G})$ or eta squared $(\eta^2)$. Post hoc comparisons were conducted using Holm's correction. A Cook's distance of $\geq 1$ was used to identify any influential cases.

# Results

## Pre-registered analysis

To test whether delayed retention (Figure \@ref(fig:fig1)C) was differentially impacted by the experimental group (i.e., Self-Controlled, Traditional Yoked, Explicit Yoked) experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test. As can be seen, the Self-Controlled group $(M = 9.99$, $95\%CI = [9.68,10.31])$, the Traditional Yoked group $(M = 10.18$, $95\%CI = [9.86,10.50])$, and the Explicit Yoked group $(M = 10.12$, $95\%CI = [9.81,10.44])$ all had similar stacking times in retention (means are shown as the adjusted means controlling for pre-test). The effect of Group was not significant, $F(2,146) = .335$, $p = .716$, $\eta^2 = .002$.

(ref:fig1-caption) Physical performance data of the experiment. The Self-Controlled group is shown in red with solid lines and/or circles, the Traditional Yoked group is shown in blue with dotted and/or triangles, and the Explicit Yoked group is shown in orange with dashed and/or squares. **A**. Trial-by-trial stacking time (s) data averaged across participants within each group (shaded area represents standard error). Splits between line segments denote the end of one phase and the start of the next. Pre-test (Trials 1 to 5) and Acquisition (Trials 6 to 30) occurred on Day 1 and Retention (Trials 31 to 35) occurred on Day 2, approximately 24-hours later. **B**. Mean stacking time (s) for each group was computed by averaging the data from **A** into 7 blocks of trials. Error bars represent 95% confidence intervals. Splits between line segments denote the end of one phase and the start of the next. **C**. Mean stacking time (s) adjusted for pre-test for each group. Error bars represent 95% confidence intervals. **D**. Scatterplot showing the relationship between each participant's mean stacking time (s) in pre-test and retention.

```{r fig1, echo = FALSE, fig.cap = "(ref:fig1-caption)", fig.align = "center", out.height = "55%"}
knitr::include_graphics("../../figs/fig1.pdf")
```

## Non pre-registered analyses

### Traditional self-controlled learning advantage

To investigate whether a traditional self-controlled learning advantage existed---that is a comparison between the Self-Controlled and Traditional Yoked groups---we analyzed the non-adjusted retention scores using a Welch's *t*-test. The analysis revealed that the Self-Controlled group $(M = 9.77$, $95\%CI = [9.55,9.99])$ and the Traditional Yoked group $(M = 10.20$, $95\%CI = [9.92,10.49])$ were not statistically different, $t(88.10) = 1.45$, $p = .15$, $g = .29$.

### Acquisition phase

Model frequency and the video speed request data are reported in Table \@ref(tab:table2). The mean frequency of viewing the video demonstration during acquisition was $16.7\%$. When a video demonstration was selected, the mean frequency that the regular speed was selected was $37.3\%$. Stacking time for each Group decreased across acquisition trials (Figure \@ref(fig:fig1)A) and blocks (Figure \@ref(fig:fig1)B). A 3 Group x 5 Block mixed ANOVA with repeated measures on Block revealed a significant Block effect, $F(3.63,533.79) = 116.73$, $p < .001$, $\eta^2_{G} = .133$. Post hoc comparisons revealed all acquisition blocks were significantly different from each other. Both the Group effect, $F(2,147) = .738$, $p = .48$, $\eta^2_{G} = .008$, and Group x Block interaction, $F(7.26,533.79) = .543$, $p = .802$, $\eta^2_{G} = .001$, were not statistically significant.

### Perceived autonomy

Self-reported perceived autonomy scores are displayed in Figure \@ref(fig:fig2)A where it can be seen that the Self-Controlled group reported slightly higher scores compared to the two Yoked groups at all time points following the pre-test. A 3 Group x 3 Time ANCOVA controlling for pre-test revealed a significant Group effect, $F(2,146) = 8.04$, $p < .001$, $\eta^2_{G} = .083.$ Post hoc comparisons on the adjusted means revealed that the Self-Controlled group $(M = 5.61$, $95\%CI =[5.42,5.80])$ had significantly higher perceptions of autonomy compared to both the Traditional Yoked group $(M = 5.13$, $95\%CI = [4.94,5.32])$ and the Explicit Yoked group $(M = 5.13$, $95\%CI = [4.94,5.32])$, which did not differ from each other (and were, in fact, identical to two decimal places). Both the Time effect, $F(1.61,234.98) = .867$, $p = .400$, $\eta^2_{G} = .001$, and Group x Time interaction, $F(3.22,234.98) = 2.10$, $p = .096$, $\eta^2_{G} = .005$, were not significant.

```{r table2, echo = FALSE, results = "asis"}

table_2 <- data.frame(c(
  "Model viewing frequency",
  " ",
  "Regular speed frequency"
  ),
  c(
    "32.6%",
    " ",
    "33.8%"
  ),
  c(
    "16.9%",
    " ",
    "38.1%"
  ),
  c(
    "12.0%",
    " ",
    "50.0%"
  ),
  c(
    "12.9%",
    " ",
    "34.4%"
  ),
  c(
    "9.3%",
    " ",
    "30.4%"
  )
)

apa_table(table_2, font_size = "scriptsize", col.names = c(" ", "Block 1", "Block 2", "Block 3", "Block 4", "Block 5"), booktabs = TRUE, span_text_columns = TRUE, caption = "The mean frequencies for each acquisition block of requesting to watch the video demonstration and choosing the regular viewing speed.", placement = "t")

```

### Intrinsic motivation

Self-reported intrinsic motivation scores can be found in Figure \@ref(fig:fig2)B. At each time point, all groups reported similar scores on the interest/enjoyment subscale. A 3 Group x 3 Time ANCOVA controlling for pre-test revealed non-significant effects for Group, $F(2,146) = 2.08$, $p = .129$, $\eta^2_{G} = .024$, Time, $F(1.68,245.73) = .563$, $p = .541$, $\eta^2_{G} = .001$, and the Group x Time interaction, $F(3.37,245.73) = .333$, $p = .824$, $\eta^2_{G} = .001$.

### Perceived competence

The scores from the perceived competence subscale at each time point are displayed in Figure \@ref(fig:fig2)C. As can be seen, perceived competence scores showed a modest increase over time followed by a slight decrease before the delayed retention test. A 3 Group x 3 Time ANCOVA controlling for pre-test showed an effect of Time, $F(1.75,255.22) = 10.60$, $p < .001$, $\eta^2_{G} = .015$. Post hoc tests on adjusted means revealed that scores were rated as significantly higher at the end of acquisition $(M = 3.98$, $95\%CI = [3.67,3.89])$ and before retention $(M = 3.78$, $95\%CI = [3.67,3.89])$ compared to after trial 5 $(M = 3.60$, $95\%CI = [3.49,3.71])$. However, perceived competence was significantly lower before retention compared to the end of acquisition. No significant effect of Group, $F(2,146) = 2.65$, $p = .074$, $\eta^2_{G} = .028$, or Group x Time interaction, $F(3.50,255.22) = .549$, $p = .677$, $\eta^2_{G} = .002$, was found.

(ref:fig2-caption) Questionnaire data. Groups means for **A** perceived autonomy, **B** intrinsic motivation, and **C** perceived competence after pre-test, trial 5, and trial 25 on Day 1, and before retention on Day 2. The Self-Controlled group is shown in red circles, the Traditional Yoked group is shown in blue triangles, and the Explicit Yoked group is shown in orange squares. Dots represent individual participants in each group. Scores could range from 1 (Strongly disagree) to 7 (Strongly agree). Error bars represent 95% confidence intervals.

```{r fig2, echo = FALSE, fig.cap = "(ref:fig2-caption)", fig.align = "center", out.height = "75%"}
knitr::include_graphics("../../figs/fig2.pdf")

```

### Equivalence tests

To further probe our null effects [@harms2018] related to our main predictions, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure [@lakens2018; @schuirmann1987]. To establish our smallest effect size of interest [@lakens2021] we calculated the effect size our design had 33% power to detect [@simonsohn2015], which was $d_{s} = .31$. The Self-Controlled and Traditional Yoked groups were not statistically different, $t(97.99) = -0.830$, $p = 0.409$, and not statistically equivalent, $t(97.99) = 0.720$, $p = 0.237$, given equivalence bounds of $-.355$ and $.355$ (on a raw scale). Similarly, the Traditional Yoked and Explicit Yoked groups were not statistically different, $t(97.99) = 0.262$, $p = 0.794$, and not statistically equivalent, $t(97.99) = -1.288$, $p = 0.100$, given equivalence bounds of $-.355$ and $.355$ (on a raw scale).

# Discussion

It has been argued that self-controlled practice conditions are effective for motor learning because they are autonomy-supportive in nature [@wulf2016]. Yet, this claim has received, at best, modest support in the motor learning literature [e.g., @mckay2020a; but see @barros2019; @carter2017a; @ste-marie2013 for non-support]. Here, we addressed a possible methodological limitation for this lack of support. That is, in previous self-controlled motor learning research, participants in the yoked group are not made aware that they have been denied opportunities to exercise choice over a practice variable such as feedback or watching a modeled demonstration. In the present experiment we introduced a novel yoked group that was explicitly told that the observation schedule---frequency and speed of video---they would receive during practice was actually one created by another participant in the experiment. Contrary to our prediction, the Explicit Yoked group did not report significantly lower perceived autonomy scores than the Traditional Yoked group, which was only informed their observation schedule was predetermined. In line with the "OPTIMAL" theory [@wulf2016], the Self-Controlled group reported significantly higher perceived autonomy-support than both the Traditional and Explicit Yoked groups. However, this boost in perceived autonomy did not lead to enhanced motor performance or learning. These findings from a well-powered experiment are difficult to reconcile with a core pillar of the "OPTIMAL" theory of motor learning.

## Self-controlled practice conditions as autonomy-supportive

A common problem with many of the self-controlled or choice motor learning literature claiming autonomy-support as an underlying mechanism for self-controlled learning advantages is a failure to include measures that actually test this claim [e.g., @chiviacowsky2014; @chiviacowsky2012; @lewthwaite2015]. Instead, this link to autonomy-support is merely assumed based on the provision of choice to one group of participants versus not giving the same choice to another group of participants. As noted earlier, an issue with this assumption is that within the practice environment itself, there are myriad opportunities for participants, independent of group, to exercise choice. In throwing tasks common to motor learning, participants can explore the task workspace by attempting different throwing techniques. In more lab-based tasks that consist of multiple spatial and timing goals (e.g., waveform matching), participants can choose a single goal to focus on and master before shifting their attention to another goal. Commensurate with this idea, @ste-marie2013 found no differences in perceived choice regarding the motor task being learned between their self-controlled and yoked groups, despite the self-controlled group showing enhanced retention. This may explain why research has consistently reported perceived autonomy scores that do not differ significantly between self-controlled and yoked groups [@barros2019; @carter2017a; @mckay2020b].

Another possible explanation for the finding that being in a self-controlled group has not been perceived as more autonomy-supportive than being in a yoked group is that choice is typically provided over a single element of the practice variable, such as the frequency of receiving feedback [e.g., @aiken2012; @carter2017b] or the level of task difficulty [@andrieux2012; @leiker2016]. Control or choice over a single dimension may not be strong enough to elicit a large enough boost in perceived autonomy above and beyond that of being able to explore one's task workspace as mentioned above. Thus, to increase the saliency of the self-controlled manipulation in the present experiment, we gave the self-controlled participants control over two elements of their observation schedule: viewing frequency and video playback speed. Having control of these two dimensions resulted in higher perceptions of autonomy in our Self-Controlled group compared to the Traditional and Explicit Yoked groups. This may explain the inconsistency with past research failing to find this effect [@barros2019; @carter2017a; @mckay2020b; @ste-marie2013]. However, @mckay2020a recently found that choice over a single element increased perceived autonomy, but similar to our data they also did not find this led to increased learning. Thus, it is unclear whether the higher autonomy scores in the present experiment can in fact be attributed to having control over multiple elements of one's observation schedule.

In a similar vein, past research has also suggested that self-controlled learning benefits are not dependent on the amount of choice opportunities over a single element [@patterson2011]. Given these findings, we argue that the most likely explanation for the inconsistency surrounding the effect of self-controlled practice being autonomy-supportive is that this effect is quite small, and the designs of previous experiments have lacked the statistical power to reliability detect this effect. These experiments have had sample sizes of 20 participants or less per group, whereas there were 50 participants in each group in the present experiment and 64 per group (when collapsed across constant and variable practice schedules) in @mckay2020a. Collapsing across our two yoked groups, we estimate an effect of autonomy-support of $g = .197$ whereas the estimate from @mckay2020a was $g = .57$. Regardless of the estimated size of the effect for autonomy-support through a self-controlled practice condition, a larger issue and challenge to the "OPTIMAL" theory is that significantly higher perceptions of autonomy did not result in superior performance in either acquisition or delayed retention [@wulf2016].

## No learning advantage from a self-controlled observation schedule

The delayed retention results in the present experiment not only are inconsistent with numerous past experiments reporting a self-controlled motor learning benefit [for a review see @ste-marie2019], but also the general consensus that the self-controlled learning advantage is a robust effect [@wulf2016]. Of late, however, there has been an increase in the number of papers reporting a failure to detect the so-called self-controlled learning advantage [e.g., @barros2019; @grand2017; @mckay2020a; @mckay2020b]. This recent lack of support may arise from the self-controlled learning advantage being a much smaller effect than originally estimated ($g = 0.63$ by McKay et al. 2014). A more recent estimate of this effect from a meta-analysis using a weight-function model was $g = .11, \,95\% CI = [.047, .18]$ [@mckay2021]. This estimate was further reduced to $g = .054$ after controlling for publication bias using the precision-effect estimate with standard error (PEESE) method. Thus, both models seem to suggest a trivial effect for self-controlled learning. Additional simulations included in the meta-analysis provided plausible effect size estimates ranging from $g = -.11$ to $.26$ (i.e., it could even favour being in the yoked group). In our experiment, the estimated effect size of self-controlled versus yoked (collapsed across our Traditional and Explicit Yoked groups) was $g = 0.22$. While this estimate is larger than those from the weight-function model and PEESE method, it does fall within the range of plausible effect sizes [@mckay2021]. When the lack of a self-controlled advantage in previous work and our current experiment are contextualized within the findings of this recent meta-analysis, it is not as surprising that the so-called self-controlled learning benefit was not replicated.

Despite the large sample size of the present experiment (*n*/group = 50) versus the typical self-controlled motor learning experiment (median *n*/group = 18 based on the experiments included in the meta-analysis by McKay et al. 2021), the results of the primary analysis and the equivalence tests remain inconclusive. This, along with the effect size estimates in the recent meta-analysis, suggest enormous sample sizes are required to reliably detect an effect of a self-controlled learning advantage. Using the upper bound, $g = .26$, of the range of plausible effects, *253 participants* are required to have 80% power to detect this effect in retention using an independent-samples *t*-test. The number of participants jumps to *1300 per group*, if for instance the estimate from the weight-function model, $g = .11$, is accurate [@mckay2021]. Given the field of motor learning suffers from a lack of adequately powered designs [@lohse2016] and that underpowered designs are more likely to produce false positives and overestimated effect sizes [@button2013], we are skeptical of the replicability of the previous overwhelming support for the self-controlled learning advantage.

## Lack of support for key predictions of the "OPTIMAL" theory of motor learning

Within the "OPTIMAL" theory [@wulf2016], it is predicted that practice conditions that promote autonomy-support and enhance expectancies contribute to a virtuous cycle that leads to superior motor performance and learning. In other words, significant group differences between self-controlled and yoked groups would be expected on measures related to these psychological constructs. As mentioned earlier, we found higher perceptions of autonomy-support in our Self-Controlled group relative to the Traditional and Explicit Yoked groups; however, this did not enhance motor learning as predicted within the virtuous cycle. Contrary to the "OPTIMAL" theory, we did not find an effect of group for perceived competence (i.e., enhanced expectancies) or intrinsic motivation. Perceived competence scores did increase across acquisition blocks, which mirrors the improved motor performance seen throughout acquisition. These results are in line with results of a path analysis that suggested self-efficacy (i.e., enhanced expectancies) and intrinsic motivation were insufficient to explain self-controlled learning benefits [@ste-marie2016]. Overall, our results are inconsistent with key predictions of the "OPTIMAL" theory regarding autonomy-support and enhanced expectancies, and further question the causal role such manipulations play in motor learning.

In sum, we found that being able to control two aspects of one's observation schedule during practice was perceived as autonomy-supportive relative to not having this same control opportunity. However, making participants in an Explicit Yoked group aware they would be denied a control opportunity during practice did not decrease perceptions of autonomy relative to participants in the Traditional Yoked group. Furthermore, we did not find evidence than an autonomy-supportive manipulation had any direct causal effect on learning and we also failed to replicate the typical self-controlled learning advantage. It is worth noting that in some situations autonomy-support in and of itself might be a desired affective outcome [@ste-marie2020]. In such circumstance, providing learners with choice opportunities may be a useful motivationally-protective outcome. However, such a tool should be used judiciously as it is typically motor outcomes in the form of relatively permanent performance changes that is the true goal of any motor learning intervention [@ste-marie2020]. Ultimately, our results add to a growing body of evidence that questions whether autonomy-supportive manipulations directly affect learning. One explanation for this lack of replicability is that the *"true"* effect of such manipulations are much smaller than previously estimated [@mckay2021]. Given the resources required (in terms of sample size) to reliably detect the tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either studying practice conditions that have much bigger effects or devising ways to reduce variability and increase power through clever experimental design [@mcclelland2000].

\newpage

# Conflict of interest
The authors declare no competing interests.

# Funding
This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC). LSG was also supported by an NSERC PGS-D scholarship.

# Data and code availability
All material, data, and scripts to reproduce our analyses and figures can be accessed here: https://github.com/cartermaclab/expt_explicit-yoked.

# R packages used in this project
`r cite_r("../r-references.bib")`.

\newpage

# References

```{=tex}
\begingroup
\interlinepenalty = 10000
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
<!-- <div id="refs" custom-style="Bibliography"></div> -->

\endgroup

### 2021-05-20 scripts/stats.R

@@ -1,0 +1,291 @@
+##########################################################################
+## Statistical analyses for Explicit yoked group project                ##
+## -- St. Germain, Williams, Balbaa, Poskus, Leshchyshen, Lohse, Carter ##
+##                                                                      ##
+## Created by Laura St. Germain and Keith R Lohse                       ##
+##########################################################################
+
+
+# SCRIPT SETUP ---------------
+#
+# Load everything from other R script file
+source("scripts/wrangle.R")
+
+# Required libraries
+library(jmv)
+library(pwr)
+library(TOSTER)
+
+#-------------------------------------------------
+# CONVERT TIBBLES TO WIDE FORMAT FOR JMV() LIBRARY
+#
+motor_acq_p_wide <- motor_acq_p_tib %>%
+    dplyr::select(id, group_id, block_id, mean_mt) %>%
+    tidyr::pivot_wider(names_from = block_id, values_from = mean_mt) %>%
+    dplyr::rename(b1 = 3) %>% # specifying using column number
+    dplyr::rename(b2 = 4) %>% # specifying using column number
+    dplyr::rename(b3 = 5) %>% # specifying using column number
+    dplyr::rename(b4 = 6) %>% # specifying using column number
+    dplyr::rename(b5 = 7) # specifying using column number
+
+motor_pre_ret_p_wide <- motor_pre_ret_p_tib %>%
+    dplyr::select(id, group_id, phase_id, block_id, mean_mt) %>%
+    tidyr::pivot_wider(names_from = phase_id, values_from = mean_mt) %>%
+    dplyr::rename(pre = 4) %>%  # specifying using column number
+    dplyr::rename(ret = 5) # specifying using column number
+
+qaire_im_p_wide <- qaire_im_p_tib %>%
+    tidyr::pivot_wider(names_from = time_id, values_from = score) %>%
+    dplyr::rename(t1 = 4) %>% # specifying using column number
+    dplyr::rename(t2 = 5) %>% # specifying using column number
+    dplyr::rename(t3 = 6) %>% # specifying using column number
+    dplyr::rename(t4 = 7) # specifying using column number
+
+qaire_pc_p_wide <- qaire_pc_p_tib %>%
[…]

### 2021-05-20 scripts/wrangle.R

@@ -1,0 +1,178 @@
+##########################################################################
+## Data wrangling for Explicit yoked group project                      ##
+## -- St. Germain, Williams, Balbaa, Poskus, Leshchyshen, Lohse, Carter ##
+##                                                                      ##
+## Created by Laura St. Germain and Mike Carter                         ##
+##########################################################################
+
+
+# SCRIPT SETUP ---------------
+#
+# Required libraries
+library(tidyverse)
+
+# Load data files into base objects
+motor_data <- readr::read_csv("data/2020-03-30_behaviour-data.csv")
+qaire_data <- readr::read_csv("data/2020-03-30_qaire-data.csv")
+
+
+# INITIAL SETUP FOR MOTOR PERFORMANCE DATA ---------------
+#
+# Create a workable tibble and add columns for non-resetting
+# blocks and trials
+motor_tib <- motor_data %>%
+    dplyr::mutate(block_id_expt = rep(rep(1:7, each = 5), 150)) %>%
+    dplyr::mutate(trial_expt = rep(1:35, 150))
+
+# Re-order columns for readability
+motor_tib <- motor_tib %>%
+    dplyr::select(1:6, block_id_expt, trial_expt, everything())
+
+# Turn variables into factors
+motor_tib <- motor_tib %>%
+    dplyr::mutate(
+        group_id = forcats::as_factor(group_id),
+        phase_id = forcats::as_factor(phase_id),
+        block_id = forcats::as_factor(block_id),
+        block_id_expt = forcats::as_factor(block_id_expt),
+    )
+dplyr::glimpse(motor_tib)
+
+
+# CREATE TIBBLES OF MOTOR DATA FOR STATS AND FIGURES ---------------
+#
+# Tibble for entire experiment (7 blocks with 5 trials in each
+# at the group level)
+motor_7blocks_g_tib <- motor_tib %>%
+    dplyr::group_by(group_id, phase_id, block_id_expt) %>%
+    dplyr::summarize(
+        n = n(),
+        mean_mt = mean(time, na.rm = TRUE),
+        sd_mt = sd(time, na.rm = TRUE),
+        ci_low = ggplot2::mean_cl_normal(time)$ymin,
[…]

### 2021-05-20 docs/preprint/preprint.Rmd
init

--- 2021-05-20 docs/submission/manuscript.Rmd
@@
 authornote: |
-  \addORCIDlink{Laura St. Germain}{0000-0002-5513-4183}
-
-  \addORCIDlink{Keith R. Lohse}{0000-0002-7643-3887}
-
-  \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
+  \addORCIDlink{Laura St. Germain}{0000-0002-5513-4183}; \addORCIDlink{Keith R. Lohse}{0000-0002-7643-3887}; \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
 
@@
 
-floatsintext      : yes
+floatsintext      : no
 figurelist        : no
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
 documentclass     : "apa7"
-classoption       : "man" # man for manuscript & jou for journal
+classoption       : "jou" # man for manuscript & jou for journal
 output            : papaja::apa6_pdf
 header-includes   :
-  - \pagewiselinenumbers
+  # - \pagewiselinenumbers
   - \raggedbottom
@@
 
-apa_table(table_1, font_size = "scriptsize", col.names = c(" ", "Acquisition instructions"), booktabs = TRUE, span_text_columns = TRUE, caption = "Group specific instructions detailing the observation schedule that would be experienced during Acquisition.")
+apa_table(table_1, col.names = c(" ", "Acquisition instructions"), booktabs = TRUE, span_text_columns = TRUE, caption = "Group specific instructions detailing the observation schedule that would be experienced during Acquisition.")
 
@@
 
-```{r fig1, echo = FALSE, fig.cap = "(ref:fig1-caption)", fig.align = "center", out.height = "55%"}
+```{r fig1, echo = FALSE, fig.cap = "(ref:fig1-caption)", out.width = "100%", out.height = "100%", fig.align = "center", fig.env = "figure*"}
 knitr::include_graphics("../../figs/fig1.pdf")
 ```
-
-## Non pre-registered analyses
-
-### Traditional self-controlled learning advantage
-
-To investigate whether a traditional self-controlled learning advantage existed---that is a comparison between the Self-Controlled and Traditional Yoked groups---we analyzed the non-adjusted retention scores using a Welch's *t*-test.
-The analysis revealed that the Self-Controlled group $(M = 9.77$, $95\%CI = [9.55,9.99])$ and the Traditional Yoked group $(M = 10.20$, $95\%CI = [9.92,10.49])$ were not statistically different, $t(88.10) = 1.45$, $p = .15$, $g = .29$.
-
-### Acquisition phase
-
-Model frequency and the video speed request data are reported in Table \@ref(tab:table2).
-The mean frequency of viewing the video demonstration during acquisition was $16.7\%$.
-When a video demonstration was selected, the mean frequency that the regular speed was selected was $37.3\%$.
-Stacking time for each Group decreased across acquisition trials (Figure \@ref(fig:fig1)A) and blocks (Figure \@ref(fig:fig1)B).
-A 3 Group x 5 Block mixed ANOVA with repeated measures on Block revealed a significant Block effect, $F(3.63,533.79) = 116.73$, $p < .001$, $\eta^2_{G} = .133$.
-Post hoc comparisons revealed all acquisition blocks were significantly different from each other.
-Both the Group effect, $F(2,147) = .738$, $p = .48$, $\eta^2_{G} = .008$, and Group x Block interaction, $F(7.26,533.79) = .543$, $p = .802$, $\eta^2_{G} = .001$, were not statistically significant.
-
-### Perceived autonomy
-
-Self-reported perceived autonomy scores are displayed in Figure \@ref(fig:fig2)A where it can be seen that the Self-Controlled group reported slightly higher scores compared to the two Yoked groups at all time points following the pre-test.
-A 3 Group x 3 Time ANCOVA controlling for pre-test revealed a significant Group effect, $F(2,146) = 8.04$, $p < .001$, $\eta^2_{G} = .083.$ Post hoc comparisons on the adjusted means revealed that the Self-Controlled group $(M = 5.61$, $95\%CI =[5.42,5.80])$ had significantly higher perceptions of autonomy compared to both the Traditional Yoked group $(M = 5.13$, $95\%CI = [4.94,5.32])$ and the Explicit Yoked group $(M = 5.13$, $95\%CI = [4.94,5.32])$, which did not differ from each other (and were, in fact, identical to two decimal places).
-Both the Time effect, $F(1.61,234.98) = .867$, $p = .400$, $\eta^2_{G} = .001$, and Group x Time interaction, $F(3.22,234.98) = 2.10$, $p = .096$, $\eta^2_{G} = .005$, were not significant.
 
@@
 
-apa_table(table_2, font_size = "scriptsize", col.names = c(" ", "Block 1", "Block 2", "Block 3", "Block 4", "Block 5"), booktabs = TRUE, span_text_columns = TRUE, caption = "The mean frequencies for each acquisition block of requesting to watch the video demonstration and choosing the regular viewing speed.", placement = "t")
+apa_table(table_2, col.names = c(" ", "Block 1", "Block 2", "Block 3", "Block 4", "Block 5"), booktabs = TRUE, span_text_columns = TRUE, caption = "The mean frequencies for each acquisition block of requesting to watch the video demonstration and choosing the regular viewing speed.", placement = "t")
 
 ```
+
+## Non pre-registered analyses
+
+### Traditional self-controlled learning advantage
+
+To investigate whether a traditional self-controlled learning advantage existed---that is a comparison between the Self-Controlled and Traditional Yoked groups---we analyzed the non-adjusted retention scores using a Welch's *t*-test.
+The analysis revealed that the Self-Controlled group $(M = 9.77$, $95\%CI = [9.55,9.99])$ and the Traditional Yoked group $(M = 10.20$, $95\%CI = [9.92,10.49])$ were not statistically different, $t(88.10) = 1.45$, $p = .15$, $g = .29$.
+
+### Acquisition phase
+
+Model frequency and the video speed request data are reported in Table \@ref(tab:table2).
+The mean frequency of viewing the video demonstration during acquisition was $16.7\%$.
+When a video demonstration was selected, the mean frequency that the regular speed was selected was $37.3\%$.
+Stacking time for each Group decreased across acquisition trials (Figure \@ref(fig:fig1)A) and blocks (Figure \@ref(fig:fig1)B).
+A 3 Group x 5 Block mixed ANOVA with repeated measures on Block revealed a significant Block effect, $F(3.63,533.79) = 116.73$, $p < .001$, $\eta^2_{G} = .133$.
+Post hoc comparisons revealed all acquisition blocks were significantly different from each other.
+Both the Group effect, $F(2,147) = .738$, $p = .48$, $\eta^2_{G} = .008$, and Group x Block interaction, $F(7.26,533.79) = .543$, $p = .802$, $\eta^2_{G} = .001$, were not statistically significant.
+
+### Perceived autonomy
+
+Self-reported perceived autonomy scores are displayed in Figure \@ref(fig:fig2)A where it can be seen that the Self-Controlled group reported slightly higher scores compared to the two Yoked groups at all time points following the pre-test.
+A 3 Group x 3 Time ANCOVA controlling for pre-test revealed a significant Group effect, $F(2,146) = 8.04$, $p < .001$, $\eta^2_{G} = .083.$ Post hoc comparisons on the adjusted means revealed that the Self-Controlled group $(M = 5.61$, $95\%CI =[5.42,5.80])$ had significantly higher perceptions of autonomy compared to both the Traditional Yoked group $(M = 5.13$, $95\%CI = [4.94,5.32])$ and the Explicit Yoked group $(M = 5.13$, $95\%CI = [4.94,5.32])$, which did not differ from each other (and were, in fact, identical to two decimal places).
+Both the Time effect, $F(1.61,234.98) = .867$, $p = .400$, $\eta^2_{G} = .001$, and Group x Time interaction, $F(3.22,234.98) = 2.10$, $p = .096$, $\eta^2_{G} = .005$, were not significant.
+
+(ref:fig2-caption) Questionnaire data.
+Groups means for **A** perceived autonomy, **B** intrinsic motivation, and **C** perceived competence after pre-test, trial 5, and trial 25 on Day 1, and before retention on Day 2.
+The Self-Controlled group is shown in red circles, the Traditional Yoked group is shown in blue triangles, and the Explicit Yoked group is shown in orange squares.
+Dots represent individual participants in each group.
+Scores could range from 1 (Strongly disagree) to 7 (Strongly agree).
+Error bars represent 95% confidence intervals.
 
@@
 
-(ref:fig2-caption) Questionnaire data.
-Groups means for **A** perceived autonomy, **B** intrinsic motivation, and **C** perceived competence after pre-test, trial 5, and trial 25 on Day 1, and before retention on Day 2.
-The Self-Controlled group is shown in red circles, the Traditional Yoked group is shown in blue triangles, and the Explicit Yoked group is shown in orange squares.
-Dots represent individual participants in each group.
-Scores could range from 1 (Strongly disagree) to 7 (Strongly agree).
-Error bars represent 95% confidence intervals.
-
-```{r fig2, echo = FALSE, fig.cap = "(ref:fig2-caption)", fig.align = "center", out.height = "75%"}
-knitr::include_graphics("../../figs/fig2.pdf")
-
-```
-
 ### Equivalence tests
@@
 Similarly, the Traditional Yoked and Explicit Yoked groups were not statistically different, $t(97.99) = 0.262$, $p = 0.794$, and not statistically equivalent, $t(97.99) = -1.288$, $p = 0.100$, given equivalence bounds of $-.355$ and $.355$ (on a raw scale).
+
+```{r fig2, echo = FALSE, fig.cap = "(ref:fig2-caption)", out.width = "85%", out.height = "85%", fig.align = "center", fig.env = "figure*"}
+knitr::include_graphics("../../figs/fig2.pdf")
+
+```
 
@@
 
-\newpage
-
 # Conflict of interest

### 2021-05-20 materials/instructions.Rmd
init

---
title: "Instructions"
#author: ""
#date: ""
output: pdf_document
---

# Pre-test

**Note.** All participants received the same instructions prior to completing the Pre-test of the experiment.

## Everyone
> Welcome to the Pre-test! For this task, you will be required to perform a 3-6-3 cup stacking sequence. Your goal is to complete the up-stack and down-stack as quickly and accurately as possible. Here is a brief instructional video explaining the task. Pay attention to the video because you are only able to watch it once.

*[Video was an excerpt (3:04 to 3:34) from the following video (https://youtu.be/OjEH3ugV6mM) available on the Speed Stacks Inc YouTube channel]*

> You will begin each trial with your hands on the table in front of you in the marked locations. After a brief period of time, the words ‘Get Ready!’ will appear on the screen. Shortly after this (1 sec), you will hear a ‘Go’ beep and see a green square. Once you hear this beep and see the green square, the timer will begin and you should begin the cup stacking task as quickly as possible. Once you have finished the up-stack and down-stack phases, you should hit the SPACEBAR on the keyboard located in front of you to stop the timer. Lastly, here is a brief video explaining some rules about what to do if your cups fall over. Again, please pay attention to the video because you are only able to watch it once.

*[Video was an excerpt (4:12 to 4:48) from the following video (https://youtu.be/OjEH3ugV6mM) available on the Speed Stacks Inc YouTube channel]*

> Do you have any questions? Do you still consent to participate in the experiment? You will now perform 5 trials of the task but will not be told your time.

# Acquisition

**Note.** The first and last portions of the instructions were the same for all participants. The middle portion is where group specific instructions were presented.

## Everyone
> Welcome to Acquisition! For this task, you will be required to perform a 3-6-3 cup stacking sequence. Your goal is to complete the up-stack and down-stack as quickly and accurately as possible. You will begin each trial with your hands on the table in front of you in the marked locations. After a brief period of time, the words ‘Get Ready!’ will appear on the screen. Shortly after this (1 sec), you will hear a ‘Go’ beep and see a green square. Once you hear this beep and see the green square, the timer will begin and you should begin the cup stacking task as quickly as possible. Once you have finished the up-stack and down-stack phases, you should hit the SPACEBAR on the keyboard located in front of you to stop the timer. You will now perform 25 trials of the task.

## Group specific

### Self-Controlled group
> Before each trial, you will be asked whether you wish to watch a modeled demonstration of the task. If you choose YES, you will then be asked whether you want to watch the video in real-time or in slow-motion.

### Traditional Yoked group
> Before each trial, you may or may not watch a modeled demonstration of the task based on a pre-determined schedule. If you observe a model, it might be presented in real-time or in slow-motion based on the pre-determined schedule.

### Explicit Yoked group
> Before each trial, you may or may not watch a modeled demonstration of the task based on the schedule another participant selected. If you observe a model, it might be presented in real-time or in slow-motion based on what that participant selected.

## Everyone
> After each trial, you will be told how long you took to perform the task. If you knock over your cups during the up-stack phase, remember that the previous stack must be standing before you can continue. Should you require a break at any point, please inform the researcher. Do you have any questions?

# Retention

**Note.** All participants received the same instructions prior to completing the Pre-test of the experiment.

## Everyone
> Welcome to Retention! For this task, you will be required to perform a 3-6-3 cup stacking sequence. Your goal is to complete the up-stack and down-stack as quickly and accurately as possible. You will begin each trial with your hands on the table in front of you in the marked locations. After a brief period of time, the words ‘Get Ready!’ will appear on the screen. Shortly after this (1 sec), you will hear a ‘Go’ beep and see a green square. Once you hear this beep and see the green square, the timer will begin and you should begin the cup stacking task as quickly as possible. Once you have finished the up-stack and down-stack phases, you should hit the SPACEBAR on the keyboard located in front of you to stop the timer. If you knock over your cups during the up-stack phase, remember that the previous stack must be standing before you can continue. Do you have any questions? You will now perform 5 trials of the task but ill not be told your time.

### 2021-05-20 scripts/figs.R

@@ -1,0 +1,391 @@
+##########################################################################
+## Visualizations for Explicit yoked group project                      ##
+## -- St. Germain, Williams, Balbaa, Poskus, Leshchyshen, Lohse, Carter ##
+##                                                                      ##
+## Created by Mike Carter                                               ##
+##########################################################################
+
+
+# SCRIPT SETUP ---------------
+#
+# Load everything from other R script file
+source("scripts/wrangle.R")
+
+# Required libraries
+library(cowplot)
+
+# Color and theme setup
+color_theme <- c("#bf616a", "#5e81ac", "#d08770")
+
+theme_set(
+    theme_classic() +
+        theme(
+            axis.title = element_text(size = 14, face = "bold"),
+            axis.text = element_text(size = 12, face = "bold")
+        )
+)
+
+
+# FIGURE 1 ---------------
+#
+# Figure 1a
+fig1a <- ggplot2::ggplot(motor_trialxtrial_g_tib,
+                         aes(x = trial_expt,
+                             y = mean_mt,
+                             group = interaction(group_id, phase_id),
+                             color = group_id)) +
+    geom_ribbon(aes(ymin = se_low,
+                    ymax = se_upp,
+                    fill = group_id),
+                linetype = 0,
+                alpha = 0.2) +
+    geom_line(aes(linetype = group_id,
+                  group = interaction(group_id, phase_id))) +
+    scale_x_continuous(name = "Trial",
+                       limits = c(1, 35),
+                       breaks = seq(1, 35, 3)) +
+    scale_y_continuous(name = "Mean stacking time (s)",
+                       limits = c(5, 25),
+                       breaks = seq(5, 25, 5)) +
+    scale_linetype_manual(values = c(1, 3, 5),
+                          labels = c("Self-Controlled",
+                                     "Traditional Yoked",
+                                     "Explicit Yoked")) +
+    scale_color_manual(values = color_theme,
+                       labels = c("Self-Controlled",
+                                  "Traditional Yoked",
+                                  "Explicit Yoked")) +
+    scale_fill_manual(values = color_theme,
+                       labels = c("Self-Controlled",
+                                  "Traditional Yoked",
+                                  "Explicit Yoked")) +
+    theme(
+        legend.position = c(0.84, 0.88),
+        legend.title = element_blank(),
[…]

### 2021-06-16 docs/submission/manuscript.tex
init
update: submission and preprint dirs

--- 2021-05-20 docs/preprint/preprint.tex
@@
   english,
-  jou]{apa7}
+  man,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
@@
 \shorttitle{Autonomy-support does not benefit motor learning}
-\keywords{Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing}
-\usepackage{dblfloatfix}
+\keywords{Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing\newline\indent Word count: 5055}
+\usepackage{lineno}
 
+\linenumbers
 \usepackage{csquotes}
+\usepackage{pdflscape}
+\pagewiselinenumbers
 \raggedbottom
@@
 
-\addORCIDlink{Laura St. Germain}{0000-0002-5513-4183}; \addORCIDlink{Keith R. Lohse}{0000-0002-7643-3887}; \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
+\addORCIDlink{Laura St. Germain}{0000-0002-5513-4183}
 
-We have outlined author contributions using CRediT (Contributor Roles Taxonomy - \url{https://casrai.org/credit/}).
+\addORCIDlink{Keith R. Lohse}{0000-0002-7643-3887}
 
-The authors made the following contributions.
-Laura St.~Germain: Conceptualization, Data curation, Formal analysis, Investigation - Performed the experiment, Methodology, Project administration, Software - Task Programming, Validation, Visualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Allison Williams: Investigation - Performed the experiment, Writing - Original Draft Preparation, Writing - Review \& Editing; Noura Balbaa: Investigation - Performed the experiment, Writing - Original Draft Preparation, Writing - Review \& Editing; Andrew Poskus: Investigation - Performed the experiment, Writing - Review \& Editing; Olena Leshchyshen: Investigation - Performed the experiment, Writing - Review \& Editing; Keith R.
-Lohse: Conceptualization, Data curation, Formal analysis, Methodology, Validation, Writing - Original Draft Preparation, Writing - Review \& Editing; Michael J.
-Carter: Conceptualization, Data curation, Formal analysis, Funding acquisition, Methodology, Project administration, Resources, Software - Task Programming, Supervision, Validation, Visualization, Writing - Original Draft Preparation, Writing - Review \& Editing.
+\addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
+
+Preregistration: \url{https://aspredicted.org/ze8cj.pdf}
+
+Data, code, and materials: \url{https://github.com/cartermaclab/expt_explicit-yoked}
+
+PsyArXiv preprint: \url{https://doi.org/10.31234/osf.io/s34fg}
 
@@
 There has been growing research interest in the effects that motivation plays in motor learning, and specifically how autonomy, competence, and social relatedness may directly benefit the learning process.
-Here, we present a preregistered manipulation of autonomy-support by providing learners with choice during the practice of a speed cup-stacking skill.
+Here, we present a preregistered manipulation of autonomy-support by providing learners with choice during the practice of a speed cup-stacking task.
 One group was given control over when a video demonstration was provided and the viewing speed.
@@
 These findings add to a growing body of research that questions a causal role of autonomy-support on motor learning, and the robustness of the so-called self-controlled learning advantage.
+
+\textbf{\emph{Public Significance Statement}}\\
+The present study suggests that although university-aged students may experience a boost in feelings of autonomy when given choice over features of their learning environment, this boost does not enhance learning of a new motor skill.
+Additionally, it highlights that coaches and practictioners should be encouraged to incorporate other and more effective practice variables into their training regimes.
 }
@@
 Either of these in isolation, or both simultaneously could contribute to the consistent finding that participants in self-controlled and yoked groups report similar perceived autonomy scores when asked about their opportunities for choices with respect to the motor task (Ste-Marie et al., 2013) or about their practice environment in general (Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020b).
-
-\begin{table*}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:table1}Group specific instructions detailing the observation schedule that would be experienced during Acquisition.}
-
-\begin{tabular}{ll}
-\toprule
-  & Acquisition instructions\\
-\midrule
-Self-Controlled & Before each trial, you will be asked whether you wish to watch a modeled demonstration of the task.\\
- & If you choose YES, you will then be asked whether you want to watch the video in real-time or in\\
- & slow-motion.\\
-Traditional Yoked & Before each trial, you may or may not watch a modeled demonstration of the task based on a pre-\\
- & determined schedule. If you observe a model, it might be presented in real-time or in slow-motion\\
- & based on the pre-determined schedule.\\
-Explicit Yoked & Before each trial, you may or may not watch a modeled demonstration of the task based on the\\
- & schedule another participant selected. If you observe a model, it might be presented in real-time or in\\
- & slow-motion based on what that participant selected.\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table*}
 
@@
 Session 2 consisted of a delayed retention test.
-At the start of each phase of the experiment, all participants received phase-specific instructions (see Data and code availability section).
+At the start of each phase of the experiment, all participants received phase-specific instructions \hyperref[sec:sharing]{(see Data, materials, and code availability section)}.
 Group specific instructions were provided prior to the acquisition phase (see Table \ref{tab:table1}).
@@
 Participants followed along as the instructions were read aloud by the researcher.
+\medskip
+
+\begin{table}
+
+\caption{\label{tab:table1}Group specific components from the instructions detailing the observation schedule that would be experienced during Acquisition.}
+\fontsize{11}{13}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{33em}}
+\toprule
+  & Acquisition instructions\\
+\midrule
+Self-Controlled & Before each trial, you will be asked whether you wish to watch a modeled demonstration of the task.
+If you choose YES, you will then be asked whether you want to watch the video in real-time or in slow-motion.\\
+\addlinespace
+Traditional Yoked & Before each trial, you may or may not watch a modeled demonstration of the task based on a pre-determined schedule.
+If you observe a model, it might be presented in real-time or in slow-motion based on the pre-determined schedule.\\
+\addlinespace
+Explicit Yoked & Before each trial, you may or may not watch a modeled demonstration of the task based on the schedule another participant selected.
+If you observe a model, it might be presented in real-time or in slow-motion based on what that participant selected.\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 Post hoc comparisons were conducted using Holm's correction.
-A Cook's distance of \(\geq 1\) was used to identify any influential cases.
+A Cook's distance of \(\geq 1\) was used to identify any influential cases and none were identified.
 
@@
 
-\begin{figure*}
+\begin{figure}
 
-{\centering \includegraphics[width=1\linewidth,height=1\textheight]{../../figs/fig1}
+{\centering \includegraphics[height=0.51\textheight]{../../figs/fig1}
 
@@
 Scatterplot showing the relationship between each participant's mean stacking time (s) in pre-test and retention.}\label{fig:fig1}
-\end{figure*}
+\end{figure}
 
-\begin{table*}[t]
+\newpage
 
-\begin{center}
-\begin{threeparttable}
+\begin{table}
 
-\caption{\label{tab:table2}The mean frequencies for each acquisition block of requesting to watch the video demonstration and choosing the regular viewing speed.}
-
-\begin{tabular}{llllll}
+\caption{\label{tab:table2}The mean frequencies for each Acquisition block of requesting to watch the video demonstration and of those requests, the mean frequency of choosing the regular viewing speed.}
+\fontsize{11}{13}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{13em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}l}
 \toprule
@@
 \midrule
-Model viewing frequency & 32.6\% & 16.9\% & 12.0\% & 12.9\% & 9.3\%\\
- &  &  &  &  & \\
+Model viewing frequency & 32.6\% & 16.9\% & 12.0\%\% & 12.9\% & 9.3\%\\
+\addlinespace
 Regular speed frequency & 33.8\% & 38.1\% & 50.0\% & 34.4\% & 30.4\%\\
@@
 \end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table*}
+\end{table}
 
@@
 
-\hypertarget{equivalence-tests}{%
-\subsubsection{Equivalence tests}\label{equivalence-tests}}
+\begin{figure}
 
-To further probe our null effects (Harms \& Lakens, 2018) related to our main predictions, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure (Lakens et al., 2018; Schuirmann, 1987).
-To establish our smallest effect size of interest (Lakens, 2021) we calculated the effect size our design had 33\% power to detect (Simonsohn, 2015), which was \(d_{s} = .31\).
-The Self-Controlled and Traditional Yoked groups were not statistically different, \(t(97.99) = -0.830\), \(p = 0.409\), and not statistically equivalent, \(t(97.99) = 0.720\), \(p = 0.237\), given equivalence bounds of \(-.355\) and \(.355\) (on a raw scale).
-Similarly, the Traditional Yoked and Explicit Yoked groups were not statistically different, \(t(97.99) = 0.262\), \(p = 0.794\), and not statistically equivalent, \(t(97.99) = -1.288\), \(p = 0.100\), given equivalence bounds of \(-.355\) and \(.355\) (on a raw scale).
-
-\begin{figure*}
-
-{\centering \includegraphics[width=0.85\linewidth,height=0.85\textheight]{../../figs/fig2}
+{\centering \includegraphics[height=0.72\textheight]{../../figs/fig2}
 
@@
 Error bars represent 95\% confidence intervals.}\label{fig:fig2}
-\end{figure*}
+\end{figure}
+
+\hypertarget{equivalence-tests}{%
+\subsubsection{Equivalence tests}\label{equivalence-tests}}
+
+To further probe the null effects (Harms \& Lakens, 2018) related to our main predictions, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure (Lakens et al., 2018; Schuirmann, 1987).
+To establish our smallest effect size of interest (Lakens, 2021) we calculated the effect size our design had 33\% power to detect (Simonsohn, 2015), which was \(d_{s} = .31\).
+The Self-Controlled and Traditional Yoked groups were not statistically different, \(t(97.99) = -0.830\), \(p = 0.409\), and not statistically equivalent, \(t(97.99) = 0.720\), \(p = 0.237\), given equivalence bounds of \(-.355\) and \(.355\) (on a raw scale).
+Similarly, the Traditional Yoked and Explicit Yoked groups were not statistically different, \(t(97.99) = 0.262\), \(p = 0.794\), and not statistically equivalent, \(t(97.99) = -1.288\), \(p = 0.100\), given equivalence bounds of \(-.355\) and \(.355\) (on a raw scale).
 
@@
 However, this boost in perceived autonomy did not lead to enhanced motor performance or learning.
-These findings from a well-powered experiment are difficult to reconcile with a core pillar of the ``OPTIMAL'' theory of motor learning.
+These findings from a preregistered experiment are difficult to reconcile with a core pillar of the ``OPTIMAL'' theory of motor learning.
 
@@
 It is worth noting that in some situations autonomy-support in and of itself might be a desired affective outcome (Ste-Marie et al., 2020).
-In such circumstance, providing learners with choice opportunities may be a useful motivationally-protective outcome.
+In such circumstances, providing learners with choice opportunities may be a useful motivationally-protective outcome.
 However, such a tool should be used judiciously as it is typically motor outcomes in the form of relatively permanent performance changes that is the true goal of any motor learning intervention (Ste-Marie et al., 2020).
-Ultimately, our results add to a growing body of evidence that questions whether autonomy-supportive manipulations directly affect learning.
+Ultimately, our results add to a growing body of evidence that questions whether autonomy-supportive manipulations directly affect motor learning.
 One explanation for this lack of replicability is that the \emph{``true''} effect of such manipulations are much smaller than previously estimated (McKay et al., 2021).
-Given the resources required (in terms of sample size) to reliably detect the tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either studying practice conditions that have much bigger effects or devising ways to reduce variability and increase power through clever experimental design (McClelland, 2000).
+Given the resources required (in terms of sample size) to reliably detect these tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either studying practice conditions that have much bigger effects or devising ways to reduce variability and increase power through clever experimental design (McClelland, 2000).
+
+\vfill
+
+\hypertarget{contributions-using-credit-httpscasrai.orgcredit}{%
+\section{\texorpdfstring{Contributions using CrediT (\url{https://casrai.org/credit/})}{Contributions using CrediT (https://casrai.org/credit/)}}\label{contributions-using-credit-httpscasrai.orgcredit}}
+
+Conceptualization (LSG, KRL, MJC); Data curation (LSG, KRL, MJC); Formal analysis (LSG, KRL, MJC); Funding acquisition (MJC); Investigation - Performed Experiment (LSG, AW, NB, AP, OL); Methodology (LSG, KRL, MJC); Project administration (LSG, MJC); Resources (MJC); Software - Task Programming (LSG, MJC); Supervision (MJC); Validation (LSG, KRL, MJC); Visualization (LSG, MJC); Writing - Original Draft Preparation (LSG, AW, NB, KRL, MJC); Writing - Review \& Editing (LSG, AW, NB, AP, OL, KRL, MJC)
+
+\hypertarget{data-materials-and-code-availability}{%
+\section{Data, materials, and code availability}\label{data-materials-and-code-availability}}
+
+\label{sec:sharing}
+All material, data, and scripts to reproduce our analyses and figures can be accessed here: \url{https://github.com/cartermaclab/expt_explicit-yoked}.
+The preregistration can be accessed here: \url{https://aspredicted.org/ze8cj.pdf}.
+
+\hypertarget{r-packages-used-in-this-project}{%
+\section{R packages used in this project}\label{r-packages-used-in-this-project}}
+
+R {[}Version 4.1.0; R Core Team (2021){]} and the R-packages \emph{cowplot} {[}Version 1.1.1; Wilke (2020){]}, \emph{ggplot2} {[}Version 3.3.3; Wickham (2016){]}, \emph{jmv} {[}Version 1.2.23; Selker et al.
+(2020){]}, \emph{kableExtra} {[}Version 1.3.4; Zhu (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{pwr} {[}Version 1.3.0; Champely (2020){]}, \emph{tidyverse} {[}Version 1.3.1; Wickham et al.
+(2019){]}, and \emph{TOSTER} {[}Version 0.4.0; Lakens (2017){]}.
 
@@
 
-This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC). LSG was also supported by an NSERC PGS-D scholarship.
-
-\hypertarget{data-and-code-availability}{%
-\section{Data and code availability}\label{data-and-code-availability}}
-
-All material, data, and scripts to reproduce our analyses and figures can be accessed here: \url{https://github.com/cartermaclab/expt_explicit-yoked}.
-
-\hypertarget{r-packages-used-in-this-project}{%
-\section{R packages used in this project}\label{r-packages-used-in-this-project}}
-
-R {[}Version 4.0.5; R Core Team (2021){]} and the R-packages \emph{cowplot} {[}Version 1.1.1; Wilke (2020){]}, \emph{jmv} {[}Version 1.2.23; Selker et al.
-(2020){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{pwr} {[}Version 1.3.0; Champely (2020){]}, \emph{tidyverse} {[}Version 1.3.1; Wickham et al.
-(2019){]}, and \emph{TOSTER} {[}Version 0.3.4; Lakens (2017){]}.
-
-\newpage
+This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC).
+LSG was supported by an NSERC Postgraduate Scholarship.
+AW and AP were supported by NSERC Undergraduate Student Research Awards.
 
@@
 
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}
+
 \leavevmode\hypertarget{ref-R-tidyverse}{}%
@@
 
+\leavevmode\hypertarget{ref-R-kableExtra}{}%
+Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. \url{https://CRAN.R-project.org/package=kableExtra}
+
 \end{CSLReferences}

### 2021-10-31 docs/r0_submission/r0_manuscript.Rmd
update: rename directory and files

--- 2021-05-20 docs/submission/manuscript.Rmd
@@
     corresponding : no    # Define only one corresponding author
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Data curation
-      - Formal analysis
-      - Investigation - Performed the experiment
-      - Methodology
-      - Project administration
-      - Software - Task Programming
-      - Validation
-      - Visualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
+    # role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+    #   - Conceptualization
+    #   - Data curation
+    #   - Formal analysis
+    #   - Investigation - Performed the experiment
+    #   - Methodology
+    #   - Project administration
+    #   - Software - Task Programming
+    #   - Validation
+    #   - Visualization
+    #   - Writing - Original Draft Preparation
+    #   - Writing - Review & Editing
   - name          : "Allison Williams"
     affiliation   : "1"
-    role:
-      - Investigation - Performed the experiment
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
+    # role:
+    #   - Investigation - Performed the experiment
+    #   - Writing - Original Draft Preparation
+    #   - Writing - Review & Editing
   - name          : "Noura Balbaa"
     affiliation   : "1"
-    role:
-      - Investigation - Performed the experiment
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
+    # role:
+    #   - Investigation - Performed the experiment
+    #   - Writing - Original Draft Preparation
+    #   - Writing - Review & Editing
   - name          : "Andrew Poskus"
     affiliation   : "1"
-    role:
-      - Investigation - Performed the experiment
-      - Writing - Review & Editing
+    # role:
+    #   - Investigation - Performed the experiment
+    #   - Writing - Review & Editing
   - name          : "Olena Leshchyshen"
     affiliation   : "1"
-    role:
-      - Investigation - Performed the experiment
-      - Writing - Review & Editing
+    # role:
+    #   - Investigation - Performed the experiment
+    #   - Writing - Review & Editing
   - name          : "Keith R. Lohse"
     affiliation   : "2"
-    role:
-      - Conceptualization
-      - Data curation
-      - Formal analysis
-      - Methodology
-      - Validation
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
+    # role:
+    #   - Conceptualization
+    #   - Data curation
+    #   - Formal analysis
+    #   - Methodology
+    #   - Validation
+    #   - Writing - Original Draft Preparation
+    #   - Writing - Review & Editing
   - name          : "Michael J. Carter"
@@
     email         : "michaelcarter@mcmaster.ca"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Data curation
-      - Formal analysis
-      - Funding acquisition
-      - Methodology
-      - Project administration
-      - Resources
-      - Software - Task Programming
-      - Supervision
-      - Validation
-      - Visualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
+    # role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+    #   - Conceptualization
+    #   - Data curation
+    #   - Formal analysis
+    #   - Funding acquisition
+    #   - Methodology
+    #   - Project administration
+    #   - Resources
+    #   - Software - Task Programming
+    #   - Supervision
+    #   - Validation
+    #   - Visualization
+    #   - Writing - Original Draft Preparation
+    #   - Writing - Review & Editing
 
@@
 
-  We have outlined author contributions using CRediT (Contributor Roles Taxonomy - https://casrai.org/credit/).
+  Preregistration: https://aspredicted.org/ze8cj.pdf
+
+  Data, code, and materials: https://github.com/cartermaclab/expt_explicit-yoked
+
+  PsyArXiv preprint: https://doi.org/10.31234/osf.io/s34fg
 
@@
   There has been growing research interest in the effects that motivation plays in motor learning, and specifically how autonomy, competence, and social relatedness may directly benefit the learning process.
-Here, we present a preregistered manipulation of autonomy-support by providing learners with choice during the practice of a speed cup-stacking skill.
+Here, we present a preregistered manipulation of autonomy-support by providing learners with choice during the practice of a speed cup-stacking task.
 One group was given control over when a video demonstration was provided and the viewing speed.
@@
 
+  ***Public Significance Statement***  
+  The present study suggests that although university-aged students may experience a boost in feelings of autonomy when given choice over features of their learning environment, this boost does not enhance learning of a new motor skill.
+Additionally, it highlights that coaches and practictioners should be encouraged to incorporate other and more effective practice variables into their training regimes.
+
 keywords          : "Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing"
-#wordcount         : "4926"
+wordcount         : "5055"
 bibliography      : ["../references.bib", "../r-references.bib"]
@@
 
-csl               : "../apa-single-spaced.csl"
+csl               : "../apa.csl"
 documentclass     : "apa7"
@@
 header-includes   :
+  - \usepackage{pdflscape}
   - \pagewiselinenumbers
@@
 library(papaja)
-r_refs("r-references.bib")
+library(tidyverse)
+library(kableExtra)
+# r_refs("../r-references.bib")
 ```
@@
 
-```{r table1, echo = FALSE, results = "asis"}
-
-table_1 <- data.frame(c(
-  "Self-Controlled",
-  "", "",
-  "Traditional Yoked",
-  "", "",
-  "Explicit Yoked", 
-  "", ""),
-  c(
-    "Before each trial, you will be asked whether you wish to watch a modeled demonstration of the task.",
-    "If you choose YES, you will then be asked whether you want to watch the video in real-time or in",
-    "slow-motion.",
-
-    "Before each trial, you may or may not watch a modeled demonstration of the task based on a pre-",
-    "determined schedule. If you observe a model, it might be presented in real-time or in slow-motion",
-    "based on the pre-determined schedule.",
-
-    "Before each trial, you may or may not watch a modeled demonstration of the task based on the", 
-    "schedule another participant selected. If you observe a model, it might be presented in real-time or in",
-    "slow-motion based on what that participant selected."
-  )
-)
-
-apa_table(table_1, font_size = "scriptsize", col.names = c(" ", "Acquisition instructions"), booktabs = TRUE, span_text_columns = TRUE, caption = "Group specific instructions detailing the observation schedule that would be experienced during Acquisition.")
-
-```
-
 Here we investigated the effects of making participants in a yoked group explicitly aware of not only being denied opportunities for choice over their frequency of watching and the playback speed of video demonstrations, but also that the schedule they would experience during practice was created by another participant in the experiment.
@@
 Session 2 consisted of a delayed retention test.
-At the start of each phase of the experiment, all participants received phase-specific instructions (see Data and code availability section).
+At the start of each phase of the experiment, all participants received phase-specific instructions \hyperref[sec:sharing]{(see Data, materials, and code availability section)}.
 Group specific instructions were provided prior to the acquisition phase (see Table \@ref(tab:table1)).
@@
 Participants followed along as the instructions were read aloud by the researcher.
+\medskip
+
+```{r table1, echo = FALSE, results = "asis"}
+
+table_1 <- tibble(
+    Group = c("Self-Controlled",
+              "Traditional Yoked",
+              "Explicit Yoked"),
+    Instructions = c("Before each trial, you will be asked whether you wish to watch a modeled demonstration of the task.
+If you choose YES, you will then be asked whether you want to watch the video in real-time or in slow-motion.",
+                     "Before each trial, you may or may not watch a modeled demonstration of the task based on a pre-determined schedule.
+If you observe a model, it might be presented in real-time or in slow-motion based on the pre-determined schedule.",
+                     "Before each trial, you may or may not watch a modeled demonstration of the task based on the schedule another participant selected.
+If you observe a model, it might be presented in real-time or in slow-motion based on what that participant selected.")
+)
+
+kbl(table_1,
+    booktabs = TRUE,
+    escape = TRUE,
+    linesep = "\\addlinespace",
+    caption = "Group specific components from the instructions detailing the observation schedule that would be experienced during Acquisition.",
+    col.names = c(" ",
+                  "Acquisition instructions")
+    ) %>% 
+  #landscape() %>% 
+  kable_styling(position = "left",
+                font_size = 11) %>% 
+  column_spec(1, width = "8em") %>% 
+  column_spec(2, width = "33em")
+```
 
@@
 Post hoc comparisons were conducted using Holm's correction.
-A Cook's distance of $\geq 1$ was used to identify any influential cases.
+A Cook's distance of $\geq 1$ was used to identify any influential cases and none were identified.
 
@@
 
-```{r fig1, echo = FALSE, fig.cap = "(ref:fig1-caption)", fig.align = "center", out.height = "55%"}
+```{r fig1, echo = FALSE, fig.cap = "(ref:fig1-caption)", fig.align = "center", out.height = "51%"}
 knitr::include_graphics("../../figs/fig1.pdf")
+```
+
+\newpage
+
+```{r table2, echo = FALSE, results = "asis"}
+
+table_2 <- tibble(
+    Observation = c("Model viewing frequency",
+                    "Regular speed frequency"),
+    b1 = c("32.6%",
+           "33.8%"),
+    b2 = c("16.9%",
+           "38.1%"),
+    b3 = c("12.0%%",
+           "50.0%"),
+    b4 = c("12.9%",
+           "34.4%"),
+    b5 = c("9.3%",
+           "30.4%"),
+)
+
+kbl(table_2,
+    booktabs = TRUE,
+    escape = TRUE,
+    linesep = "\\addlinespace",
+    caption = "The mean frequencies for each Acquisition block of requesting to watch the video demonstration and of those requests, the mean frequency of choosing the regular viewing speed.",
+    col.names = c(" ",
+                  "Block 1",
+                  "Block 2",
+                  "Block 3",
+                  "Block 4",
+                  "Block 5")
+    ) %>% 
+    kable_styling(position = "left",
+                  font_size = 11) %>% 
+    column_spec(1, width = "13em") %>% 
+    column_spec(2, width = "5em") %>% 
+    column_spec(3, width = "5em") %>% 
+    column_spec(4, width = "5em") %>% 
+    column_spec(5, width = "5em")
+
 ```
@@
 
-```{r table2, echo = FALSE, results = "asis"}
-
-table_2 <- data.frame(c(
-  "Model viewing frequency",
-  " ",
-  "Regular speed frequency"
-  ),
-  c(
-    "32.6%",
-    " ",
-    "33.8%"
-  ),
-  c(
-    "16.9%",
-    " ",
-    "38.1%"
-  ),
-  c(
-    "12.0%",
-    " ",
-    "50.0%"
-  ),
-  c(
-    "12.9%",
-    " ",
-    "34.4%"
-  ),
-  c(
-    "9.3%",
-    " ",
-    "30.4%"
-  )
-)
-
-apa_table(table_2, font_size = "scriptsize", col.names = c(" ", "Block 1", "Block 2", "Block 3", "Block 4", "Block 5"), booktabs = TRUE, span_text_columns = TRUE, caption = "The mean frequencies for each acquisition block of requesting to watch the video demonstration and choosing the regular viewing speed.", placement = "t")
-
-```
-
 ### Intrinsic motivation
@@
 
-```{r fig2, echo = FALSE, fig.cap = "(ref:fig2-caption)", fig.align = "center", out.height = "75%"}
+```{r fig2, echo = FALSE, fig.cap = "(ref:fig2-caption)", fig.align = "center", out.height = "72%"}
 knitr::include_graphics("../../figs/fig2.pdf")
@@
 
-To further probe our null effects [@harms2018] related to our main predictions, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure [@lakens2018; @schuirmann1987].
+To further probe the null effects [@harms2018] related to our main predictions, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure [@lakens2018; @schuirmann1987].
 To establish our smallest effect size of interest [@lakens2021] we calculated the effect size our design had 33% power to detect [@simonsohn2015], which was $d_{s} = .31$.
@@
 However, this boost in perceived autonomy did not lead to enhanced motor performance or learning.
-These findings from a well-powered experiment are difficult to reconcile with a core pillar of the "OPTIMAL" theory of motor learning.
+These findings from a preregistered experiment are difficult to reconcile with a core pillar of the "OPTIMAL" theory of motor learning.
 
@@
 It is worth noting that in some situations autonomy-support in and of itself might be a desired affective outcome [@ste-marie2020].
-In such circumstance, providing learners with choice opportunities may be a useful motivationally-protective outcome.
+In such circumstances, providing learners with choice opportunities may be a useful motivationally-protective outcome.
 However, such a tool should be used judiciously as it is typically motor outcomes in the form of relatively permanent performance changes that is the true goal of any motor learning intervention [@ste-marie2020].
-Ultimately, our results add to a growing body of evidence that questions whether autonomy-supportive manipulations directly affect learning.
+Ultimately, our results add to a growing body of evidence that questions whether autonomy-supportive manipulations directly affect motor learning.
 One explanation for this lack of replicability is that the *"true"* effect of such manipulations are much smaller than previously estimated [@mckay2021].
-Given the resources required (in terms of sample size) to reliably detect the tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either studying practice conditions that have much bigger effects or devising ways to reduce variability and increase power through clever experimental design [@mcclelland2000].
+Given the resources required (in terms of sample size) to reliably detect these tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either studying practice conditions that have much bigger effects or devising ways to reduce variability and increase power through clever experimental design [@mcclelland2000].
 
-\newpage
+\vfill
+
+# Contributions using CrediT (https://casrai.org/credit/)
+Conceptualization (LSG, KRL, MJC); Data curation (LSG, KRL, MJC); Formal analysis (LSG, KRL, MJC); Funding acquisition (MJC); Investigation - Performed Experiment (LSG, AW, NB, AP, OL); Methodology (LSG, KRL, MJC); Project administration (LSG, MJC); Resources (MJC); Software - Task Programming (LSG, MJC); Supervision (MJC); Validation (LSG, KRL, MJC); Visualization (LSG, MJC); Writing - Original Draft Preparation (LSG, AW, NB, KRL, MJC); Writing - Review & Editing (LSG, AW, NB, AP, OL, KRL, MJC)
+
+# Data, materials, and code availability
+\label{sec:sharing}
+All material, data, and scripts to reproduce our analyses and figures can be accessed here: https://github.com/cartermaclab/expt_explicit-yoked.
+The preregistration can be accessed here: https://aspredicted.org/ze8cj.pdf.
+
+# R packages used in this project
+`r cite_r("../r-references.bib")`.
 
@@
 # Funding
-This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC). LSG was also supported by an NSERC PGS-D scholarship.
-
-# Data and code availability
-All material, data, and scripts to reproduce our analyses and figures can be accessed here: https://github.com/cartermaclab/expt_explicit-yoked.
-
-# R packages used in this project
-`r cite_r("../r-references.bib")`.
-
-\newpage
+This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC).
+LSG was supported by an NSERC Postgraduate Scholarship.
+AW and AP were supported by NSERC Undergraduate Student Research Awards.
 

### 2021-10-31 docs/r1_submission/r1_manuscript.Rmd
add: directory for r1 revisions and copy over original submission

--- 2021-10-31 docs/r0_submission/r0_manuscript.Rmd
@@
 
-csl               : "../apa.csl"
 documentclass     : "apa7"
@@
 In fact, autonomy-support is considered such a robust learning variable that it is one of three key pillars in the recently proposed "OPTIMAL" theory of motor learning [@wulf2016].
-@wulf2016 argued that providing learners with opportunities for choice---considered an autonomy-supportive practice manipulation---can facilitate motor performance and learning by enhancing learner's expectancies for success, and by allowing the learner to maintain their attentional focus on the task by reducing the need for self-regulatory activity [@abdollahipour2017; @chua2018; @wulf2018].
+@wulf2016 argued that providing learners with opportunities for choice---considered an autonomy-supportive practice manipulation---can facilitate motor performance and learning by enhancing learner's expectancies for success, and by allowing the learner to maintain their attentional focus on the task by reducing the need for self-regulatory activity [e.g., @abdollahipour2017; @chua2018; @wulf2018].
 In other words, these psychological and attentional benefits, and concomitant increases in performance and learning are a by-product of exercising choice during practice.
-Overall, autonomy-support is seen as a means to efficient goal-action coupling [@wulf2016] and also links the "OPTIMAL" theory with Self-Determination theory [@deci2000].
 
-Despite its prominent role within the "OPTIMAL" theory of motor learning, there are numerous reasons to doubt the importance of autonomy-support through the provision of choice during practice.
-First, if the benefits are the result of having opportunities for choice then learning differences should not emerge between different self-controlled groups.
-However, in experiments where different groups of participants have choice over their feedback schedule, such learning differences have been found, but not limited to, when this choice is made *after* rather than before a performance attempt [@chiviacowsky2005; @carter2014], when different criteria for success are provided to participants [@chiviacowsky2012], and when the absolute number of feedback choice opportunities are limited compared to unlimited at the outset of practice [@hansen2011; @patterson2011].
-Second, there has been little-to-no support for the notion that practicing in a self-controlled group is perceived as more autonomy-supportive than being in a yoked group.
+Despite its prominent role within the "OPTIMAL" theory of motor learning, there are reasons to doubt the importance of autonomy-support through the provision of choice during practice.
+First, if the benefits are primarily the result of having opportunities for choice then learning differences should not emerge between different self-controlled groups.
+However, in experiments where different groups of participants have choice over their feedback schedule, such learning differences have been found when this choice is made *after* rather than before a performance attempt [@chiviacowsky2005; @carter2014], when different criteria for success are provided to participants [@chiviacowsky2012], and when the absolute number of feedback choice opportunities are limited compared to unlimited at the outset of practice [@hansen2011; @patterson2011].
+Second, the notion that practicing in a self-controlled group is in fact more autonomy-supportive than practicing in a yoked group has predominantly been assumed rather than supported empirically.
+
+there has been limited support for the notion that practicing in a self-controlled group is in fact perceived as more autonomy-supportive than being in a yoked group.
+
 @ste-marie2013, for example, had participants in the self-controlled and yoked groups complete the perceived choice subscale of the Intrinsic Motivation Inventory and failed to find the expected effect of higher self-reported scores during practice in the self-controlled group.
-Similar findings have been reported by others [@barros2019; @carter2017a; @mckay2020b].
+Failures to detect increased perceptions of autonomy in self-controlled groups relative to yoked groups have also been reported by others [@barros2019; @carter2017a; @mckay2020b].
 However, @mckay2020a recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group.

### 2021-11-03 docs/r1_submission/r1_manuscript.Rmd
update: begin moving revisions from gdocs to rmd

@@
 In fact, autonomy-support is considered such a robust learning variable that it is one of three key pillars in the recently proposed "OPTIMAL" theory of motor learning [@wulf2016].
-@wulf2016 argued that providing learners with opportunities for choice---considered an autonomy-supportive practice manipulation---can facilitate motor performance and learning by enhancing learner's expectancies for success, and by allowing the learner to maintain their attentional focus on the task by reducing the need for self-regulatory activity [e.g., @abdollahipour2017; @chua2018; @wulf2018].
+@wulf2016 argued that providing learners with opportunities for choice---considered an autonomy-supportive practice manipulation---can facilitate motor performance and learning through enhanced expectancies for success and having the learner maintain their attentional focus on the task thereby reducing the need for self-regulatory activity [e.g., @abdollahipour2017; @chua2018; @wulf2018].
 In other words, these psychological and attentional benefits, and concomitant increases in performance and learning are a by-product of exercising choice during practice.
+Overall, @wulf2016's "OPTIMAL" theory of motor learning provides a motivational account for the learning advantage of self-controlled practice conditions over yoked practice conditions.
+[ADD A FOOTNOTE ABOUT INFORMATION-PROCESSING BUT THAT IT IS THE MOTIVATIONAL VIEW THAT SEEMS TO HAVE GARNERED THE MOST ATTENTION]
 
 Despite its prominent role within the "OPTIMAL" theory of motor learning, there are reasons to doubt the importance of autonomy-support through the provision of choice during practice.
-First, if the benefits are primarily the result of having opportunities for choice then learning differences should not emerge between different self-controlled groups.
+First, if the learning benefits arise out of the opportunity for choice itself then learning differences should not emerge between different self-controlled groups.
 However, in experiments where different groups of participants have choice over their feedback schedule, such learning differences have been found when this choice is made *after* rather than before a performance attempt [@chiviacowsky2005; @carter2014], when different criteria for success are provided to participants [@chiviacowsky2012], and when the absolute number of feedback choice opportunities are limited compared to unlimited at the outset of practice [@hansen2011; @patterson2011].

### 2021-11-03 docs/r1_submission/r1_responses-to-reviewers.Rmd
init: response letter and begin transferring from gdocs

---
title       : "Increased perceptions of autonomy through choice fail to enhance motor skill retention"
authors     : "Laura St. Germain, Allison Williams, Noura Balbaa, Andrew Poskus, Olena Leshchyshen, Keith R. Lohse & Michael J. Carter"
journal     : "Journal of Experimental Psychology: Human Perception and Performance"
manuscript  : "XHP-2021-1912"

class       : "final" # draft or final

output      : papaja::revision_letter_pdf
---

Jacqueline Clare Snow, PhD  
Associate Editor  
*Journal of Experimental Psychology: Human Perception and Performance*

Dear Dr. Snow,

Thank you for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_. We have read the comments provided by the Reviewers and have revised the manuscript accordingly. We thank the Reviewers for their helpful and insightful comments. Below we provide a point-by-point reply to the Reviewer comments (in bold-italic) and our responses in normal text. Any changes that have been made to the original submission are included in the response letter (in a text box) and are in red font in the revised manuscript to facilitate further review.

Kind regards,

Laura St. Germain  
Allison Williams  
Noura Balbaa  
Andrew Poskus  
Olena Leshchyshen  
Keith R. Lohse  
Michael J. Carter

# Reviewer \#1

\RC{\emph{The authors provide a well-thought-out and clearly presented research design with clear theoretical implications. In particular, the analyses were very appropriate and should serve as an example for others conducting similar work. Though I carefully reviewed the manuscript, I do not have any specific suggested changes or questions for the authors. Though certainly not necessary for publication, the authors may wish consider the work of Katz and Assor (2007) surrounding choice and motivation from a Self Determination Theory perspective, as this seems to be relevant to the present findings. 
}}

Thank you for the positive comments about our manuscript and for sharing the reference to Katz and Assor (2007).

# Reviewer \#2

\RC{\emph{The authors submitted a well written manuscript reporting a pre-registered experiment that investigated the effect of awareness of being denied control over two relevant variables of the practice environment (i.e., frequency and speed of video demonstration) as participants learned the speed cup-stacking task. Results revealed that participants allowed to choose when to watch and the speed of the video demonstrations (i.e., self-controlled group) showed higher perceived autonomy scores when compared to yoked participants who received the demonstrations in matched schedule to a self-controlled counterpart and were either explicitly aware of this information (Explicit Yoked) or not (Traditional Yoked). However, the authors failed to replicate the so-called self-control learning benefit as no differences between groups were found in the retention test. Additionally, groups did not differ in self-reported measures of perceived competence and intrinsic motivation.}

\emph{Overall, I think this paper can be a valuable addition to the literature. The study is methodologically strong, it has one of the largest sample sizes reported in the motor learning literature, the authors pre-registered the main analyses, carried out a power calculation, and equivalence test, and heartfully embraced open science practices (I was able to easily reproduce the analyses/figures reported in the paper). However, I do have a few concerns/recommendations that, if addressed, can help to further improve the paper. 
}}

Thank your for the positive general comments about our manuscript. We are pleased to hear that you were able to reproduce the analyses and figures. Below are the responses to your specific comments. Given the length of the first comment, we have split it into multiple comments to facilitate our response.

\RC{\emph{My major concern is how the study's rationale and relevance are framed. The authors start by questioning the role played by autonomy support in practice conditions wherein provision of choice is manipulated. They argued that "if the benefits are the result of having opportunities for choice then learning differences should not emerge between different self-controlled groups" [Page 5, line 7]. However, this claim disregards another possible explanation for the self-control learning benefit, namely information processing factors (Barros et al., 2019).
}}

# Reviewer \#3

\RC{\emph{It was a pleasure to read and review your article "Increased perceptions of autonomy through choice fail to enhance motor skill retention" submitted to the Journal of Experimental Psychology: Human Perception and Performance. Your writing is apparent and concise. This article examines autonomy-support during the speed cup-stacking task. There were three conditions: the self-control group, the traditional yoked group, and the explicit yoked group. The results suggest that there are no statistically significant learning differences between the groups. 
}}

This is our response.

> This is a section quoted from the revised manuscript to illustrate the change.

\clearpage

# References

\begingroup

<div id="refs"></div>

\endgroup

### 2021-11-03 docs/r1_submission/r1_manuscript.tex
update: include revisions based on reviewer comments

--- 2021-06-16 docs/submission/manuscript.tex
@@
   english,
-  man,floatsintext]{apa7}
+  man, donotrepeattitle,floatsintext]{apa7}
+\title{Increased perceptions of autonomy through choice fail to enhance motor skill retention}
+\author{Laura St.~Germain\textsuperscript{1}, Allison Williams\textsuperscript{1}, Noura Balbaa\textsuperscript{1}, Andrew Poskus\textsuperscript{1}, Olena Leshchyshen\textsuperscript{1}, Keith R.
+Lohse\textsuperscript{2}, \& Michael J.
+Carter\textsuperscript{1}}
+\date{}
+
 \usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 % Manuscript styling
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
@@
 
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 % \usepackage{etoolbox}
@@
 \makeatother
-\shorttitle{Autonomy-support does not benefit motor learning}
 \keywords{Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing\newline\indent Word count: 5055}
@@
 \rightheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
-\ifxetex
+\ifXeTeX
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-\title{Increased perceptions of autonomy through choice fail to enhance motor skill retention}
-\author{Laura St.~Germain\textsuperscript{1}, Allison Williams\textsuperscript{1}, Noura Balbaa\textsuperscript{1}, Andrew Poskus\textsuperscript{1}, Olena Leshchyshen\textsuperscript{1}, Keith R.
-Lohse\textsuperscript{2}, \& Michael J.
-Carter\textsuperscript{1}}
-\date{}
+\shorttitle{Autonomy-support does not benefit motor learning}
 
@@
 
-A popular recommendation in recent years for creating an effective environment for motor skill learning has been to allow the learner to take control over an element of their practice that is traditionally controlled by a coach, therapist, or teacher (Sanli et al., 2013; Ste-Marie et al., 2019).
+A popular recommendation in recent years for creating an effective environment for motor skill learning has been to allow the learner to take control over an element of their practice that is traditionally controlled by a coach, therapist, or teacher (Sanli, Patterson, Bray, \& Lee, 2013; Ste-Marie, Carter, \& Yantha, 2019).
 This recommendation is based on the consistent finding that participants in a self-controlled (i.e., choice) group perform with higher proficiency compared to participants in a yoked (i.e., control) group on delayed retention and/or transfer tests.
@@
 Instead, they are linked to a self-controlled participant and experience this participant's self-selected practice schedule.
-This so-called self-controlled learning advantage has been shown when participants are given the opportunity to schedule task difficulty (e.g., Andrieux et al., 2012; Leiker et al., 2016), the order that multiple tasks are practiced (e.g., Wu \& Magill, 2011), the frequency of watching a modeled demonstration (e.g.
-Wulf et al., 2005), and when to receive augmented feedback (e.g., Janelle et al., 1997; Patterson \& Carter, 2010).
+This so-called self-controlled learning advantage has been shown when participants are given the opportunity to schedule task difficulty (e.g., Andrieux, Danna, \& Thon, 2012; Leiker et al., 2016), the order that multiple tasks are practiced (e.g., Wu \& Magill, 2011), the frequency of watching a modeled demonstration (e.g.
+Wulf, Raupach, \& Pfeiffer, 2005), and when to receive augmented feedback (e.g., Janelle, Barba, Frehlich, Tennant, \& Cauraugh, 1997; Patterson \& Carter, 2010).
 
 Over the years, this manipulation has been described using a variety of names (e.g., self- and/or learner-controlled; -regulated; -directed; -selected), but more recently it has been subsumed by autonomy-support.
-In fact, autonomy-support is considered such a robust learning variable that it is one of three key pillars in the recently proposed ``OPTIMAL'' theory of motor learning (Wulf \& Lewthwaite, 2016).
-Wulf and Lewthwaite (2016) argued that providing learners with opportunities for choice---considered an autonomy-supportive practice manipulation---can facilitate motor performance and learning by enhancing learner's expectancies for success, and by allowing the learner to maintain their attentional focus on the task by reducing the need for self-regulatory activity (Abdollahipour et al., 2017; Chua et al., 2018; Wulf et al., 2018).
-In other words, these psychological and attentional benefits, and concomitant increases in performance and learning are a by-product of exercising choice during practice.
-Overall, autonomy-support is seen as a means to efficient goal-action coupling (Wulf \& Lewthwaite, 2016) and also links the ``OPTIMAL'' theory with Self-Determination theory (Deci \& Ryan, 2000).
+\textcolor{red}{Within their ``OPTIMAL'' theory of motor learning,} Wulf and Lewthwaite (2016) \textcolor{red}{argued that providing learners with opportunities for choice creates an autonomy-supportive practice environment, which facilitates motor performance and learning.
+Specifically, the authors predict that autonomy-support facilitates performance by enhancing expectancies (Prediction 3, p.
+1404), that enhanced expectancies and autonomy support contribute to efficient goal-action coupling by readying the motor system for task execution (Prediction 2, p.
+1404), and that enhanced expectancies and autonomy support facilitate motor learning by making dopamine available for memory consolidation and neural pathway development (Prediction 7, p.
+1404).
+In other words, these psychological benefits of increased perceptions of autonomy and competence, and the resulting increases in performance and learning are a by-product of having choice itself.
+Overall,} Wulf and Lewthwaite (2016)'s \textcolor{red}{``OPTIMAL'' theory of motor learning provides a motivational explanation for the learning advantages of self-controlled practice conditions over yoked practice conditions.}\footnote{\textcolor{red}{It should be noted that other researchers have instead presented an information-processing explanation for the self-controlled learning advantages} (see Ste-Marie et al., 2019 for a recent discussion of the motivational and information-processing explanations)\textcolor{red}{.
+We acknowledge this view here; however, unlike previous experiments} (e.g., Barros, Yantha, Carter, Hussien, \& Ste-Marie, 2019; Carter, Carlsen, \& Ste-Marie, 2014; Carter \& Ste-Marie, 2017b, 2017a; Couvillion, Bass, \& Fairbrother, 2020; Woodard \& Fairbrother, 2020) \textcolor{red}{the current experiment was not designed to test between explanations.
+We focused on the motivational explanation as this view has garnered more attention due the ``OPTIMAL'' theory of motor learning.}}
 
-Despite its prominent role within the ``OPTIMAL'' theory of motor learning, there are numerous reasons to doubt the importance of autonomy-support through the provision of choice during practice.
-First, if the benefits are the result of having opportunities for choice then learning differences should not emerge between different self-controlled groups.
-However, in experiments where different groups of participants have choice over their feedback schedule, such learning differences have been found, but not limited to, when this choice is made \emph{after} rather than before a performance attempt (Carter et al., 2014; Chiviacowsky \& Wulf, 2005), when different criteria for success are provided to participants (Chiviacowsky et al., 2012), and when the absolute number of feedback choice opportunities are limited compared to unlimited at the outset of practice (Hansen et al., 2011; Patterson et al., 2011).
-Second, there has been little-to-no support for the notion that practicing in a self-controlled group is perceived as more autonomy-supportive than being in a yoked group.
-Ste-Marie et al.
-(2013), for example, had participants in the self-controlled and yoked groups complete the perceived choice subscale of the Intrinsic Motivation Inventory and failed to find the expected effect of higher self-reported scores during practice in the self-controlled group.
-Similar findings have been reported by others (Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020b).
-However, McKay and Ste-Marie (2020a) recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group.
-This increased perceived autonomy-support did not, however, translate into enhanced learning compared to the yoked group.
-Although the available literature does not provide substantial evidence that self-controlled practice is autonomy-supportive, this does not necessarily mean such a manipulation is not autonomy-supportive (Altman \& Bland, 1995).
-For instance, this effect may in fact be quite small and require much larger sample sizes to detect than those commonly used in motor learning experiments (Lohse et al., 2016).
+\textcolor{red}{Despite its prominent role as a robust and generalizable learning variable in the ``OPTIMAL'' theory (p.
+1393), there is considerable ambiguity surrounding whether the provision of choice is in fact an autonomy-supportive manipulation.
+First, the notion that practicing in a self-controlled group is actually more autonomy-supportive than a yoked group has primarily been assumed} (e.g., Abdollahipour, Palomo Nieto, Psotta, \& Wulf, 2017; Chua, Wulf, \& Lewthwaite, 2018; Lewthwaite, Chiviacowsky, Drews, \& Wulf, 2015; Wulf, Lewthwaite, Cardozo, \& Chiviacowsky, 2018) \textcolor{red}{rather than supported empirically.
+Second, when researchers have included measures related to perceptions of autonomy the data is mixed.
+For example,} Ste-Marie, Vertes, Law, and Rymal (2013) \textcolor{red}{did not find the expected effect of higher perceptions of autonomy during practice in a self-controlled group as compared to a yoked group.
+Similar outcomes have been reported by others} (e.g., Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020a).
+\textcolor{red}{In contrast,} McKay and Ste-Marie (2020b) \textcolor{red}{recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group.
+However, the higher perceived autonomy scores did not translate into enhanced motor performance or learning in the self-controlled group as predicted in the ``OPTIMAL'' theory.
+Although the majority of experiments that included a measure related to perceived autonomy reported no group differences, the ``absence of evidence is not evidence of absence''} (Altman \& Bland, 1995)\textcolor{red}{.
+Thus, self-controlled practice conditions could be an autonomy-supportive manipulation but such an effect may actually be quite small and require much larger sample sizes to detect than those used in previous experiments} (e.g., Barros et al., 2019; Ste-Marie et al., 2013) \textcolor{red}{and in motor learning experiments in general} (see Lohse, Buchanan, \& Miller, 2016 for a discussion)\textcolor{red}{.
+This argument of underpowered experimental designs is supported by the results of} McKay and Ste-Marie (2020b) \textcolor{red}{as these authors had one of the largest sample sizes to date in the self-controlled literature.}
 
 There are at least two other methodological issues that warrant consideration.
-The first of these is that in self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component (e.g., feedback or when to watch a modeled demonstration) of their practice and participants in the yoked group are not given choice over this component.
-However, within the context of practice itself there are many other opportunities for choice that participants may explore, independent of their assigned group.
-Target-based tasks such as basketball free throws (e.g., Aiken et al., 2012) or bean-bag tossing (Grand et al., 2015) are a popular choice in motor learning experiments and have been used in self-controlled learning experiments.
-While a participant in the yoked group may not be permitted choice over their feedback schedule (or some other practice variable) in these experiments, this does not preclude them from opportunities for choice---and thus autonomy-support---when deciding to try different throwing techniques, speeds, and/or release points.
+In self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component (e.g., feedback or when to watch a modeled demonstration) of their practice and participants in the yoked group are not given choice over this component.
+However, within the context of practice itself there are other opportunities for choice that participants may explore, independent of their assigned group.
+Past self-controlled learning experiments have used a variety of motor tasks, including but not limited to basketball free throws (e.g., Aiken, Fairbrother, \& Post, 2012) and bean-bag tossing (e.g., Grand et al., 2015).
+Although participants in a yoked group may not have choice over their feedback schedule (or some other practice variable) while learning such tasks, this does not preclude them from opportunities for choice---and thus autonomy-support---when choosing to try different throwing techniques, speeds, and/or release points.
 Thus, labeling yoked groups as being devoid of choice opportunities may be a misnomer.
-The other consideration relates to the instructions that are provided to participants in the yoked group.
+The other issue relates to the instructions that are provided to participants in a yoked group.
 In the context of feedback\footnote{While feedback is used in this example, this issue surrounding instructions is also relevant to other practice variables commonly used in self-controlled learning experiments.}, these participants are typically informed that during practice they may or may not receive feedback after a given trial (e.g., Chiviacowsky \& Wulf, 2002; Patterson \& Carter, 2010).
-This means that participants in yoked groups are not even aware that they have been denied an opportunity for choice, nor that their feedback schedule was created by another participant who was given choice over when feedback was or was not provided.
-Either of these in isolation, or both simultaneously could contribute to the consistent finding that participants in self-controlled and yoked groups report similar perceived autonomy scores when asked about their opportunities for choices with respect to the motor task (Ste-Marie et al., 2013) or about their practice environment in general (Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020b).
+This means that participants in yoked groups are not even aware that they have been denied an opportunity for choice, or that their feedback schedule was created by another participant who had choice over when feedback was or was not provided.
+These two methodological issues, either in isolation or simultaneously, may have contributed to the consistent finding in past research with self-controlled and yoked participants self-reporting numerically similar perceptions of autonomy when asked about opportunities for choice with respect to the motor task (e.g., Ste-Marie et al., 2013) or about their practice environment in general (e.g., Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020a).
 
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study (Simmons et al., 2012).
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study (Simmons, Nelson, \& Simonsohn, 2012).
 The experimental design and analyses were preregistered using AsPredicted.org and can be viewed here: \url{https://aspredicted.org/ze8cj.pdf}.
@@
 Sample size was determined by an a priori power calculation based on our smallest comparison of interest.
-An early estimate for the effect of self-controlled over yoked practice was a Hedges' \(g = 0.63\) (McKay et al., 2014) and while planning this experiment this effect was estimated to be \(g = 0.52\) (Z.
+An early estimate for the effect of self-controlled over yoked practice was a Hedges' \(g = 0.63\) (McKay, Carter, \& Ste-Marie, 2014) and while planning this experiment this effect was estimated to be \(g = 0.52\) (Z.
 Yantha, personal communication, October 2019).
@@
 
-To test predictions based on the ``OPTIMAL'' theory regarding the role of motivation, enhanced expectancies, and autonomy-support, participants completed the interest/enjoyment and perceived competence subscales from the Intrinsic Motivation Inventory (McAuley et al., 1989) and a custom scale regarding choice used in previous self-controlled motor learning experiments (Barros et al., 2019; Carter \& Ste-Marie, 2017b).
+To test predictions based on the ``OPTIMAL'' theory regarding the role of motivation, enhanced expectancies, and autonomy-support, participants completed the interest/enjoyment and perceived competence subscales from the Intrinsic Motivation Inventory (McAuley, Duncan, \& Tammen, 1989) and a custom scale regarding choice used in previous self-controlled motor learning experiments (Barros et al., 2019; Carter \& Ste-Marie, 2017b).
 The order of questions from each scale were randomized and each question was rated using a 7-point Likert scale.
@@
 
-To further probe the null effects (Harms \& Lakens, 2018) related to our main predictions, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure (Lakens et al., 2018; Schuirmann, 1987).
+To further probe the null effects (Harms \& Lakens, 2018) related to our main predictions, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure (Lakens, Scheel, \& Isager, 2018; Schuirmann, 1987).
 To establish our smallest effect size of interest (Lakens, 2021) we calculated the effect size our design had 33\% power to detect (Simonsohn, 2015), which was \(d_{s} = .31\).
@@
 It has been argued that self-controlled practice conditions are effective for motor learning because they are autonomy-supportive in nature (Wulf \& Lewthwaite, 2016).
-Yet, this claim has received, at best, modest support in the motor learning literature (e.g., McKay \& Ste-Marie, 2020a; but see Barros et al., 2019; Carter \& Ste-Marie, 2017b; Ste-Marie et al., 2013 for non-support).
+Yet, this claim has received, at best, modest support in the motor learning literature (e.g., McKay \& Ste-Marie, 2020b; but see Barros et al., 2019; Carter \& Ste-Marie, 2017b; Ste-Marie et al., 2013 for non-support).
 Here, we addressed a possible methodological limitation for this lack of support.
@@
 
-A common problem with many of the self-controlled or choice motor learning literature claiming autonomy-support as an underlying mechanism for self-controlled learning advantages is a failure to include measures that actually test this claim (e.g., Chiviacowsky, 2014; Chiviacowsky et al., 2012; Lewthwaite et al., 2015).
+A common problem with many of the self-controlled or choice motor learning literature claiming autonomy-support as an underlying mechanism for self-controlled learning advantages is a failure to include measures that actually test this claim (e.g., Chiviacowsky, 2014; Chiviacowsky, Wulf, \& Lewthwaite, 2012; Lewthwaite et al., 2015).
 Instead, this link to autonomy-support is merely assumed based on the provision of choice to one group of participants versus not giving the same choice to another group of participants.
@@
 (2013) found no differences in perceived choice regarding the motor task being learned between their self-controlled and yoked groups, despite the self-controlled group showing enhanced retention.
-This may explain why research has consistently reported perceived autonomy scores that do not differ significantly between self-controlled and yoked groups (Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020b).
+This may explain why research has consistently reported perceived autonomy scores that do not differ significantly between self-controlled and yoked groups (Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020a).
 
@@
 Having control of these two dimensions resulted in higher perceptions of autonomy in our Self-Controlled group compared to the Traditional and Explicit Yoked groups.
-This may explain the inconsistency with past research failing to find this effect (Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020b; Ste-Marie et al., 2013).
-However, McKay and Ste-Marie (2020a) recently found that choice over a single element increased perceived autonomy, but similar to our data they also did not find this led to increased learning.
+This may explain the inconsistency with past research failing to find this effect (Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020a; Ste-Marie et al., 2013).
+However, McKay and Ste-Marie (2020b) recently found that choice over a single element increased perceived autonomy, but similar to our data they also did not find this led to increased learning.
 Thus, it is unclear whether the higher autonomy scores in the present experiment can in fact be attributed to having control over multiple elements of one's observation schedule.
 
-In a similar vein, past research has also suggested that self-controlled learning benefits are not dependent on the amount of choice opportunities over a single element (Patterson et al., 2011).
+In a similar vein, past research has also suggested that self-controlled learning benefits are not dependent on the amount of choice opportunities over a single element (Patterson, Carter, \& Sanli, 2011).
 Given these findings, we argue that the most likely explanation for the inconsistency surrounding the effect of self-controlled practice being autonomy-supportive is that this effect is quite small, and the designs of previous experiments have lacked the statistical power to reliability detect this effect.
-These experiments have had sample sizes of 20 participants or less per group, whereas there were 50 participants in each group in the present experiment and 64 per group (when collapsed across constant and variable practice schedules) in McKay and Ste-Marie (2020a).
-Collapsing across our two yoked groups, we estimate an effect of autonomy-support of \(g = .197\) whereas the estimate from McKay and Ste-Marie (2020a) was \(g = .57\).
+These experiments have had sample sizes of 20 participants or less per group, whereas there were 50 participants in each group in the present experiment and 64 per group (when collapsed across constant and variable practice schedules) in McKay and Ste-Marie (2020b).
+Collapsing across our two yoked groups, we estimate an effect of autonomy-support of \(g = .197\) whereas the estimate from McKay and Ste-Marie (2020b) was \(g = .57\).
 Regardless of the estimated size of the effect for autonomy-support through a self-controlled practice condition, a larger issue and challenge to the ``OPTIMAL'' theory is that significantly higher perceptions of autonomy did not result in superior performance in either acquisition or delayed retention (Wulf \& Lewthwaite, 2016).
@@
 The delayed retention results in the present experiment not only are inconsistent with numerous past experiments reporting a self-controlled motor learning benefit (for a review see Ste-Marie et al., 2019), but also the general consensus that the self-controlled learning advantage is a robust effect (Wulf \& Lewthwaite, 2016).
-Of late, however, there has been an increase in the number of papers reporting a failure to detect the so-called self-controlled learning advantage (e.g., Barros et al., 2019; Grand et al., 2017; McKay \& Ste-Marie, 2020a, 2020b).
+Of late, however, there has been an increase in the number of papers reporting a failure to detect the so-called self-controlled learning advantage (e.g., Barros et al., 2019; Grand, Daou, Lohse, \& Miller, 2017; McKay \& Ste-Marie, 2020b, 2020a).
 This recent lack of support may arise from the self-controlled learning advantage being a much smaller effect than originally estimated (\(g = 0.63\) by McKay et al.~2014).
-A more recent estimate of this effect from a meta-analysis using a weight-function model was \(g = .11, \,95\% CI = [.047, .18]\) (McKay et al., 2021).
+A more recent estimate of this effect from a meta-analysis using a weight-function model was \(g = .11, \,95\% CI = [.047, .18]\) (McKay, Yantha, Hussien, Carter, \& Ste-Marie, 2021).
 This estimate was further reduced to \(g = .054\) after controlling for publication bias using the precision-effect estimate with standard error (PEESE) method.
@@
 Perceived competence scores did increase across acquisition blocks, which mirrors the improved motor performance seen throughout acquisition.
-These results are in line with results of a path analysis that suggested self-efficacy (i.e., enhanced expectancies) and intrinsic motivation were insufficient to explain self-controlled learning benefits (Ste-Marie et al., 2016).
+These results are in line with results of a path analysis that suggested self-efficacy (i.e., enhanced expectancies) and intrinsic motivation were insufficient to explain self-controlled learning benefits (Ste-Marie, Carter, Law, Vertes, \& Smith, 2016).
 Overall, our results are inconsistent with key predictions of the ``OPTIMAL'' theory regarding autonomy-support and enhanced expectancies, and further question the causal role such manipulations play in motor learning.
@@
 Furthermore, we did not find evidence than an autonomy-supportive manipulation had any direct causal effect on learning and we also failed to replicate the typical self-controlled learning advantage.
-It is worth noting that in some situations autonomy-support in and of itself might be a desired affective outcome (Ste-Marie et al., 2020).
+It is worth noting that in some situations autonomy-support in and of itself might be a desired affective outcome (Ste-Marie, Lelievre, \& Germain, 2020).
 In such circumstances, providing learners with choice opportunities may be a useful motivationally-protective outcome.
@@
 
-R {[}Version 4.1.0; R Core Team (2021){]} and the R-packages \emph{cowplot} {[}Version 1.1.1; Wilke (2020){]}, \emph{ggplot2} {[}Version 3.3.3; Wickham (2016){]}, \emph{jmv} {[}Version 1.2.23; Selker et al.
-(2020){]}, \emph{kableExtra} {[}Version 1.3.4; Zhu (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{pwr} {[}Version 1.3.0; Champely (2020){]}, \emph{tidyverse} {[}Version 1.3.1; Wickham et al.
-(2019){]}, and \emph{TOSTER} {[}Version 0.4.0; Lakens (2017){]}.
+R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{jmv} (Version 2.0; Selker, Love, \& Dropmann, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{pwr} (Version 1.3.0; Champely, 2020), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), and \emph{TOSTER} (Version 0.4.0; Lakens, 2017).
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-abdollahipour2017}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-abdollahipour2017}{}}%
 Abdollahipour, R., Palomo Nieto, M., Psotta, R., \& Wulf, G.
@@
 
-\leavevmode\hypertarget{ref-aiken2012}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-aiken2012}{}}%
 Aiken, C.
@@
 
-\leavevmode\hypertarget{ref-altman1995}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-altman1995}{}}%
 Altman, D. G., \& Bland, J. M. (1995). Statistics notes: Absence of evidence is not evidence of absence. \emph{BMJ}, \emph{311}(7003), 485. \url{https://doi.org/10.1136/bmj.311.7003.485}
 
-\leavevmode\hypertarget{ref-andrieux2012}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-andrieux2012}{}}%
 Andrieux, M., Danna, J., \& Thon, B.
@@
 
-\leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. \url{https://github.com/crsh/papaja}
+\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
+Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
-\leavevmode\hypertarget{ref-barros2019}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-barros2019}{}}%
 Barros, J.
@@
 
-\leavevmode\hypertarget{ref-button2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-button2013}{}}%
 Button, K.
@@
 
-\leavevmode\hypertarget{ref-carter2014}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-carter2014}{}}%
 Carter, M.
@@
 
-\leavevmode\hypertarget{ref-carter2017b}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-carter2017b}{}}%
 Carter, M.
@@
 
-\leavevmode\hypertarget{ref-carter2017a}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-carter2017a}{}}%
 Carter, M.
@@
 
-\leavevmode\hypertarget{ref-R-pwr}{}%
-Champely, S. (2020). \emph{Pwr: Basic functions for power analysis}. \url{https://CRAN.R-project.org/package=pwr}
+\leavevmode\vadjust pre{\hypertarget{ref-R-pwr}{}}%
+Champely, S. (2020). \emph{Pwr: Basic functions for power analysis}. Retrieved from \url{https://CRAN.R-project.org/package=pwr}
 
-\leavevmode\hypertarget{ref-chiviacowsky2014}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-chiviacowsky2014}{}}%
 Chiviacowsky, S.
@@
 
-\leavevmode\hypertarget{ref-chiviacowsky2005}{}%
-Chiviacowsky, S., \& Wulf, G.
-(2005).
-Self-controlled feedback is effective if it is based on the learner's performance.
-\emph{Research Quarterly for Exercise and Sport}, \emph{76}(1), 42--48.
-\url{https://doi.org/10.1080/02701367.2005.10599260}
-
-\leavevmode\hypertarget{ref-chiviacowsky2002}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-chiviacowsky2002}{}}%
 Chiviacowsky, S., \& Wulf, G.
@@
 
-\leavevmode\hypertarget{ref-chiviacowsky2012}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-chiviacowsky2012}{}}%
 Chiviacowsky, S., Wulf, G., \& Lewthwaite, R.
@@
 
-\leavevmode\hypertarget{ref-chua2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-chua2018}{}}%
 Chua, L.-K., Wulf, G., \& Lewthwaite, R. (2018). Onward and upward: Optimizing motor performance. \emph{Human Movement Science}, \emph{60}, 107--114. \url{https://doi.org/10.1016/j.humov.2018.05.006}
 
-\leavevmode\hypertarget{ref-deci2000}{}%
-Deci, E.
-L., \& Ryan, R.
-M.
-(2000).
-The {"}what{"} and {"}why{"} of goal pursuits: Human needs and the self-determination of behavior.
-\emph{Psychological Inquiry}, \emph{11}(4), 227--268.
-\url{https://doi.org/10.1207/S15327965PLI1104_01}
+\leavevmode\vadjust pre{\hypertarget{ref-couvillion2020}{}}%
+Couvillion, K.
+F., Bass, A.
+D., \& Fairbrother, J.
+T.
+(2020).
+Increased cognitive load during acquisition of a continuous task eliminates the learning effects of self-controlled knowledge of results.
+\emph{Journal of Sports Sciences}, \emph{38}(1), 94--99.
+\url{https://doi.org/10.1080/02640414.2019.1682901}
 
-\leavevmode\hypertarget{ref-grand2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-grand2015}{}}%
 Grand, K.
@@
 M., Thompson, A.
-G., Buchanan, T.
-L., \& Miller, M.
+G., \ldots{} Miller, M.
 W.
@@
 
-\leavevmode\hypertarget{ref-grand2017}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-grand2017}{}}%
 Grand, K.
@@
 
-\leavevmode\hypertarget{ref-hansen2011}{}%
-Hansen, S., Pfeiffer, J., \& Patterson, J.
-T.
-(2011).
-Self-control of feedback during motor learning: Accounting for the absolute amount of feedback using a yoked group with self-control over feedback.
-\emph{Journal of Motor Behavior}, \emph{43}(2), 113--119.
-\url{https://doi.org/10.1080/00222895.2010.548421}
-
-\leavevmode\hypertarget{ref-harms2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-harms2018}{}}%
 Harms, C., \& Lakens, D.
@@
 
-\leavevmode\hypertarget{ref-janelle1997}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-janelle1997}{}}%
 Janelle, C.
@@
 
-\leavevmode\hypertarget{ref-lakens2021}{}%
-Lakens, D. (2021). \emph{Sample size justification}. \url{https://doi.org/10.31234/osf.io/9d3yf}
-
-\leavevmode\hypertarget{ref-R-TOSTER}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-TOSTER}{}}%
 Lakens, D.
@@
 
-\leavevmode\hypertarget{ref-lakens2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lakens2021}{}}%
+Lakens, D. (2021). \emph{Sample size justification}. \url{https://doi.org/10.31234/osf.io/9d3yf}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lakens2018}{}}%
 Lakens, D., Scheel, A.
@@
 
-\leavevmode\hypertarget{ref-leiker2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-leiker2016}{}}%
 Leiker, A.
@@
 
-\leavevmode\hypertarget{ref-lewthwaite2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lewthwaite2015}{}}%
 Lewthwaite, R., Chiviacowsky, S., Drews, R., \& Wulf, G.
@@
 
-\leavevmode\hypertarget{ref-lohse2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lohse2016}{}}%
 Lohse, K., Buchanan, T., \& Miller, M.
@@
 
-\leavevmode\hypertarget{ref-mcauley1989}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mcauley1989}{}}%
 McAuley, E., Duncan, T., \& Tammen, V.
@@
 
-\leavevmode\hypertarget{ref-mcclelland2000}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mcclelland2000}{}}%
 McClelland, G.
@@
 
-\leavevmode\hypertarget{ref-mckay2014}{}%
-McKay, B., Carter, M. J., \& Ste-Marie, D. M. (2014). Self-controlledlearning: A meta-analysis. \emph{Journal of Sport \& Exercise Psychology,} \emph{36}, S43.
+\leavevmode\vadjust pre{\hypertarget{ref-mckay2014}{}}%
+McKay, B., Carter, M. J., \& Ste-Marie, D. M. (2014). Self-controlledlearning: A meta-analysis. \emph{Journal of sport \& exercise psychology,} \emph{36}, S43.
 
-\leavevmode\hypertarget{ref-mckay2020a}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mckay2020b}{}}%
 McKay, B., \& Ste-Marie, D.
@@
 (2020a).
+Autonomy support and reduced feedback frequency have trivial effects on learning and performance of a golf putting task.
+\emph{Human Movement Science}, \emph{71}(1026124).
+\url{https://doi.org/10.1016/j.humov.2020.102612}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mckay2020a}{}}%
+McKay, B., \& Ste-Marie, D.
+M.
+(2020b).
 Autonomy support via instructionally irrelevant choice not beneficial for motor performance or learning.
@@
 
-\leavevmode\hypertarget{ref-mckay2020b}{}%
-McKay, B., \& Ste-Marie, D.
-M.
-(2020b).
-Autonomy support and reduced feedback frequency have trivial effects on learning and performance of a golf putting task.
-\emph{Human Movement Science}, \emph{71}(1026124).
-\url{https://doi.org/10.1016/j.humov.2020.102612}
-
-\leavevmode\hypertarget{ref-mckay2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mckay2021}{}}%
 McKay, B., Yantha, Z.
@@
 
-\leavevmode\hypertarget{ref-patterson2010}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-patterson2010}{}}%
 Patterson, J.
@@
 
-\leavevmode\hypertarget{ref-patterson2011}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-patterson2011}{}}%
 Patterson, J.
@@
 
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2021). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
+R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
-\leavevmode\hypertarget{ref-sanli2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-sanli2013}{}}%
 Sanli, E.
@@
 
-\leavevmode\hypertarget{ref-schuirmann1987}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-schuirmann1987}{}}%
 Schuirmann, D.
@@
 
-\leavevmode\hypertarget{ref-R-jmv}{}%
-Selker, R., Love, J., \& Dropmann, D. (2020). \emph{Jmv: The 'jamovi' analyses}. \url{https://CRAN.R-project.org/package=jmv}
+\leavevmode\vadjust pre{\hypertarget{ref-R-jmv}{}}%
+Selker, R., Love, J., \& Dropmann, D. (2020). \emph{Jmv: The 'jamovi' analyses}. Retrieved from \url{https://CRAN.R-project.org/package=jmv}
 
-\leavevmode\hypertarget{ref-simmons2012}{}%
-Simmons, J. P., Nelson, L. D., \& Simonsohn, U. (2012). \emph{A 21 Word Solution}. \url{https://doi.org/10.2139/ssrn.2160588}
+\leavevmode\vadjust pre{\hypertarget{ref-simmons2012}{}}%
+Simmons, J. P., Nelson, L. D., \& Simonsohn, U. (2012). \emph{A 21 Word Solution}. Rochester, NY. \url{https://doi.org/10.2139/ssrn.2160588}
 
-\leavevmode\hypertarget{ref-simonsohn2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-simonsohn2015}{}}%
 Simonsohn, U. (2015). Small Telescopes: Detectability and the Evaluation of Replication Results. \emph{Psychological Science}, \emph{26}(5), 559--569. \url{https://doi.org/10.1177/0956797614567341}
 
-\leavevmode\hypertarget{ref-ste-marie2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ste-marie2016}{}}%
 Ste-Marie, D.
@@
 
-\leavevmode\hypertarget{ref-ste-marie2019}{}%
-Ste-Marie, D. M., Carter, M. J., \& Yantha, Z. D. (2019). \emph{Self-controlled learning: Current findings, theoretical perspectives, and future directions} (3rd ed.). Routledge.
+\leavevmode\vadjust pre{\hypertarget{ref-ste-marie2019}{}}%
+Ste-Marie, D.
+M., Carter, M.
+J., \& Yantha, Z.
+D.
+(2019).
+\emph{Self-controlled learning: Current findings, theoretical perspectives, and future directions}.
+In \emph{Skill Acquisition in Sport: Research, Theory, and Practice} (3rd ed.).
+Routledge.
 
-\leavevmode\hypertarget{ref-ste-marie2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ste-marie2020}{}}%
 Ste-Marie, D.
@@
 (2020).
-Revisiting the applied model for the use of observation: A review of articles spanning 2011{{}}2018.
+Revisiting the applied model for the use of observation: A review of articles spanning 2011{\textendash}2018.
 \emph{Research Quarterly for Exercise and Sport}, \emph{91}(4), 594--617.
@@
 
-\leavevmode\hypertarget{ref-ste-marie2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ste-marie2013}{}}%
 Ste-Marie, D.
@@
 
-\leavevmode\hypertarget{ref-R-ggplot2}{}%
-Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
 
-\leavevmode\hypertarget{ref-R-tidyverse}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
 Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T.
-L., Miller, E., Bache, S.
-M., Müller, K., Ooms, J., Robinson, D., Seidel, D.
-P., Spinu, V., \ldots{} Yutani, H.
+D., François, R., \ldots{} Yutani, H.
 (2019).
@@
 
-\leavevmode\hypertarget{ref-R-cowplot}{}%
-Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. \url{https://CRAN.R-project.org/package=cowplot}
+\leavevmode\vadjust pre{\hypertarget{ref-R-cowplot}{}}%
+Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
 
-\leavevmode\hypertarget{ref-wu2011}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-woodard2020}{}}%
+Woodard, K.
+F., \& Fairbrother, J.
+T.
+(2020).
+Cognitive loading during and after continuous task execution alters the effects of self-controlled knowledge of results.
+\emph{Frontiers in Psychology}, \emph{11}.
+\url{https://doi.org/10.3389/fpsyg.2020.01046}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wu2011}{}}%
 Wu, W. F. W., \& Magill, R. A. (2011). Allowing learners to choose. \emph{Research Quarterly for Exercise and Sport}, \emph{82}(3), 449--457. \url{https://doi.org/10.1080/02701367.2011.10599777}
 
-\leavevmode\hypertarget{ref-wulf2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-wulf2016}{}}%
 Wulf, G., \& Lewthwaite, R.
@@
 
-\leavevmode\hypertarget{ref-wulf2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-wulf2018}{}}%
 Wulf, G., Lewthwaite, R., Cardozo, P., \& Chiviacowsky, S.
@@
 
-\leavevmode\hypertarget{ref-wulf2005}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-wulf2005}{}}%
 Wulf, G., Raupach, M., \& Pfeiffer, F.
@@
 
-\leavevmode\hypertarget{ref-R-kableExtra}{}%
-Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. \url{https://CRAN.R-project.org/package=kableExtra}
+\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
+Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
 

### 2021-11-03 docs/r1_submission/r1_manuscript.Rmd
update: include revisions based on reviewer comments

--- 2021-10-31 docs/r0_submission/r0_manuscript.Rmd
@@
 
-csl               : "../apa.csl"
 documentclass     : "apa7"
-classoption       : "man" # man for manuscript & jou for journal
+classoption       : "man, donotrepeattitle" # man for manuscript & jou for journal
 output            : papaja::apa6_pdf
@@
 Over the years, this manipulation has been described using a variety of names (e.g., self- and/or learner-controlled; -regulated; -directed; -selected), but more recently it has been subsumed by autonomy-support.
-In fact, autonomy-support is considered such a robust learning variable that it is one of three key pillars in the recently proposed "OPTIMAL" theory of motor learning [@wulf2016].
-@wulf2016 argued that providing learners with opportunities for choice---considered an autonomy-supportive practice manipulation---can facilitate motor performance and learning by enhancing learner's expectancies for success, and by allowing the learner to maintain their attentional focus on the task by reducing the need for self-regulatory activity [@abdollahipour2017; @chua2018; @wulf2018].
-In other words, these psychological and attentional benefits, and concomitant increases in performance and learning are a by-product of exercising choice during practice.
-Overall, autonomy-support is seen as a means to efficient goal-action coupling [@wulf2016] and also links the "OPTIMAL" theory with Self-Determination theory [@deci2000].
+\textcolor{red}{Within their ``OPTIMAL'' theory of motor learning,} @wulf2016 \textcolor{red}{argued that providing learners with opportunities for choice creates an autonomy-supportive practice environment, which facilitates motor performance and learning.
+Specifically, the authors predict that autonomy-support facilitates performance by enhancing expectancies (Prediction 3, p.
+1404), that enhanced expectancies and autonomy support contribute to efficient goal-action coupling by readying the motor system for task execution (Prediction 2, p.
+1404), and that enhanced expectancies and autonomy support facilitate motor learning by making dopamine available for memory consolidation and neural pathway development (Prediction 7, p.
+1404).
+In other words, these psychological benefits of increased perceptions of autonomy and competence, and the resulting increases in performance and learning are a by-product of having choice itself.
+Overall,} @wulf2016's \textcolor{red}{``OPTIMAL'' theory of motor learning provides a motivational explanation for the learning advantages of self-controlled practice conditions over yoked practice conditions.}[^1]
 
-Despite its prominent role within the "OPTIMAL" theory of motor learning, there are numerous reasons to doubt the importance of autonomy-support through the provision of choice during practice.
-First, if the benefits are the result of having opportunities for choice then learning differences should not emerge between different self-controlled groups.
-However, in experiments where different groups of participants have choice over their feedback schedule, such learning differences have been found, but not limited to, when this choice is made *after* rather than before a performance attempt [@chiviacowsky2005; @carter2014], when different criteria for success are provided to participants [@chiviacowsky2012], and when the absolute number of feedback choice opportunities are limited compared to unlimited at the outset of practice [@hansen2011; @patterson2011].
-Second, there has been little-to-no support for the notion that practicing in a self-controlled group is perceived as more autonomy-supportive than being in a yoked group.
-@ste-marie2013, for example, had participants in the self-controlled and yoked groups complete the perceived choice subscale of the Intrinsic Motivation Inventory and failed to find the expected effect of higher self-reported scores during practice in the self-controlled group.
-Similar findings have been reported by others [@barros2019; @carter2017a; @mckay2020b].
-However, @mckay2020a recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group.
-This increased perceived autonomy-support did not, however, translate into enhanced learning compared to the yoked group.
-Although the available literature does not provide substantial evidence that self-controlled practice is autonomy-supportive, this does not necessarily mean such a manipulation is not autonomy-supportive [@altman1995].
-For instance, this effect may in fact be quite small and require much larger sample sizes to detect than those commonly used in motor learning experiments [@lohse2016].
+[^1]: \textcolor{red}{It should be noted that other researchers have instead presented an information-processing explanation for the self-controlled learning advantages} [see @ste-marie2019 for a recent discussion of the motivational and information-processing explanations]\textcolor{red}{.
+We acknowledge this view here; however, unlike previous experiments} [e.g., @barros2019; @carter2014; @carter2017a; @carter2017b; @couvillion2020; @woodard2020] \textcolor{red}{the current experiment was not designed to test between explanations.
+We focused on the motivational explanation as this view has garnered more attention due the ``OPTIMAL'' theory of motor learning.}
+
+\textcolor{red}{Despite its prominent role as a robust and generalizable learning variable in the ``OPTIMAL'' theory (p.
+1393), there is considerable ambiguity surrounding whether the provision of choice is in fact an autonomy-supportive manipulation.
+First, the notion that practicing in a self-controlled group is actually more autonomy-supportive than a yoked group has primarily been assumed} [e.g., @abdollahipour2017; @chua2018; @lewthwaite2015; @wulf2018] \textcolor{red}{rather than supported empirically.
+Second, when researchers have included measures related to perceptions of autonomy the data is mixed.
+For example,} @ste-marie2013 \textcolor{red}{did not find the expected effect of higher perceptions of autonomy during practice in a self-controlled group as compared to a yoked group.
+Similar outcomes have been reported by others} [e.g., @barros2019; @carter2017a; @mckay2020b].
+\textcolor{red}{In contrast,} @mckay2020a \textcolor{red}{recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group.
+However, the higher perceived autonomy scores did not translate into enhanced motor performance or learning in the self-controlled group as predicted in the ``OPTIMAL'' theory.
+Although the majority of experiments that included a measure related to perceived autonomy reported no group differences, the ``absence of evidence is not evidence of absence''} [@altman1995]\textcolor{red}{.
+Thus, self-controlled practice conditions could be an autonomy-supportive manipulation but such an effect may actually be quite small and require much larger sample sizes to detect than those used in previous experiments} [e.g., @barros2019; @ste-marie2013] \textcolor{red}{and in motor learning experiments in general} [see @lohse2016 for a discussion]\textcolor{red}{.
+This argument of underpowered experimental designs is supported by the results of} @mckay2020a \textcolor{red}{as these authors had one of the largest sample sizes to date in the self-controlled literature.}
 
 There are at least two other methodological issues that warrant consideration.
-The first of these is that in self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component (e.g., feedback or when to watch a modeled demonstration) of their practice and participants in the yoked group are not given choice over this component.
-However, within the context of practice itself there are many other opportunities for choice that participants may explore, independent of their assigned group.
-Target-based tasks such as basketball free throws [e.g., @aiken2012] or bean-bag tossing [@grand2015] are a popular choice in motor learning experiments and have been used in self-controlled learning experiments.
-While a participant in the yoked group may not be permitted choice over their feedback schedule (or some other practice variable) in these experiments, this does not preclude them from opportunities for choice---and thus autonomy-support---when deciding to try different throwing techniques, speeds, and/or release points.
+In self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component (e.g., feedback or when to watch a modeled demonstration) of their practice and participants in the yoked group are not given choice over this component.
+However, within the context of practice itself there are other opportunities for choice that participants may explore, independent of their assigned group.
+Past self-controlled learning experiments have used a variety of motor tasks, including but not limited to basketball free throws [e.g., @aiken2012] and bean-bag tossing [e.g., @grand2015].
+Although participants in a yoked group may not have choice over their feedback schedule (or some other practice variable) while learning such tasks, this does not preclude them from opportunities for choice---and thus autonomy-support---when choosing to try different throwing techniques, speeds, and/or release points.
 Thus, labeling yoked groups as being devoid of choice opportunities may be a misnomer.
-The other consideration relates to the instructions that are provided to participants in the yoked group.
-In the context of feedback[^1], these participants are typically informed that during practice they may or may not receive feedback after a given trial [e.g., @chiviacowsky2002; @patterson2010].
-This means that participants in yoked groups are not even aware that they have been denied an opportunity for choice, nor that their feedback schedule was created by another participant who was given choice over when feedback was or was not provided.
-Either of these in isolation, or both simultaneously could contribute to the consistent finding that participants in self-controlled and yoked groups report similar perceived autonomy scores when asked about their opportunities for choices with respect to the motor task [@ste-marie2013] or about their practice environment in general [@barros2019; @carter2017a; @mckay2020b].
+The other issue relates to the instructions that are provided to participants in a yoked group.
+In the context of feedback[^2], these participants are typically informed that during practice they may or may not receive feedback after a given trial [e.g., @chiviacowsky2002; @patterson2010].
+This means that participants in yoked groups are not even aware that they have been denied an opportunity for choice, or that their feedback schedule was created by another participant who had choice over when feedback was or was not provided.
+These two methodological issues, either in isolation or simultaneously, may have contributed to the consistent finding in past research with self-controlled and yoked participants self-reporting numerically similar perceptions of autonomy when asked about opportunities for choice with respect to the motor task [e.g., @ste-marie2013] or about their practice environment in general [e.g., @barros2019; @carter2017a; @mckay2020b].
 
-[^1]: While feedback is used in this example, this issue surrounding instructions is also relevant to other practice variables commonly used in self-controlled learning experiments.
+[^2]: While feedback is used in this example, this issue surrounding instructions is also relevant to other practice variables commonly used in self-controlled learning experiments.
 

### 2021-11-03 docs/r1_submission/r1_responses-to-reviewers.Rmd
update: continuing transferring responses and adding information

@@
 Below we provide a point-by-point reply to the Reviewer comments (in bold-italic) and our responses in normal text.
-Any changes that have been made to the original submission are included in the response letter (in a text box) and are in red font in the revised manuscript to facilitate further review.
+Any substantial changes that have been made to the original submission are also included in the response letter (in a text box) and are in red font in the revised manuscript.
 
@@
 Below are the responses to your specific comments.
-Given the length of the first comment, we have split it into multiple comments to facilitate our response.
+We have split the first comment into smaller chunks to facilitate our response.
 
@@
 }}
+
+We agree with the reviewer that an information-processing explanation has also been forwarded to account for the self-controlled learning advantages.
+We did not not specifically refer to it in the introduction as this experiment was not designed to dissociate between the motivational and the information-processing explanations.
+We have removed the quoted text in the revised submission and have added the following as a footnote to acknowledge the information-processing view **(see Page XX)**:
+
+> It should be noted that other researchers have instead presented an information-processing explanation for the self-controlled learning advantages (see Ste-Marie et al., 2019 for a recent discussion of the motivational and information-processing explanations).
+We acknowledge this view here; however, unlike previous experiments (e.g., Barros, Yantha, Carter, Hussien, & Ste-Marie, 2019; Carter, Carlsen, & Ste-Marie, 2014; Carter & Ste-Marie, 2017b, 2017a; Couvillion, Bass, & Fairbrother, 2020; Woodard & Fairbrother, 2020) the current experiment was not designed to test between explanations.
+We focused on the motivational explanation as this view has garnered more attention due the “OPTIMAL” theory of motor learning.
+
+\RC{\emph{Second, they state that "there has been little-to-no support for the notion that practicing in a self-controlled group is perceived as more autonomy-supportive than being in a yoked group" [Page 5, line 15].
+Although this statement has been supported by previous studies such as the one cited in the paper (Ste-Marie et al., 2013), group differences regarding levels of perceived autonomy have been found in recent studies (McKay \& Ste-Marie, 2020- also cited in the paper).
+The evidence, therefore, as presented in the paper seems mixed.
+Moreover, another explanation for the lack of group differences might have to do with the fact that increased levels of perceived autonomy have been assumed instead of directly measured in self-control studies.
+Thus, it becomes unclear whether the little-to-no support for the notion that practicing in a self-controlled group is perceived as more autonomy-supportive comes from a lack of differences when there is a measure of perceived autonomy or, rather, from a lack of studies assessing how provision of choice affects perception of autonomy.
+The authors then proceed to claim that "Although the available literature does not provide substantial evidence that self-controlled practice is autonomy-supportive, this does not necessarily mean such [extra 'a' here] manipulation is not autonomy-supportive.
+For instance, this effect may in fact be quite small and require much larger sample sizes to detect than those commonly used in motor learning experiments" [Page 5, line 25], which is a fair claim to make considering the methodological concerns surrounding motor learning studies (Lohse et al., 2016).
+However, the way this argument was structured led to the notion that it is still unclear whether self-control conditions lead to higher levels of perceived autonomy, circling back to my previous argument that the evidence is somewhat mixed and might be due to the lack of studies directly measuring perceived autonomy.
+}}
+
+We agree with many of the points raised here.
+We attempted to capture the mixed nature of findings by presenting experiments that failed to find an effect and the one that did find the expected effect.
+We restricted our discussion of past work not including measures in the Discussion as the true impact of this unknown and speculative.
+Based on your comments, we have restructured part of the Introduction to improve the clarity of our arguments **(see Pages XX, Lines XX)**:
+
+> Despite its prominent role as a robust and generalizable learning variable in the “OPTIMAL” theory (p.
+1393), there is considerable ambiguity surrounding whether the provision of choice is in fact an autonomy-supportive manipulation.
+First, the notion that practicing in a self-controlled group is actually more autonomy-supportive than a yoked group has primarily been assumed (e.g., Abdollahipour, Palomo Nieto, Psotta, & Wulf, 2017; Chua, Wulf, & Lewthwaite, 2018; Lewthwaite, Chiviacowsky, Drews, & Wulf, 2015; Wulf, Lewthwaite, Cardozo, & Chiviacowsky, 2018) rather than supported empirically.
+Second, when researchers have included measures related to perceptions of autonomy the data is mixed.
+For example, Ste-Marie, Vertes, Law, and Rymal (2013) did not find the expected effect of higher perceptions of autonomy during practice in a self-controlled group as compared to a yoked group.
+Similar outcomes have been reported by others (e.g., Barros et al., 2019; Carter & Ste-Marie, 2017b; McKay & Ste-Marie, 2020a).
+In contrast, McKay and Ste-Marie (2020b) recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group.
+However, the higher perceived autonomy scores did not translate into enhanced motor performance or learning in the self-controlled group as predicted in the “OPTIMAL” theory.
+Although the majority of experiments that included a measure related to perceived autonomy reported no group differences, the “absence of evidence is not evidence of absence” (Altman & Bland, 1995).
+Thus, self-controlled practice conditions could be an autonomy-supportive manipulation but such an effect may actually be quite small and require much larger sample sizes to detect than those used in previous experiments (e.g., Barros et al., 2019; Ste-Marie et al., 2013) and in motor learning experiments in general (see Lohse, Buchanan, & Miller, 2016 for a discussion).
+This argument of underpowered experimental designs is supported by the results of McKay and Ste-Marie (2020b) as these authors had one of the largest sample sizes to date in the self-controlled literature.
+
+\RC{\emph{Moreover, there was no explicit mention as to how levels of perceived autonomy might have a mechanistic role in motor skill learning.
+Self-control conditions might lead to higher levels of perceived autonomy but no learning advantage (as seen in the present study).
+But, when looking at the title of the paper and how the discussion unfolds, the authors shift their focus to claim that autonomy-support does not benefit motor learning.
+}}
+
+We agree that self-controlled practice conditions might lead to higher levels of perceived autonomy without any learning advantage.
+This, however, is not what is predicted in "OPTIMAL" theory where a causal relationship is put forward.
+The title of our paper and how the discussion unfolds is based on the results of our experiment, which suggests that increased perceptions of autonomy do not benefit motor learning.
+To your first point, we have added the following to the introduction to better outline how autonomy-support might have a mechanistic role in motor performance and learning according to the "OPTIMAL" theory of motor learning **(see Pages XX, Lines XX)**:
+
+> Within their “OPTIMAL” theory of motor learning, Wulf and Lewthwaite (2016) argued that providing learners with opportunities for choice creates an autonomy-supportive practice environment, which facilitates motor performance and learning.
+Specifically, the authors predict that autonomy-support facilitates performance by enhancing expectancies (Prediction 3, p.
+1404), that enhanced expectancies and autonomy support contribute to efficient goal-action coupling by readying the motor system for task execution (Prediction 2, p.
+1404), and that enhanced expectancies and autonomy support facilitate motor learning by making dopamine available for memory consolidation and neural pathway development (Prediction 7, p.
+1404).
+In other words, these psychological benefits of increased perceptions of autonomy and competence, and the resulting increases in performance and learning are a by-product of having choice itself.
+Overall, Wulf and Lewthwaite (2016)’s “OPTIMAL” theory of motor learning provides a motivational explanation for the learning advantages of self-controlled practice conditions over yoked practice conditions.
+
+\RC{\emph{The narrative in its current form lacks clarity.
+Are the authors interested in detecting group differences in levels of perceived autonomy (regardless of whether it predicts learning) or in the role of autonomy-support in enhancing learning (i.e., replicate the self-control learning benefit under a motivational perspective)?
+The issue gets even more cloudy as the authors raise two methodological concerns identified in the autonomy-support literature: 1) "The first of these is that in self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component of their practice and participants in the yoked group are not given choice over this component.
+However, within the context of practice itself there are many other opportunities for choice that participants may explore, independent of their assigned group" [Page6, line 4], and 2) "The other consideration relates to the instructions that are provided to participants in the yoked group [Page 6, line 16]", "Participants in yoked groups are not even aware that they have been denied an opportunity for choice, nor that their feedback schedule was created by another participant who was given choice over when feedback was or was not provided" [Page 6, line 20].
+Regarding the first one, the benefits of self-control experiments have been found even when choice is given over an irrelevant aspect of the practice condition (incidental choice - Wulf \& Lewthwaite, 2016).
+Following this logic, it seems like the authors are referring specifically to the levels of perceived autonomy (having control over more variables might lead to higher levels of perceived autonomy).
+However, making yoked participants aware of being denied choice over some aspects of the practice condition does not prevent them from experiencing choice through other opportunities, weaking this argument.
+Moreover, this manipulation (i.e., making yoked participants aware of being denied choice) is better fitted under the controlling instructional language manipulation, which is contrasted against autonomy-supportive language (e.g., Hooyman et al., 2014).
+Yet, the authors do not even mention past research investigating the effect of controlling language on motor learning.
+}}
+
+Based on the "OPTIMAL" theory, we were interested in replicating the typical self-controlled learning advantage (group difference in retention favouring the self-controlled group) and testing the claim that self-controlled practice conditions are a way to create an autonomy-supportive environment (group difference in self-reported perceptions of autonomy).
+We have added details about our predictions to the revised manuscript (but we include this information below with your specific comment about these missing from the manuscript).
+In terms of the first methodological limitation, yes some researchers have reported a learning benefit of task-irrelevant choices (e.g., Lewthwaite & Wulf 2015); however, this is a fairly selective stance given the mixed results surrounding task-irrelevant choices (e.g., Carter & Ste-Marie 2017; Grand et al.
+2015; McKay & Ste-Marie 2020ab).
+In McKay & Ste-Marie 2020a, the task-irrelevant choice groups actually performed with significantly more error in the acquisition and transfer.
 

### 2021-11-04 docs/r1_submission/r1_manuscript.Rmd
update: finalized changes to revised manuscript

@@
 
-  ***Public Significance Statement***  
-  The present study suggests that although university-aged students may experience a boost in feelings of autonomy when given choice over features of their learning environment, this boost does not enhance learning of a new motor skill.
-Additionally, it highlights that coaches and practictioners should be encouraged to incorporate other and more effective practice variables into their training regimes.
+  \noindent \textbf{\emph{Public Significance Statement}}  
+  The present study suggests that although university-aged students may experience a boost in feelings of autonomy when given choice over features of their learning environment, this boost may not enhance learning of a new motor skill.
+Our results also highlight the need for higher powered and pre-registered motor learning experiments if coaches and practictioners are to be provided with reliable recommendations for training and rehabilitation protocols.
 
-keywords          : "Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing"
-wordcount         : "5055"
+keywords          : "Motor learning; Pre-registered; Self-controlled; Observation"
+wordcount         : "4585"
 bibliography      : ["../references.bib", "../r-references.bib"]
@@
 
-Over the years, this manipulation has been described using a variety of names (e.g., self- and/or learner-controlled; -regulated; -directed; -selected), but more recently it has been subsumed by autonomy-support.
+Over the years, this manipulation has been described using a variety of names (e.g., self- and/or learner-controlled; -regulated; -directed; -selected), but more recently \textcolor{red}{some researchers have adopted the term} autonomy-support.
 \textcolor{red}{Within their ``OPTIMAL'' theory of motor learning,} @wulf2016 \textcolor{red}{argued that providing learners with opportunities for choice creates an autonomy-supportive practice environment, which facilitates motor performance and learning.
@@
 \textcolor{red}{In contrast,} @mckay2020a \textcolor{red}{recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group.
-However, the higher perceived autonomy scores did not translate into enhanced motor performance or learning in the self-controlled group as predicted in the ``OPTIMAL'' theory.
+However, despite their higher perceived autonomy scores the self-controlled group did not have significantly better motor performance and learning as predicted in the ``OPTIMAL'' theory.
 Although the majority of experiments that included a measure related to perceived autonomy reported no group differences, the ``absence of evidence is not evidence of absence''} [@altman1995]\textcolor{red}{.
@@
 
-Here we investigated the effects of making participants in a yoked group explicitly aware of not only being denied opportunities for choice over their frequency of watching and the playback speed of video demonstrations, but also that the schedule they would experience during practice was created by another participant in the experiment.
-The addition of this novel yoked group allowed us to address one of the previously identified methodological limitations regarding experimental group instructions in past self-controlled research.
-We compared the performance of this explicit yoked group with traditional self-controlled and yoked groups on a speed cup-stacking task in practice and in a delayed retention test.
+\textcolor{red}{Here, we addressed the methodological limitation of past self-controlled research where participants in the yoked group are unaware that a feature of their practice environment was created by another participant in the experiment.
+To this end, participants learned a speed cup-stacking task in either a self-controlled group, a traditional yoked group, or a novel explicitly aware yoked group.
+The self-controlled group has choice over the frequency of watching a video demonstration and the video playback speed (real-time or slow motion).
+Participants in the traditional and explicit yoked groups were matched to a participant in the self-controlled group and experienced the observation schedule selected by this participant.
+The key difference being that participants in the explicit yoked group were told that the observation schedule they would experience during practice was selected by another participant, whereas participants in the traditional yoked group were not aware of this.
+Motor learning was assessed using a delayed retention test.
+We predicted that the self-controlled group would have significantly faster stacking times in retention than the traditional yoked group.
+In other words, we expected to replicate the typical self-controlled learning advantage.
+If the self-controlled learning advantage results from choice being autonomy-supportive as argued in the ``OPTIMAL'' theory} [@wulf2016]\textcolor{red}{, then participants in the self-controlled group should also self-report significantly higher scores for perceptions of autonomy.
+Also based on the view that autonomy-support is the mechanism underlying the typical self-controlled learning advantage} [@wulf2016]\textcolor{red}{, we predicted that the explicit yoked group should have significantly slower stacking times in retention.
+Although we found significantly higher perceptions of autonomy in the self-controlled group, there were no significant group differences in stacking times during retention.
+Overall, these results do not support our predictions and are inconsistent with predictions 2, 3, and 7 in the ``OPTIMAL'' theory of motor learning} [@wulf2016].
 
@@
 
-One-hundred and fifty participants completed the experiment.
-Sample size was determined by an a priori power calculation based on our smallest comparison of interest.
+One-hundred and fifty \textcolor{red}{university students} participated in the experiment.
+Sample size was determined by an a priori power calculation based on our smallest comparison of interest \textcolor{red}{using GLIMMPSE (https://glimmpse.samplesizeshop.org/)}.
 An early estimate for the effect of self-controlled over yoked practice was a Hedges' $g = 0.63$ [@mckay2014] and while planning this experiment this effect was estimated to be $g = 0.52$ (Z.
 Yantha, personal communication, October 2019).
-Based on this effect, a positive correlation of $r = 0.6$ between retention and pre-test as the covariate, and 80% power to detect a difference between the self-controlled and traditional yoked groups, the required number of participants was 31 per group.
+Based on this effect, a positive correlation of $r = 0.6$ between retention and pre-test as the covariate, \textcolor{red}{an alpha of 0.05}, and 80% power to detect a difference between the self-controlled and traditional yoked groups, the required number of participants was 31 per group.
 Considering the novelty of our Explicit Yoked group, we assumed a smaller effect, $g = 0.4$, between it and the Traditional Yoked group.
-With the same parameters as above, this resulted in our final sample of 50 participants per group.
+\textcolor{red}{Using this effect and} the same parameters as above, this resulted in our final sample of 50 participants per group.
 
-Participants completed the experiment in either the Self-Controlled group $(M_{age} = 18.0$, *SD* = 0.34), the Traditional Yoked group $(M_{age} = 19.5$, *SD* = 1.89), or the Explicit Yoked group $(M_{age} = 19.2$, *SD* = 1.55).
+Participants completed the experiment in either the Self-Controlled group $(M_{age} = 18.0$, *SD* = 0.34; \textcolor{red}{32 females}), the Traditional Yoked group $(M_{age} = 19.5$, *SD* = 1.89; \textcolor{red}{28 females}), or the Explicit Yoked group $(M_{age} = 19.2$, *SD* = 1.55; \textcolor{red}{30 females}).
 We collected the Self-Controlled group first as their self-selected observation schedule was required for the yoking procedure for the two other groups.
@@
 Participants answered these questions after the pre-test, after trials five and 25 of acquisition, and before the delayed retention test.
+The values for Cronbach's alpha for each questionnaire at each time point are reported in Table \@ref(tab:table2).
 
 A custom LabVIEW (National Instruments Inc.) program was created that controlled the presentation of all instructions, the video demonstrations, the timing of the experimental protocol, and recorded and stored the data for later analysis.
+
+```{r table2, echo = FALSE, results = "asis"}
+
+table_2 <- tibble(
+    c1 = c("Perceived autonomy",
+           "Perceived competence",
+           "Intrinsic motivation"),
+    c2 = c("0.62",
+           "0.90",
+           "0.86"),
+    c3 = c("0.79",
+           "0.92",
+           "0.90"),
+    c4 = c("0.79",
+           "0.94",
+           "0.92"),
+    c5 = c("0.84",
+           "0.92",
+           "0.92"),
+)
+
+kbl(table_2,
+    booktabs = TRUE,
+    escape = TRUE,
+    linesep = "\\addlinespace",
+    caption = "Cronbach's alpha for each questionnaire at each time point.",
+    col.names = c(" ",
+                  "After pre-test",
+                  "After trial 5",
+                  "After trial 25",
+                  "Before retention")
+    ) %>% 
+    kable_styling(position = "left",
+                  font_size = 11) %>% 
+    column_spec(1, width = "10em") %>% 
+    column_spec(2, width = "6em") %>% 
+    column_spec(3, width = "6em") %>% 
+    column_spec(4, width = "6em") %>% 
+    column_spec(5, width = "7em")
+
+```
 
@@
 A Cook's distance of $\geq 1$ was used to identify any influential cases and none were identified.
+\textcolor{red}{Statistical tests are described below.}
 
@@
 
-To test whether delayed retention (Figure \@ref(fig:fig1)C) was differentially impacted by the experimental group (i.e., Self-Controlled, Traditional Yoked, Explicit Yoked) experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test.
+To test whether delayed retention (Figure \@ref(fig:fig1)C) was differentially impacted by the experimental group experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test.
 As can be seen, the Self-Controlled group $(M = 9.99$, $95\%CI = [9.68,10.31])$, the Traditional Yoked group $(M = 10.18$, $95\%CI = [9.86,10.50])$, and the Explicit Yoked group $(M = 10.12$, $95\%CI = [9.81,10.44])$ all had similar stacking times in retention (means are shown as the adjusted means controlling for pre-test).
@@
 
-```{r table2, echo = FALSE, results = "asis"}
+```{r table3, echo = FALSE, results = "asis"}
 
-table_2 <- tibble(
+table_3 <- tibble(
     Observation = c("Model viewing frequency",
@@
 
-kbl(table_2,
+kbl(table_3,
     booktabs = TRUE,
@@
 
-Model frequency and the video speed request data are reported in Table \@ref(tab:table2).
+Model frequency and the video speed request data are reported in Table \@ref(tab:table3).
 The mean frequency of viewing the video demonstration during acquisition was $16.7\%$.
@@
 
-To further probe the null effects [@harms2018] related to our main predictions, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure [@lakens2018; @schuirmann1987].
+\textcolor{red}{Given our pre-registered analysis resulted in a non-significant finding, we performed two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times using the two one-sided test procedure} [@lakens2018; @schuirmann1987].
+\textcolor{red}{Equivalence tests are a statistical tool that researchers can use to support the absence of a meaningful effect and avoid incorrectly concluded no effect exists based on a non-significant finding} [@harms2018].
 To establish our smallest effect size of interest [@lakens2021] we calculated the effect size our design had 33% power to detect [@simonsohn2015], which was $d_{s} = .31$.
@@
 One explanation for this lack of replicability is that the *"true"* effect of such manipulations are much smaller than previously estimated [@mckay2021].
-Given the resources required (in terms of sample size) to reliably detect these tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either studying practice conditions that have much bigger effects or devising ways to reduce variability and increase power through clever experimental design [@mcclelland2000].
+\textcolor{red}{Given the resources required (in terms of sample size) to reliably detect these tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either by adopting the use of sequential analyses} [@lakens2021; @lakens2014; @wald1945] \textcolor{red}{and/or multi-lab collaborations} [@boland2017] \textcolor{red}{or studying practice conditions that likely have much bigger effects on motor learning.}
 

### 2021-11-04 docs/r1_submission/r1_manuscript.tex
update: finalized changes to revised manuscript

@@
   pdflang={en-EN},
-  pdfkeywords={Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing},
+  pdfkeywords={Motor learning; Pre-registered; Self-controlled; Observation},
   hidelinks,
@@
 \makeatother
-\keywords{Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing\newline\indent Word count: 5055}
+\keywords{Motor learning; Pre-registered; Self-controlled; Observation\newline\indent Word count: 4585}
 \usepackage{lineno}
@@
 
-\textbf{\emph{Public Significance Statement}}\\
-The present study suggests that although university-aged students may experience a boost in feelings of autonomy when given choice over features of their learning environment, this boost does not enhance learning of a new motor skill.
-Additionally, it highlights that coaches and practictioners should be encouraged to incorporate other and more effective practice variables into their training regimes.
+\noindent \textbf{\emph{Public Significance Statement}}\\
+The present study suggests that although university-aged students may experience a boost in feelings of autonomy when given choice over features of their learning environment, this boost may not enhance learning of a new motor skill.
+Our results also highlight the need for higher powered and pre-registered motor learning experiments if coaches and practictioners are to be provided with reliable recommendations for training and rehabilitation protocols.
 }
@@
 
-Over the years, this manipulation has been described using a variety of names (e.g., self- and/or learner-controlled; -regulated; -directed; -selected), but more recently it has been subsumed by autonomy-support.
+Over the years, this manipulation has been described using a variety of names (e.g., self- and/or learner-controlled; -regulated; -directed; -selected), but more recently \textcolor{red}{some researchers have adopted the term} autonomy-support.
 \textcolor{red}{Within their ``OPTIMAL'' theory of motor learning,} Wulf and Lewthwaite (2016) \textcolor{red}{argued that providing learners with opportunities for choice creates an autonomy-supportive practice environment, which facilitates motor performance and learning.
@@
 \textcolor{red}{In contrast,} McKay and Ste-Marie (2020b) \textcolor{red}{recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group.
-However, the higher perceived autonomy scores did not translate into enhanced motor performance or learning in the self-controlled group as predicted in the ``OPTIMAL'' theory.
+However, despite their higher perceived autonomy scores the self-controlled group did not have significantly better motor performance and learning as predicted in the ``OPTIMAL'' theory.
 Although the majority of experiments that included a measure related to perceived autonomy reported no group differences, the ``absence of evidence is not evidence of absence''} (Altman \& Bland, 1995)\textcolor{red}{.
@@
 
-Here we investigated the effects of making participants in a yoked group explicitly aware of not only being denied opportunities for choice over their frequency of watching and the playback speed of video demonstrations, but also that the schedule they would experience during practice was created by another participant in the experiment.
-The addition of this novel yoked group allowed us to address one of the previously identified methodological limitations regarding experimental group instructions in past self-controlled research.
-We compared the performance of this explicit yoked group with traditional self-controlled and yoked groups on a speed cup-stacking task in practice and in a delayed retention test.
+\textcolor{red}{Here, we addressed the methodological limitation of past self-controlled research where participants in the yoked group are unaware that a feature of their practice environment was created by another participant in the experiment.
+To this end, participants learned a speed cup-stacking task in either a self-controlled group, a traditional yoked group, or a novel explicitly aware yoked group.
+The self-controlled group has choice over the frequency of watching a video demonstration and the video playback speed (real-time or slow motion).
+Participants in the traditional and explicit yoked groups were matched to a participant in the self-controlled group and experienced the observation schedule selected by this participant.
+The key difference being that participants in the explicit yoked group were told that the observation schedule they would experience during practice was selected by another participant, whereas participants in the traditional yoked group were not aware of this.
+Motor learning was assessed using a delayed retention test.
+We predicted that the self-controlled group would have significantly faster stacking times in retention than the traditional yoked group.
+In other words, we expected to replicate the typical self-controlled learning advantage.
+If the self-controlled learning advantage results from choice being autonomy-supportive as argued in the ``OPTIMAL'' theory} (Wulf \& Lewthwaite, 2016)\textcolor{red}{, then participants in the self-controlled group should also self-report significantly higher scores for perceptions of autonomy.
+Also based on the view that autonomy-support is the mechanism underlying the typical self-controlled learning advantage} (Wulf \& Lewthwaite, 2016)\textcolor{red}{, we predicted that the explicit yoked group should have significantly slower stacking times in retention.
+Although we found significantly higher perceptions of autonomy in the self-controlled group, there were no significant group differences in stacking times during retention.
+Overall, these results do not support our predictions and are inconsistent with predictions 2, 3, and 7 in the ``OPTIMAL'' theory of motor learning} (Wulf \& Lewthwaite, 2016).
 
@@
 
-One-hundred and fifty participants completed the experiment.
-Sample size was determined by an a priori power calculation based on our smallest comparison of interest.
+One-hundred and fifty \textcolor{red}{university students} participated in the experiment.
+Sample size was determined by an a priori power calculation based on our smallest comparison of interest \textcolor{red}{using GLIMMPSE (https://glimmpse.samplesizeshop.org/)}.
 An early estimate for the effect of self-controlled over yoked practice was a Hedges' \(g = 0.63\) (McKay, Carter, \& Ste-Marie, 2014) and while planning this experiment this effect was estimated to be \(g = 0.52\) (Z.
 Yantha, personal communication, October 2019).
-Based on this effect, a positive correlation of \(r = 0.6\) between retention and pre-test as the covariate, and 80\% power to detect a difference between the self-controlled and traditional yoked groups, the required number of participants was 31 per group.
+Based on this effect, a positive correlation of \(r = 0.6\) between retention and pre-test as the covariate, \textcolor{red}{an alpha of 0.05}, and 80\% power to detect a difference between the self-controlled and traditional yoked groups, the required number of participants was 31 per group.
 Considering the novelty of our Explicit Yoked group, we assumed a smaller effect, \(g = 0.4\), between it and the Traditional Yoked group.
-With the same parameters as above, this resulted in our final sample of 50 participants per group.
-
-Participants completed the experiment in either the Self-Controlled group \((M_{age} = 18.0\), \emph{SD} = 0.34), the Traditional Yoked group \((M_{age} = 19.5\), \emph{SD} = 1.89), or the Explicit Yoked group \((M_{age} = 19.2\), \emph{SD} = 1.55).
+\textcolor{red}{Using this effect and} the same parameters as above, this resulted in our final sample of 50 participants per group.
+
+Participants completed the experiment in either the Self-Controlled group \((M_{age} = 18.0\), \emph{SD} = 0.34; \textcolor{red}{32 females}), the Traditional Yoked group \((M_{age} = 19.5\), \emph{SD} = 1.89; \textcolor{red}{28 females}), or the Explicit Yoked group \((M_{age} = 19.2\), \emph{SD} = 1.55; \textcolor{red}{30 females}).
 We collected the Self-Controlled group first as their self-selected observation schedule was required for the yoking procedure for the two other groups.
@@
 Participants answered these questions after the pre-test, after trials five and 25 of acquisition, and before the delayed retention test.
+The values for Cronbach's alpha for each questionnaire at each time point are reported in Table \ref{tab:table2}.
 
 A custom LabVIEW (National Instruments Inc.) program was created that controlled the presentation of all instructions, the video demonstrations, the timing of the experimental protocol, and recorded and stored the data for later analysis.
+
+\begin{table}
+
+\caption{\label{tab:table2}Cronbach's alpha for each questionnaire at each time point.}
+\fontsize{11}{13}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{7em}}
+\toprule
+  & After pre-test & After trial 5 & After trial 25 & Before retention\\
+\midrule
+Perceived autonomy & 0.62 & 0.79 & 0.79 & 0.84\\
+\addlinespace
+Perceived competence & 0.90 & 0.92 & 0.94 & 0.92\\
+\addlinespace
+Intrinsic motivation & 0.86 & 0.90 & 0.92 & 0.92\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 A Cook's distance of \(\geq 1\) was used to identify any influential cases and none were identified.
+\textcolor{red}{Statistical tests are described below.}
 
@@
 
-To test whether delayed retention (Figure \ref{fig:fig1}C) was differentially impacted by the experimental group (i.e., Self-Controlled, Traditional Yoked, Explicit Yoked) experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test.
+To test whether delayed retention (Figure \ref{fig:fig1}C) was differentially impacted by the experimental group experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test.
 As can be seen, the Self-Controlled group \((M = 9.99\), \(95\%CI = [9.68,10.31])\), the Traditional Yoked group \((M = 10.18\), \(95\%CI = [9.86,10.50])\), and the Explicit Yoked group \((M = 10.12\), \(95\%CI = [9.81,10.44])\) all had similar stacking times in retention (means are shown as the adjusted means controlling for pre-test).
@@
 
-\caption{\label{tab:table2}The mean frequencies for each Acquisition block of requesting to watch the video demonstration and of those requests, the mean frequency of choosing the regular viewing speed.}
+\caption{\label{tab:table3}The mean frequencies for each Acquisition block of requesting to watch the video demonstration and of those requests, the mean frequency of choosing the regular viewing speed.}
 \fontsize{11}{13}\selectfont
@@
 
-Model frequency and the video speed request data are reported in Table \ref{tab:table2}.
+Model frequency and the video speed request data are reported in Table \ref{tab:table3}.
 The mean frequency of viewing the video demonstration during acquisition was \(16.7\%\).
@@
 
-To further probe the null effects (Harms \& Lakens, 2018) related to our main predictions, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure (Lakens, Scheel, \& Isager, 2018; Schuirmann, 1987).
-To establish our smallest effect size of interest (Lakens, 2021) we calculated the effect size our design had 33\% power to detect (Simonsohn, 2015), which was \(d_{s} = .31\).
+\textcolor{red}{Given our pre-registered analysis resulted in a non-significant finding, we performed two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times using the two one-sided test procedure} (Lakens, Scheel, \& Isager, 2018; Schuirmann, 1987).
+\textcolor{red}{Equivalence tests are a statistical tool that researchers can use to support the absence of a meaningful effect and avoid incorrectly concluded no effect exists based on a non-significant finding} (Harms \& Lakens, 2018).
+To establish our smallest effect size of interest (Lakens, Pahlke, \& Wassmer, 2021) we calculated the effect size our design had 33\% power to detect (Simonsohn, 2015), which was \(d_{s} = .31\).
 The Self-Controlled and Traditional Yoked groups were not statistically different, \(t(97.99) = -0.830\), \(p = 0.409\), and not statistically equivalent, \(t(97.99) = 0.720\), \(p = 0.237\), given equivalence bounds of \(-.355\) and \(.355\) (on a raw scale).
@@
 This recent lack of support may arise from the self-controlled learning advantage being a much smaller effect than originally estimated (\(g = 0.63\) by McKay et al.~2014).
-A more recent estimate of this effect from a meta-analysis using a weight-function model was \(g = .11, \,95\% CI = [.047, .18]\) (McKay, Yantha, Hussien, Carter, \& Ste-Marie, 2021).
+A more recent estimate of this effect from a meta-analysis using a weight-function model was \(g = .11, \,95\% CI = [.047, .18]\) (McKay, Yantha, Hussien, Carter, \& Ste-Marie, Accepted).
 This estimate was further reduced to \(g = .054\) after controlling for publication bias using the precision-effect estimate with standard error (PEESE) method.
@@
 In our experiment, the estimated effect size of self-controlled versus yoked (collapsed across our Traditional and Explicit Yoked groups) was \(g = 0.22\).
-While this estimate is larger than those from the weight-function model and PEESE method, it does fall within the range of plausible effect sizes (McKay et al., 2021).
+While this estimate is larger than those from the weight-function model and PEESE method, it does fall within the range of plausible effect sizes (McKay et al., Accepted).
 When the lack of a self-controlled advantage in previous work and our current experiment are contextualized within the findings of this recent meta-analysis, it is not as surprising that the so-called self-controlled learning benefit was not replicated.
@@
 Using the upper bound, \(g = .26\), of the range of plausible effects, \emph{253 participants} are required to have 80\% power to detect this effect in retention using an independent-samples \emph{t}-test.
-The number of participants jumps to \emph{1300 per group}, if for instance the estimate from the weight-function model, \(g = .11\), is accurate (McKay et al., 2021).
+The number of participants jumps to \emph{1300 per group}, if for instance the estimate from the weight-function model, \(g = .11\), is accurate (McKay et al., Accepted).
 Given the field of motor learning suffers from a lack of adequately powered designs (Lohse et al., 2016) and that underpowered designs are more likely to produce false positives and overestimated effect sizes (Button et al., 2013), we are skeptical of the replicability of the previous overwhelming support for the self-controlled learning advantage.
@@
 Ultimately, our results add to a growing body of evidence that questions whether autonomy-supportive manipulations directly affect motor learning.
-One explanation for this lack of replicability is that the \emph{``true''} effect of such manipulations are much smaller than previously estimated (McKay et al., 2021).
-Given the resources required (in terms of sample size) to reliably detect these tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either studying practice conditions that have much bigger effects or devising ways to reduce variability and increase power through clever experimental design (McClelland, 2000).
+One explanation for this lack of replicability is that the \emph{``true''} effect of such manipulations are much smaller than previously estimated (McKay et al., Accepted).
+\textcolor{red}{Given the resources required (in terms of sample size) to reliably detect these tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either by adopting the use of sequential analyses} (Lakens, 2014; Lakens et al., 2021; Wald, 1945) \textcolor{red}{and/or multi-lab collaborations} (Boland, Karczewski, \& Tatonetti, 2017) \textcolor{red}{or studying practice conditions that likely have much bigger effects on motor learning.}
 
@@
 \url{https://doi.org/10.1016/j.humov.2018.12.002}
+
+\leavevmode\vadjust pre{\hypertarget{ref-boland2017}{}}%
+Boland, M.
+R., Karczewski, K.
+J., \& Tatonetti, N.
+P.
+(2017).
+Ten simple rules to enable multi-site collaborations through data sharing.
+\emph{PLOS Computational Biology}, \emph{13}, 1--12.
+\url{https://doi.org/10.1371/journal.pcbi.1005278}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-lakens2014}{}}%
+Lakens, D. (2014). Performing high-powered studies efficiently with sequential analyses. \emph{European Journal of Social Psychology}, \emph{44}(7), 701--710. \url{https://doi.org/10.1002/ejsp.2023}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-TOSTER}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lakens2021}{}}%
-Lakens, D. (2021). \emph{Sample size justification}. \url{https://doi.org/10.31234/osf.io/9d3yf}
+Lakens, D., Pahlke, F., \& Wassmer, G. (2021). Group sequential designs: A tutorial. \emph{Psyarxiv}. \url{https://doi.org/10.31234/osf.io/x4azm}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-mcclelland2000}{}}%
-McClelland, G.
-H.
-(2000).
-Increasing statistical power without increasing sample size.
-\emph{American Psychologist}, \emph{55}(8), 963--964.
-https://doi.org/\url{https://psycnet.apa.org/doi/10.1037/0003-066X.55.8.963}
-
 \leavevmode\vadjust pre{\hypertarget{ref-mckay2014}{}}%
-McKay, B., Carter, M. J., \& Ste-Marie, D. M. (2014). Self-controlledlearning: A meta-analysis. \emph{Journal of sport \& exercise psychology,} \emph{36}, S43.
+McKay, B., Carter, M. J., \& Ste-Marie, D. M. (2014). Self-controlled learning: A meta-analysis. \emph{Journal of sport \& exercise psychology,} \emph{36}, S43.
 
@@
 M.
-(2021).
-\emph{Meta-analytic findings in the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value}.
+(Accepted).
+Meta-analytic findings in the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value.
+\emph{Meta-Psychology}.
 \url{https://doi.org/10.31234/osf.io/8d3nb}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wald1945}{}}%
+Wald, A. (1945). Sequential tests of statistical hypotheses. \emph{The Annals of Mathematical Statistics}, \emph{16}(2), 117--186. \url{https://doi.org/10.1214/aoms/1177731118}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%

### 2021-11-04 docs/r1_submission/r1_responses-to-reviewers.Rmd
update: finalized response letter

@@
 
-We agree with the reviewer that an information-processing explanation has also been forwarded to account for the self-controlled learning advantages.
-We did not not specifically refer to it in the introduction as this experiment was not designed to dissociate between the motivational and the information-processing explanations.
-We have removed the quoted text in the revised submission and have added the following as a footnote to acknowledge the information-processing view **(see Page XX)**:
+We agree with that an information-processing explanation has also been forwarded to account for the self-controlled learning advantages.
+We did not not specifically refer to it in the Introduction as this experiment was not designed to test between the motivational and the information-processing explanations.
+We have removed the quoted text in your comment in the revised submission and have added the following as a footnote to acknowledge the information-processing view (see Page 5):
 
@@
 We restricted our discussion of past work not including measures in the Discussion as the true impact of this unknown and speculative.
-Based on your comments, we have restructured part of the Introduction to improve the clarity of our arguments **(see Pages XX, Lines XX)**:
+Based on your comments, we have restructured part of the Introduction to improve the clarity of our arguments (see Pages 5-6, Lines 5-20 and 1-9):
 
@@
 In contrast, McKay and Ste-Marie (2020b) recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group.
-However, the higher perceived autonomy scores did not translate into enhanced motor performance or learning in the self-controlled group as predicted in the “OPTIMAL” theory.
+However, despite their higher perceived autonomy scores the self-controlled group did not have significantly better motor performance and learning as predicted in the “OPTIMAL” theory.
 Although the majority of experiments that included a measure related to perceived autonomy reported no group differences, the “absence of evidence is not evidence of absence” (Altman & Bland, 1995).
@@
 The title of our paper and how the discussion unfolds is based on the results of our experiment, which suggests that increased perceptions of autonomy do not benefit motor learning.
-To your first point, we have added the following to the introduction to better outline how autonomy-support might have a mechanistic role in motor performance and learning according to the "OPTIMAL" theory of motor learning **(see Pages XX, Lines XX)**:
+To your first point, we have added the following to the introduction to better outline how autonomy-support might have a mechanistic role in motor performance and learning according to the "OPTIMAL" theory of motor learning (see Pages 4-5, Lines 18-27 and 1-4):
 
@@
 Are the authors interested in detecting group differences in levels of perceived autonomy (regardless of whether it predicts learning) or in the role of autonomy-support in enhancing learning (i.e., replicate the self-control learning benefit under a motivational perspective)?
-The issue gets even more cloudy as the authors raise two methodological concerns identified in the autonomy-support literature: 1) "The first of these is that in self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component of their practice and participants in the yoked group are not given choice over this component.
+The issue gets even more cloudy as the authors raise two methodological concerns identified in the autonomy-support literature: 1) "The first of these is that in self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component of their practice and participants inThank you for the positive comments about our manuscript the yoked group are not given choice over this component.
 However, within the context of practice itself there are many other opportunities for choice that participants may explore, independent of their assigned group" [Page6, line 4], and 2) "The other consideration relates to the instructions that are provided to participants in the yoked group [Page 6, line 16]", "Participants in yoked groups are not even aware that they have been denied an opportunity for choice, nor that their feedback schedule was created by another participant who was given choice over when feedback was or was not provided" [Page 6, line 20].
@@
 We have added details about our predictions to the revised manuscript (but we include this information below with your specific comment about these missing from the manuscript).
-In terms of the first methodological limitation, yes some researchers have reported a learning benefit of task-irrelevant choices (e.g., Lewthwaite & Wulf 2015); however, this is a fairly selective stance given the mixed results surrounding task-irrelevant choices (e.g., Carter & Ste-Marie 2017; Grand et al.
+In terms of the first methodological limitation, yes some researchers have reported a learning benefit of task-irrelevant choices (e.g., Lewthwaite & Wulf 2015; Wulf et al.
+2017); however, this is a fairly selective stance given the mixed results surrounding task-irrelevant choices (e.g., Carter & Ste-Marie 2017; Grand et al.
 2015; McKay & Ste-Marie 2020ab).
-In McKay & Ste-Marie 2020a, the task-irrelevant choice groups actually performed with significantly more error in the acquisition and transfer.
+Additionally, in McKay & Ste-Marie 2020a the task-irrelevant choice groups actually performed with significantly more error in acquisition and transfer than their yoked counterparts.
+As such, we respectfully disagree with your comment regarding the first methodoloThank you for the positive comments about our manuscriptgical limitation.
+Regarding the second methodological issue, we did not assert that making a yoked group aware that another participant created their observation schedule would prevent them from being able to experience other choice opportunities as we discuss in the Introduction.
+Instead, we outlined the methodological issues and acknowledged that "Either of these in isolation, or both simultaneously could contribute to the consistent finding that participants in self-controlled and yoked groups report similar perceived autonomy scores..." (Page 8, Lines 22-24 in original submission).
+We decided to only address the issue surrounding instructions with our manipulation as targeting all of the issues with the choice as autonomy-supportive literature would complicate our experimental design and likely contribute to an already messy and inconsistent body of literature as you have described in your review.
+
+Although the reviewer raises an interesting parallel with the controlling versus autonomy-supportive language manipulation, we respectfully disagree that our manipulation is better fitted under this area.
+In Hooyman et al.
+2014, the controlling instructions are very specific and describe exactly how the learner must execute the task:
+
+"Your job today will be to learn a cricket pitch and perform it well.
+You may not begin throwing until you are told so.
+Make sure all of the tennis balls are in their respective holders.
+You may only remove one tennis ball at a time.
+Once you have been told when to commence throwing you must maintain a consistent pace.
+When initiating the approach of the pitch you must cradle the ball so it travels in a circular pattern.
+At the apex of the pitch the ball must be directly over the shoulder.
+Do not throw it at a side angle.
+When initiating the release you need to focus on the center of the target or the bounce area below the target" (Hooyman et al.
+2014, p.
+193).
+
+Contrast this with our Explicit Yoked group instructions:
+
+"Before each trial, you may or may not watch a modeled demonstration of the task based on the schedule another participant selected.
+If you observe a model, it might be presented in real-time or in slow-motion based on what that participant selected."
+
+Compared to the instructions in Hooyman et al.
+2014, our instructions are far more generic in terms of their upcoming practice environment and we make no statements regarding how the task must be executed.
+Instead, the denial of choice regarding the observation schedule is fairly subtle.
+Had we explicitly stated something along the lines of "This means you have been denied choice over your observation schedule" then we would agree such instructions would fit under the controlling language manipulation.
+
+\RC{\emph{Overall, the introduction in its current form do not lead up to the research question nor does it highlight the relevance of the study.
+Are the authors manipulating autonomy support or autonomy restriction?
+It seems like the Explicit Yoked group is what makes this study unique (according to the authors), and yet little-to-no attention is given as to how the addition of this group can help to fill previously identified knowledge gaps in the self-control/autonomy support literature.
+I urge the authors to restructure the introduction in such way that the rationale, novelty, and relevance of the study are more evident.
+}}
+
+Our manipulations relate to choice (self-controlled or yoked) over observation schedule.
+As presented in our Introduction, it is far from clear whether such manipulations impact autonomy one way or the other.
+We have made changes throughout the introduction (as described above), but also have restructured the final paragraph of the Introduction based on your comments (see Pages 7-8, Lines 11-27, 1-8):
+
+> Here, we addressed the methodological limitation of past self-controlled research where participants in the yoked group are unaware that a feature of their practice environment was created by another participant in the experiment.
+To this end, participants learned a speed cup-stacking task in either a self-controlled group, a traditional yoked group, or a novel explicitly aware yoked group.
+The self-controlled group has choice over the frequency of watching a video demonstration and the video playback speed (real-time or slow motion).
+Participants in the traditional and explicit yoked groups were matched to a participant in the self-controlled group and experienced the observation schedule selected by this participant.
+The key difference being that participants in the explicit yoked group were told that the observation schedule they would experience during practice was selected by another participant, whereas participants in the traditional yoked group were not aware of this.
+Motor learning was assessed using a delayed retention test.
+We predicted that the self-controlled group would have significantly faster stacking times in retention than the traditional yoked group.
+In other words, we expected to replicate the typical self-controlled learning advantage.
+If the self-controlled learning advantage results from choice being autonomy-supportive as argued in the “OPTIMAL” theory (Wulf & Lewthwaite, 2016), then participants in the self-controlled group should also self-report significantly higher scores for perceptions of autonomy.
+Also based on the view that autonomy-support is the mechanism underlying the typical self-controlled learning advantage (Wulf & Lewthwaite, 2016), we predicted that the explicit yoked group should have significantly slower stacking times in retention.
+Although we found significantly higher perceptions of autonomy in the self-controlled group, there were no significant group differences in stacking times during retention.
+Overall, these results do not support our predictions and are inconsistent with predictions 2, 3, and 7 in the “OPTIMAL” theory of motor learning (Wulf & Lewthwaite, 2016).
+
+\RC{\emph{Still regarding the introduction, the authors did not mention their pre-registered hypotheses.
+Although they are available in the pre-registration form, it is important to include them in the manuscript.
+The inclusion of predicted outcomes, especially when they have been pre-registered, is crucial not only to help the reader to better understand the study's rationale, but also when we consider how studies might be used in the future.
+In the case of meta-analyses, for instance, studies may go through a quality assessment (that might include questions about the presence of previously established hypotheses) or be used in additional analyses such as the p-curve, in which researchers report a disclosure table where a number of questions need to be addressed, and one of them is specific to the presence/absence of clear hypotheses.
+}}
+
+We have fixed this oversight and included our predictions at the end of the Introduction as shown in the above response.
+
+\RC{\emph{Page 5, line 2: "Overall, autonomy-support is seen as a mean [there is an extra 's' here] to efficient goal-action coupling (Wulf \& Lewthwaite, 2016) and also links the "OPTIMAL" theory with Self-Determination theory (Deci \& Ryan, 2000)." To aid a reader who might not be familiar the SDT, expand on how the OPTIMAL theory is linked to the SDT.
+}}
+
+Based on earlier comments, this text has been removed from the revised manuscript.
+
+\RC{\emph{Although sample size calculation is somewhat specified in the pre-registration, it lacks important details that would allow the analysis to be replicated.
+Add a more detailed description of how sample size was calculated (e.g., software used and parameters adopted).
+}}
+
+We have included the program used to conduct the sample size calculation.
+We did notice that alpha was not specifically mentioned in the manuscript for the sample size calculation, which we have fixed plus some minor edits (see Page 8, Line 21).
+However, we are unsure what additional parameters you expect for a more detailed description of how sample size was calculated.
+
+\RC{\emph{Regarding the self-reported measures of perceived autonomy, intrinsic motivation, and perceived competence: report a measure of internal consistency for these questionnaires (e.g., Cronbach's alpha).
+}}
+
+We have added this information in a table (see Page 12).
+
+\RC{\emph{The ratio of males and females was not reported.
+Again, when we consider the use of studies in meta-analytic approaches, one might want to carry out moderator analyses based on sex to make inferences about an effect, hence the importance of providing this type of information.
+}}
+
+We have added this information (see Page 9, Lines 2-3).
+
+\RC{\emph{Participants only requested to watch the demonstrations 16.7\% of the time on average.
+This seems a very small number and I wonder whether the authors thought about how this might have affected their results.
+}}
+
+While the mean frequency of observation (16.7%) is small relative to the frequency that feedback is typically requested (usually >60% when given choice after every trial), it is in line with previous research where participants had control of the frequency of modeled demonstrations: Wrisberg and Pein (2002) reported a frequency of 9.8% and Wulf, Raupach, & Pfeiffer (2005) reported a frequency of 5.8%.
+Given this, we do not think the requested frequency affected our results and importantly, frequency was controlled across groups.
+
+\RC{\emph{Page 15, line 7: "To further probe the null effects (Harms \& Lakens, 2018) related to our main predictions".
+Here the authors allude to their predictions, but such predictions were not mentioned in the manuscript.
+}}
+
+We have added this information based on your earlier comment (see Pages 7-8, Lines 11-27, 1-8).
+
+\RC{\emph{Page 21, line 26.
+"Given the resources required (in terms of sample size) to reliably detect these tiny effects, we encourage motor learning scientists to invest their limited resources carefully—either studying practice conditions that have much bigger effects or devising ways to reduce variability and increase power through clever experimental design".
+Include some examples on how future studies may design more clever and efficient experiments (e.g., the use of sequential analysis, collaboration between labs, etc.).
+}}
+
+We have expanded this to include these suggestions (see Page 23, Lines 7-12).
+
+\RC{\emph{It is interesting to see how the manipulation affected perceived autonomy but not levels of intrinsic motivation.
+In both Sanli et al.
+(2013) and Wulf and Lewthwaite (2016), the authors discuss how practice conditions in which one's perception of autonomy is supported lead to enhanced intrinsic motivation and, consequently, better motor learning.
+Did intrinsic motivation predict post-test performance regardless of group?
+If so, this finding would be consistent with the OPTIMAL theory's claim that motivation plays an important role in motor learning.
+Also, is it possible that the instrument used to index intrinsic motivation was not sensitive enough to capture changes in motivation levels?
+There is some research showing that different measures of motivation predict different aspects of a task (see Brunstein \& Schmitt, 2004).
+The authors briefly mention these findings in the discussion section but in a vague manner.
+For example: "Overall, our results are inconsistent with key predictions of the "OPTIMAL" theory regarding autonomy-support and enhanced expectancies…" [Page 21, line 7].
+What predictions exactly?
+}}
+
+The measured related to intrinsic motivation used in the present experiment is consistent with that used in previous experiments (e.g., Barros et al.
+2019).
+While Sanli et al.
+(2013) and Wulf and Lewthwaite (2016) discuss how perceived autonomy through choice can enhance intrinsic motivation and better motor learning, Ste-Marie et al.
+(2015) ran a path analysis and showed that intrinsic motivation is not predictive of the self-controlled learning advantage.
+We elected to not run an exploratory analysis to test whether intrinsic motivation predicted post-test performance, regardless of group.
+We believe this not only detracts from the main question of our experiment, but there is not prediction in the "OPTIMAL" theory surrounding intrinsic motivation predicting post-test performance, independent of group.
+As mentioned in one of our earlier responses, we have made specific reference to the relevant predictions in the "OPTIMAL" theory (see Pages 4-5, Lines 18-27 and 1-4).
 
@@
 
-This is our response.
+Thank you for the positive comments about our manuscript.
 
-> This is a section quoted from the revised manuscript to illustrate the change.
+\RC{\emph{Public significance statement, Lines 21-23, what kind of effective practice variable should coaches and practitioners use?
+Autonomy support affects skill learning among various populations.
+For instance: (https://www.tandfonline.com/doi/abs/10.1080/17461391.2020.1720829)
+}}
 
-\clearpage
+Based on your comment and some reflection/discussions among ourselves, we decided to modify our public significance statement to the following:
 
-# References
+> The present study suggests that although university-aged students may experience a boost in feelings of autonomy when given choice over features of their learning environment, this boost may not enhance learning of a new motor skill.
+Our results also highlight the need for higher powered and pre-registered motor learning experiments if coaches and practictioners are to be provided with reliable recommendations for training and rehabilitation protocols.
 
-\begingroup
+\RC{\emph{Equivalence tests? Why is it important? I have little experience with equivalence tests.
+}}
 
-<div id="refs"></div>
+When a null hypothesis significance test returns a non-significant result, many researchers incorrectly conclude that there is no effect or that groups are not different.
+Equivalence tests provide a statistical tool that researchers can use to support the absence of a meaningful effect.
+In other words, an equivalence test can help researchers conclude that a non-zero difference between groups is practically equivalent to zero.
 
-\endgroup
+\RC{\emph{Page 4, lines 17-20, does autonomy support differ between adults and children? Can you explain the findings of this study?
+}}
+
+The reference here is to the paper that introduces the "OPTIMAL" theory of motor learning, which argues that the learning benefits of self-controlled practice conditions are "very robust and generalizable to different tasks, age groups, and populations (p.
+1393).
+
+\RC{\emph{Lines 23-24 review the sentence.
+}}
+
+This sentence has been removed in the revised manuscript based on comments from Reviewer 2.
+
+\RC{\emph{In lines 25-27 you mention previous literature does not indicate that self-controlled practice is autonomy-supportive, but in lines 17-18, p.4, you say a variety of names and labeled them as autonomy-supportive.
+Could you clarify this?
+}}
+
+We have updated our wording in these lines to clarify our position as our intention was not to label these names as being autonomy-supportive. This part now reads as (see Page 4, Lines 16-21):
+
+> Over the years, this manipulation has been described using a variety of names (e.g., self- and/or learner-controlled; -regulated; -directed; -selected), but more recently some researchers have adopted the term autonomy-support.
+Within their “OPTIMAL” theory of motor learning, Wulf and Lewthwaite (2016) argued that providing learners with opportunities for choice creates an autonomy-supportive practice environment, which facilitates motor performance and learning.
+
+\RC{\emph{ What was your hypothesis or prediction? Did your results support the hypothesis?
+}}
+
+We have added this information (see Pages 7-8, Lines 22-27 and 1-7):
+
+> We predicted that the self-controlled group would have significantly faster stacking times in retention than the traditional yoked group.
+In other words, we expected to replicate the typical self-controlled learning advantage.
+If the self-controlled learning advantage results from choice being autonomy-supportive as argued in the “OPTIMAL” theory (Wulf & Lewthwaite, 2016), then participants in the self-controlled group should also self-report significantly higher scores for perceptions of autonomy.
+Also based on the view that autonomy-support is the mechanism underlying the typical self-controlled learning advantage (Wulf & Lewthwaite, 2016), we predicted that the explicit yoked group should have significantly slower stacking times in retention.
+Although we found significantly higher perceptions of autonomy in the self-controlled group, there were no significant group differences in stacking times during retention.
+Overall, these results do not support our predictions and are inconsistent with predictions 2, 3, and 7 in the “OPTIMAL” theory of motor learning (Wulf & Lewthwaite, 2016).
+
+\RC{\emph{Thank you for providing additional material at asPredicted.org, it was very beneficial.
+}}
+
+You're welcome.
+
+\RC{\emph{Lines 18-19, p.7, what age are the participants? Where were they recruited from? Who are we looking at? (e.g., university students, adults, etc.)?
+}}
+
+We have made specific reference that the participants were university students at the start of the Participants section (see Page 8, Line 15).
+It seems like the reported mean age of the participants in each group was missed.
+This information is also reported in the Participants section.
+
+\RC{\emph{There was only one analysis explained, it would help if you discussed all analyses. Explain the analysis you ran in your data analysis section. 
+}}
+
+We described all analyses in the Results section as a way to reduce the cognitive load placed on the reader.
+We believe this prevents the reader from having to either remember all statistical analyses by the time they reach the Results section or having to scroll back and forth between the Data analysis section and the Results section.
+We have added a line to the Data analysis section that informs the reader that statistical tests are described below (see Page 12, Line 9).
+
+\RC{\emph{Why do you have other graphs? You did not run an analysis on each trial but ran three by five.
+}}
+
+We have additional figures for transparency and for the interested reader.
+Figures 1A and 1D further support the pattern of results in Figures 1B and 1C and the associated outcomes of the statistical tests.
+
+\RC{\emph{p.12, figure 1C, adjusted time is not explained in the results; what is adjusted mean stacking? Some of the graphs can be removed from the paper.
+}}
+
+Adjusted mean stacking time is stacking time in the retention test, adjusted for pre-test scores.
+We think our explanation for this may have been missed.
+In the Results section, we stated that "means are shown as the adjusted means controlling for pre-test" and the figure caption for 1C is "Mean stacking time (s) adjusted for pre-test for each group".
+We have elected to not removed any figures based on our response in the above comment.
+
+\RC{\emph{Lines 10-17, p.13, please indicate the figure the reader should reference with your results. What graph is to be looked at when you ran your analysis? 
+}}
+
+We think our reference to which figures to look may have been overlooked as these were included in the relevant subsections of the Results section.
+
+\RC{\emph{p.13, why did you use a Welch's t-test to compare two groups? Why not run a Welch's ANOVA between the three experimental groups? You had three experimental groups but only analyzed two, why?
+}}
+
+The analysis involving all three groups was run in our pre-registered analysis.
+As mentioned in the subsection Traditional self-controlled learning advantage, testing for a the typical self-controlled learning advantage involves a comparison between the Self-Controlled group and the Traditional Yoked group.
+This is why a Welch's t-test was used to test for this non-preregistered analysis.
+
+\RC{\emph{p.16, figure 2, I don't understand why you did this instead of bar graphs.
+To highlight group differences, why not use bar graphs instead of having every single data point on it.
+If no self-control effect was found, how can we trust the questionnaire data?
+}}
+
+Bar graphs have been criticized as many different datasets can produce the same bar graph (see Figure 1 in Weissgerber et al.
+2015, https://doi.org/10.1371/journal.pbio.1002128).
+For this reason, we show the individual data points in addition to the group mean for greater transparency.
+
+This is a reasonable question; however, we are not sure a self-controlled learning advantage is required to trust questionnaire data.
+Despite the claim that the provision of choice is a very robust and generalizable learning variable in the "OPTIMAL" theory, the recent meta-analysis of the self-controlled literature we highlight in the discussion strongly challenges this assertion (McKay et al.
+Accepted).
+Thus, the provision of choice may only exert an influence on perceptions of autonomy (if you have a large enough sample size to detect this small effect), which in itself may be a desired outcome in some situations.
+
+\RC{\emph{Can you explain why you have pre-registered and registered analyses separate? Why is a one-way ANCOVA the only pre-registered analysis?
+}}
+
+The ANCOVA is our only pre-registered analysis as this was our first time doing a pre-registration and we overlooked specifying the other analyses typically run in a self-controlled motor learning experiment.
+It is for this reason, we separated our analyses into a Pre-registered analysis and Non pre-registered analyses to be transparent that only one analysis was pre-registered.
+
+\RC{\emph{Can you address the equivalence tests? Most motor learning researchers are not familiar with these tests, why are equivalence tests used and needed in this study? 
+}}
+
+We have added a description for why we included equivalance tests in the present experiment (see Page 16, Lines 7-13):
+
+> Given our pre-registered analysis resulted in a non-significant finding, we performed two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times using the two one-sided test procedure (Lakens et al., 2018; Schuirmann, 1987).
+Equivalence tests are a statistical tool that researchers can use to support the absence of a meaningful effect and avoid incorrectly concluded no effect exists based on a non-significant finding (Harms & Lakens, 2018).
+
+\RC{\emph{How many papers use cup stacking?
+How do you know that it is not the task itself?
+Could the issue be with the task you chose?
+Why not use a task that is commonly used in motor learning?
+Is it an issue with the task, or is it an issue with the manipulation?
+In summary, this research is interesting and well done.
+When major revisions are addressed, the authors should take advantage of the interesting information available to them and try to publish this work.
+}}
+
+We did a quick google scholar search for "motor learning cup stacking", which resulted in over 6500 papers.
+This is in line with our perception that cup-stacking is a commonly used task in motor learning research.
+Thus, we do not think a task argument is valid for the lack of a self-controlled learning advantage.
+We think the underlying issue is that the view within the "OPTIMAL" theory that self-controlled practice conditions are a very robust and generalizable learning variable is simply wrong as supported by the trivial effects found in the meta-analysis by McKay and colleagues.
+As mentioned in the Discussion section, our estimated effect for self-controlled versus yoked fell within the plausible range of these trivial effects.
+
+<!-- \clearpage -->
+
+<!-- # References -->
+
+<!-- \begingroup -->
+
+<!-- <div id="refs"></div> -->
+
+<!-- \endgroup -->

### 2021-12-28 docs/preprint/preprint.Rmd
update: submission and preprint dirs
update: accepted version

--- 2021-05-20 docs/submission/manuscript.Rmd
@@
 ---
-title             : "Increased perceptions of autonomy through choice fail to enhance motor skill retention"
+title             : "Increased perceptions of autonomy through choice over one's observation schedule fail to enhance motor skill retention"
 shorttitle        : "Autonomy-support does not benefit motor learning"
@@
 
-  We have outlined author contributions using CRediT (Contributor Roles Taxonomy - https://casrai.org/credit/).
+  Preregistration: https://aspredicted.org/ze8cj.pdf
+
+  Data, code, and materials: https://github.com/cartermaclab/expt_explicit-yoked
+
+  PsyArXiv preprint: https://doi.org/10.31234/osf.io/s34fg \vspace{1em}
 
@@
 
-keywords          : "Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing"
-#wordcount         : "4926"
+keywords          : "Motor learning; Pre-registered; Self-controlled; Observation"
+#wordcount         : ""
 bibliography      : ["../references.bib", "../r-references.bib"]
@@
 
-csl               : "../apa-single-spaced.csl"
 documentclass     : "apa7"
-classoption       : "man" # man for manuscript & jou for journal
+classoption       : "doc, donotrepeattitle" # man for manuscript & jou for journal
 output            : papaja::apa6_pdf
 header-includes   :
-  - \pagewiselinenumbers
+  - \usepackage{pdflscape}
+  # - \pagewiselinenumbers
   - \raggedbottom
-  - \leftheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
-  - \rightheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
+  # - \leftheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
+  # - \rightheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
   #- \hypersetup{draft} # comment out after but right now will prevent error message about some link spanning multiple pages
@@
 
+\vspace{-0.5em}
+\noindent
+\begin{center}
+\textcolor{blue}{Accepted for publication in \emph{Journal of Experimental Psychology: Human Perception \& Performance}}
+\end{center}
+
+\vspace{0.5em}
+
 A popular recommendation in recent years for creating an effective environment for motor skill learning has been to allow the learner to take control over an element of their practice that is traditionally controlled by a coach, therapist, or teacher [@sanli2013; @ste-marie2019].
@@
 
-Over the years, this manipulation has been described using a variety of names (e.g., self- and/or learner-controlled; -regulated; -directed; -selected), but more recently it has been subsumed by autonomy-support.
-In fact, autonomy-support is considered such a robust learning variable that it is one of three key pillars in the recently proposed "OPTIMAL" theory of motor learning [@wulf2016].
-@wulf2016 argued that providing learners with opportunities for choice---considered an autonomy-supportive practice manipulation---can facilitate motor performance and learning by enhancing learner's expectancies for success, and by allowing the learner to maintain their attentional focus on the task by reducing the need for self-regulatory activity [@abdollahipour2017; @chua2018; @wulf2018].
-In other words, these psychological and attentional benefits, and concomitant increases in performance and learning are a by-product of exercising choice during practice.
-Overall, autonomy-support is seen as a means to efficient goal-action coupling [@wulf2016] and also links the "OPTIMAL" theory with Self-Determination theory [@deci2000].
+Over the years, this manipulation has been described using a variety of names (e.g., self- and/or learner-controlled; -regulated; -directed; -selected), but more recently some researchers have adopted the term autonomy-support.
+Within their "OPTIMAL" theory of motor learning, @wulf2016 argued that providing learners with opportunities for choice creates an autonomy-supportive practice environment, which facilitates motor performance and learning.
+Specifically, the authors predict that autonomy-support facilitates performance by enhancing expectancies (Prediction 3, p.
+1404), that enhanced expectancies and autonomy support contribute to efficient goal-action coupling by readying the motor system for task execution (Prediction 2, p.
+1404), and that enhanced expectancies and autonomy support facilitate motor learning by making dopamine available for memory consolidation and neural pathway development (Prediction 7, p.
+1404).
+In other words, these psychological benefits of increased perceptions of autonomy and competence, and the resulting increases in performance and learning are a by-product of having choice itself.
+Overall, Wulf and Lewthwaite's [-@wulf2016] "OPTIMAL" theory of motor learning provides a motivational explanation for the learning advantages of self-controlled practice conditions over yoked practice conditions.[^1]
 
-Despite its prominent role within the "OPTIMAL" theory of motor learning, there are numerous reasons to doubt the importance of autonomy-support through the provision of choice during practice.
-First, if the benefits are the result of having opportunities for choice then learning differences should not emerge between different self-controlled groups.
-However, in experiments where different groups of participants have choice over their feedback schedule, such learning differences have been found, but not limited to, when this choice is made *after* rather than before a performance attempt [@chiviacowsky2005; @carter2014], when different criteria for success are provided to participants [@chiviacowsky2012], and when the absolute number of feedback choice opportunities are limited compared to unlimited at the outset of practice [@hansen2011; @patterson2011].
-Second, there has been little-to-no support for the notion that practicing in a self-controlled group is perceived as more autonomy-supportive than being in a yoked group.
-@ste-marie2013, for example, had participants in the self-controlled and yoked groups complete the perceived choice subscale of the Intrinsic Motivation Inventory and failed to find the expected effect of higher self-reported scores during practice in the self-controlled group.
-Similar findings have been reported by others [@barros2019; @carter2017a; @mckay2020b].
-However, @mckay2020a recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group.
-This increased perceived autonomy-support did not, however, translate into enhanced learning compared to the yoked group.
-Although the available literature does not provide substantial evidence that self-controlled practice is autonomy-supportive, this does not necessarily mean such a manipulation is not autonomy-supportive [@altman1995].
-For instance, this effect may in fact be quite small and require much larger sample sizes to detect than those commonly used in motor learning experiments [@lohse2016].
+[^1]: It should be noted that other researchers have instead presented an information-processing explanation for the self-controlled learning advantages [see @ste-marie2019 for a recent discussion of the motivational and information-processing explanations].
+We acknowledge this view here; however, unlike previous experiments [e.g., @barros2019; @carter2014; @carter2017a; @carter2017b; @couvillion2020; @woodard2020] the current experiment was not designed to test between explanations.
+We focused on the motivational explanation as this view has garnered more attention due the "OPTIMAL" theory of motor learning.
+
+Despite its prominent role as a robust and generalizable learning variable in the "OPTIMAL" theory (p.
+1393), there is considerable ambiguity surrounding whether the provision of choice is in fact an autonomy-supportive manipulation.
+First, the notion that practicing in a self-controlled group is actually more autonomy-supportive than a yoked group has primarily been assumed [e.g., @abdollahipour2017; @chua2018; @lewthwaite2015; @wulf2018] rather than supported empirically.
+Second, when researchers have included measures related to perceptions of autonomy the data is mixed.
+For example, @ste-marie2013 did not find the expected effect of higher perceptions of autonomy during practice in a self-controlled group as compared to a yoked group.
+Similar outcomes have been reported by others [e.g., @barros2019; @carter2017a; @mckay2020b].
+In contrast, @mckay2020a recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group.
+However, despite their higher perceived autonomy scores the self-controlled group did not have significantly better motor performance and learning as predicted in the "OPTIMAL" theory.
+Although the majority of experiments that included a measure related to perceived autonomy reported no group differences, the *absence of evidence is not evidence of absence* [@altman1995].
+Thus, self-controlled practice conditions could be an autonomy-supportive manipulation but such an effect may actually be quite small and require much larger sample sizes to detect than those used in previous experiments [e.g., @barros2019; @ste-marie2013] and in motor learning experiments in general [see @lohse2016 for a discussion].
+This argument of underpowered experimental designs is supported by the results of @mckay2020a as these authors had one of the largest sample sizes to date in the self-controlled literature.
 
 There are at least two other methodological issues that warrant consideration.
-The first of these is that in self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component (e.g., feedback or when to watch a modeled demonstration) of their practice and participants in the yoked group are not given choice over this component.
-However, within the context of practice itself there are many other opportunities for choice that participants may explore, independent of their assigned group.
-Target-based tasks such as basketball free throws [e.g., @aiken2012] or bean-bag tossing [@grand2015] are a popular choice in motor learning experiments and have been used in self-controlled learning experiments.
-While a participant in the yoked group may not be permitted choice over their feedback schedule (or some other practice variable) in these experiments, this does not preclude them from opportunities for choice---and thus autonomy-support---when deciding to try different throwing techniques, speeds, and/or release points.
+In self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component (e.g., feedback or when to watch a modeled demonstration) of their practice and participants in the yoked group are not given choice over this component.
+However, within the context of practice itself there are other opportunities for choice that participants may explore, independent of their assigned group.
+Past self-controlled learning experiments have used a variety of motor tasks, including but not limited to basketball free throws [e.g., @aiken2012] and bean-bag tossing [e.g., @grand2015].
+Although participants in a yoked group may not have choice over their feedback schedule (or some other practice variable) while learning such tasks, this does not preclude them from opportunities for choice---and thus autonomy-support---when choosing to try different throwing techniques, speeds, and/or release points.
 Thus, labeling yoked groups as being devoid of choice opportunities may be a misnomer.
-The other consideration relates to the instructions that are provided to participants in the yoked group.
-In the context of feedback[^1], these participants are typically informed that during practice they may or may not receive feedback after a given trial [e.g., @chiviacowsky2002; @patterson2010].
-This means that participants in yoked groups are not even aware that they have been denied an opportunity for choice, nor that their feedback schedule was created by another participant who was given choice over when feedback was or was not provided.
-Either of these in isolation, or both simultaneously could contribute to the consistent finding that participants in self-controlled and yoked groups report similar perceived autonomy scores when asked about their opportunities for choices with respect to the motor task [@ste-marie2013] or about their practice environment in general [@barros2019; @carter2017a; @mckay2020b].
+The other issue relates to the instructions that are provided to participants in a yoked group.
+In the context of feedback[^2], these participants are typically informed that during practice they may or may not receive feedback after a given trial [e.g., @chiviacowsky2002; @patterson2010].
+This means that participants in yoked groups are not even aware that they have been denied an opportunity for choice, or that their feedback schedule was created by another participant who had choice over when feedback was or was not provided.
+These two methodological issues, either in isolation or simultaneously, may have contributed to the consistent finding in past research with self-controlled and yoked participants self-reporting numerically similar perceptions of autonomy when asked about opportunities for choice with respect to the motor task [e.g., @ste-marie2013] or about their practice environment in general [e.g., @barros2019; @carter2017a; @mckay2020b].
 
-[^1]: While feedback is used in this example, this issue surrounding instructions is also relevant to other practice variables commonly used in self-controlled learning experiments.
+[^2]: While feedback is used in this example, this issue surrounding instructions is also relevant to other practice variables commonly used in self-controlled learning experiments.
 
-```{r table1, echo = FALSE, results = "asis"}
-
-table_1 <- data.frame(c(
-  "Self-Controlled",
-  "", "",
-  "Traditional Yoked",
-  "", "",
-  "Explicit Yoked", 
-  "", ""),
-  c(
-    "Before each trial, you will be asked whether you wish to watch a modeled demonstration of the task.",
-    "If you choose YES, you will then be asked whether you want to watch the video in real-time or in",
-    "slow-motion.",
-
-    "Before each trial, you may or may not watch a modeled demonstration of the task based on a pre-",
-    "determined schedule. If you observe a model, it might be presented in real-time or in slow-motion",
-    "based on the pre-determined schedule.",
-
-    "Before each trial, you may or may not watch a modeled demonstration of the task based on the", 
-    "schedule another participant selected. If you observe a model, it might be presented in real-time or in",
-    "slow-motion based on what that participant selected."
-  )
-)
-
-apa_table(table_1, font_size = "scriptsize", col.names = c(" ", "Acquisition instructions"), booktabs = TRUE, span_text_columns = TRUE, caption = "Group specific instructions detailing the observation schedule that would be experienced during Acquisition.")
-
-```
-
-Here we investigated the effects of making participants in a yoked group explicitly aware of not only being denied opportunities for choice over their frequency of watching and the playback speed of video demonstrations, but also that the schedule they would experience during practice was created by another participant in the experiment.
-The addition of this novel yoked group allowed us to address one of the previously identified methodological limitations regarding experimental group instructions in past self-controlled research.
-We compared the performance of this explicit yoked group with traditional self-controlled and yoked groups on a speed cup-stacking task in practice and in a delayed retention test.
+Here, we addressed the methodological limitation of past self-controlled research where participants in the yoked group are unaware that a feature of their practice environment was created by another participant in the experiment.
+To this end, participants learned a speed cup-stacking task in either a self-controlled group, a traditional yoked group, or a novel explicitly aware yoked group.
+The self-controlled group has choice over the frequency of watching a video demonstration and the video playback speed (real-time or slow motion).
+Participants in the traditional and explicit yoked groups were matched to a participant in the self-controlled group and experienced the observation schedule selected by this participant.
+The key difference being that participants in the explicit yoked group were told that the observation schedule they would experience during practice was selected by another participant, whereas participants in the traditional yoked group were not aware of this.
+Motor learning was assessed using a delayed retention test.
+We predicted that the self-controlled group would have significantly faster stacking times in retention than the traditional yoked group.
+In other words, we expected to replicate the typical self-controlled learning advantage.
+If the self-controlled learning advantage results from choice being autonomy-supportive as argued in the "OPTIMAL" theory [@wulf2016], then participants in the self-controlled group should also self-report significantly higher scores for perceptions of autonomy.
+Also based on the view that autonomy-support is the mechanism underlying the typical self-controlled learning advantage [@wulf2016], we predicted that the explicit yoked group should have significantly slower stacking times in retention.
+Although we found significantly higher perceptions of autonomy in the self-controlled group, there were no significant group differences in stacking times during retention.
+Overall, these results do not support our predictions and are inconsistent with predictions 2, 3, and 7 in the "OPTIMAL" theory of motor learning [@wulf2016].
 
@@
 
-One-hundred and fifty participants completed the experiment.
-Sample size was determined by an a priori power calculation based on our smallest comparison of interest.
-An early estimate for the effect of self-controlled over yoked practice was a Hedges' $g = 0.63$ [@mckay2014] and while planning this experiment this effect was estimated to be $g = 0.52$ (Z.
+One-hundred and fifty university students participated in the experiment.
+Sample size was determined by an a priori power calculation based on our smallest comparison of interest using GLIMMPSE (https://glimmpse.samplesizeshop.org/).
+An early estimate for the effect of self-controlled over yoked practice was a Hedges' *g* = 0.63 [@mckay2014] and while planning this experiment this effect was estimated to be *g* = 0.52 (Z.
 Yantha, personal communication, October 2019).
-Based on this effect, a positive correlation of $r = 0.6$ between retention and pre-test as the covariate, and 80% power to detect a difference between the self-controlled and traditional yoked groups, the required number of participants was 31 per group.
-Considering the novelty of our Explicit Yoked group, we assumed a smaller effect, $g = 0.4$, between it and the Traditional Yoked group.
-With the same parameters as above, this resulted in our final sample of 50 participants per group.
+Based on this effect, a positive correlation of *r* = 0.6 between retention and pre-test as the covariate, an alpha of 0.05, and 80% power to detect a difference between the self-controlled and traditional yoked groups, the required number of participants was 31 per group.
+Considering the novelty of our Explicit Yoked group, we assumed a smaller effect, *g* = 0.4, between it and the Traditional Yoked group.
+Using this effect and the same parameters as above, this resulted in our final sample of 50 participants per group.
 
-Participants completed the experiment in either the Self-Controlled group $(M_{age} = 18.0$, *SD* = 0.34), the Traditional Yoked group $(M_{age} = 19.5$, *SD* = 1.89), or the Explicit Yoked group $(M_{age} = 19.2$, *SD* = 1.55).
+Participants completed the experiment in either the Self-Controlled group $(M_{age}$ = 18.0, *SD* = 0.34; 32 females), the Traditional Yoked group $(M_{age}$ = 19.5, *SD* = 1.89; 28 females), or the Explicit Yoked group $(M_{age}$ = 19.2, *SD* = 1.55; 30 females).
 We collected the Self-Controlled group first as their self-selected observation schedule was required for the yoking procedure for the two other groups.
@@
 All participants provided written informed consent approved by and conducted in accordance with the University's Research Ethics Board.
-Participants received either \$15 or a course bonus for their participation.
+Participants received either $15 or a course bonus for their participation.
 
@@
 Session 2 consisted of a delayed retention test.
-At the start of each phase of the experiment, all participants received phase-specific instructions (see Data and code availability section).
+At the start of each phase of the experiment, all participants received phase-specific instructions \hyperref[sec:sharing]{(see Data, materials, and code availability section).
 Group specific instructions were provided prior to the acquisition phase (see Table \@ref(tab:table1)).
@@
 Participants followed along as the instructions were read aloud by the researcher.
+\medskip
+
+```{r table1, echo = FALSE, results = "asis"}
+
+table_1 <- tibble(
+    Group = c("Self-Controlled",
+              "Traditional Yoked",
+              "Explicit Yoked"),
+    Instructions = c("Before each trial, you will be asked whether you wish to watch a modeled demonstration of the task.
+If you choose YES, you will then be asked whether you want to watch the video in real-time or in slow-motion.",
+                     "Before each trial, you may or may not watch a modeled demonstration of the task based on a pre-determined schedule.
+If you observe a model, it might be presented in real-time or in slow-motion based on the pre-determined schedule.",
+                     "Before each trial, you may or may not watch a modeled demonstration of the task based on the schedule another participant selected.
+If you observe a model, it might be presented in real-time or in slow-motion based on what that participant selected.")
+)
+
+kbl(table_1,
+    booktabs = TRUE,
+    escape = TRUE,
+    linesep = "\\addlinespace",
+    caption = "Group specific components from the instructions detailing the observation schedule that would be experienced during Acquisition.",
+    col.names = c(" ",
+                  "Acquisition instructions")
+    ) %>% 
+  #landscape() %>% 
+  kable_styling(position = "left",
+                font_size = 10) %>% 
+  column_spec(1, width = "8em") %>% 
+  column_spec(2, width = "33em")
+```
 
@@
 Participants answered these questions after the pre-test, after trials five and 25 of acquisition, and before the delayed retention test.
+The values for Cronbach's alpha for each questionnaire at each time point are reported in Table \@ref(tab:table2).
 
 A custom LabVIEW (National Instruments Inc.) program was created that controlled the presentation of all instructions, the video demonstrations, the timing of the experimental protocol, and recorded and stored the data for later analysis.
+
+```{r table2, echo = FALSE, results = "asis"}
+
+table_2 <- tibble(
+    c1 = c("Perceived autonomy",
+           "Perceived competence",
+           "Intrinsic motivation"),
+    c2 = c("0.62",
+           "0.90",
+           "0.86"),
+    c3 = c("0.79",
+           "0.92",
+           "0.90"),
+    c4 = c("0.79",
+           "0.94",
+           "0.92"),
+    c5 = c("0.84",
+           "0.92",
+           "0.92"),
+)
+
+kbl(table_2,
+    booktabs = TRUE,
+    escape = TRUE,
+    linesep = "\\addlinespace",
+    caption = "Cronbach's alpha for each questionnaire at each time point.",
+    col.names = c(" ",
+                  "After pre-test",
+                  "After trial 5",
+                  "After trial 25",
+                  "Before retention")
+    ) %>% 
+    kable_styling(position = "left",
+                  font_size = 10) %>% 
+    column_spec(1, width = "10em") %>% 
+    column_spec(2, width = "6em") %>% 
+    column_spec(3, width = "6em") %>% 
+    column_spec(4, width = "6em") %>% 
+    column_spec(5, width = "7em")
+
+```
 
@@
 Our primary outcome measure was stacking time (i.e., response time) in seconds.
-Trials recorded as errors $(76/5250 = 1.45\%)$ during data collection were manually removed prior to data analysis.
+Trials recorded as errors (76/5250 = 1.45%) during data collection were manually removed prior to data analysis.
 For each participant, pre-test and delayed retention trials were aggregated into one block of five trials and acquisition was aggregated into five blocks of five trials.
@@
 Post hoc comparisons were conducted using Holm's correction.
-A Cook's distance of $\geq 1$ was used to identify any influential cases.
+A Cook's distance of $\geq$ 1 was used to identify any influential cases and none were identified.
+Statistical tests are described below.
 
@@
 
-To test whether delayed retention (Figure \@ref(fig:fig1)C) was differentially impacted by the experimental group (i.e., Self-Controlled, Traditional Yoked, Explicit Yoked) experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test.
+To test whether delayed retention (Figure \@ref(fig:fig1)C) was differentially impacted by the experimental group experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test.
 As can be seen, the Self-Controlled group $(M = 9.99$, $95\%CI = [9.68,10.31])$, the Traditional Yoked group $(M = 10.18$, $95\%CI = [9.86,10.50])$, and the Explicit Yoked group $(M = 10.12$, $95\%CI = [9.81,10.44])$ all had similar stacking times in retention (means are shown as the adjusted means controlling for pre-test).
 The effect of Group was not significant, $F(2,146) = .335$, $p = .716$, $\eta^2 = .002$.
-
-(ref:fig1-caption) Physical performance data of the experiment.
-The Self-Controlled group is shown in red with solid lines and/or circles, the Traditional Yoked group is shown in blue with dotted and/or triangles, and the Explicit Yoked group is shown in orange with dashed and/or squares.
-**A**.
-Trial-by-trial stacking time (s) data averaged across participants within each group (shaded area represents standard error).
-Splits between line segments denote the end of one phase and the start of the next.
-Pre-test (Trials 1 to 5) and Acquisition (Trials 6 to 30) occurred on Day 1 and Retention (Trials 31 to 35) occurred on Day 2, approximately 24-hours later.
-**B**.
-Mean stacking time (s) for each group was computed by averaging the data from **A** into 7 blocks of trials.
-Error bars represent 95% confidence intervals.
-Splits between line segments denote the end of one phase and the start of the next.
-**C**.
-Mean stacking time (s) adjusted for pre-test for each group.
-Error bars represent 95% confidence intervals.
-**D**.
-Scatterplot showing the relationship between each participant's mean stacking time (s) in pre-test and retention.
-
-```{r fig1, echo = FALSE, fig.cap = "(ref:fig1-caption)", fig.align = "center", out.height = "55%"}
-knitr::include_graphics("../../figs/fig1.pdf")
-```
 
@@
 
+(ref:fig1-caption) **Physical performance data of the experiment.** The Self-Controlled group is shown in red with solid lines and/or circles, the Traditional Yoked group is shown in blue with dotted and/or triangles, and the Explicit Yoked group is shown in orange with dashed and/or squares.
+**(A).** Trial-by-trial stacking time (s) data averaged across participants within each group (shaded area represents standard error).
+Splits between line segments denote the end of one phase and the start of the next.
+Pre-test (Trials 1 to 5) and Acquisition (Trials 6 to 30) occurred on Day 1 and Retention (Trials 31 to 35) occurred on Day 2, approximately 24-hours later.
+**(B).** Mean stacking time (s) for each group was computed by averaging the data from A into 7 blocks of trials.
+Error bars represent 95% confidence intervals.
+Splits between line segments denote the end of one phase and the start of the next.
+**(C).** Mean stacking time (s) adjusted for pre-test for each group.
+Error bars represent 95% confidence intervals.
+**(D).** Scatterplot showing the relationship between each participant's mean stacking time (s) in pre-test and retention.
+
+```{r fig1, echo = FALSE, fig.cap = "(ref:fig1-caption)", fig.align = "center", out.height = "51%"}
+knitr::include_graphics("../../figs/fig1.pdf")
+```
+
+\newpage
+
+```{r table3, echo = FALSE, results = "asis"}
+
+table_3 <- tibble(
+    Observation = c("Model viewing frequency",
+                    "Regular speed frequency"),
+    b1 = c("32.6%",
+           "33.8%"),
+    b2 = c("16.9%",
+           "38.1%"),
+    b3 = c("12.0%%",
+           "50.0%"),
+    b4 = c("12.9%",
+           "34.4%"),
+    b5 = c("9.3%",
+           "30.4%"),
+)
+
+kbl(table_3,
+    booktabs = TRUE,
+    escape = TRUE,
+    linesep = "\\addlinespace",
+    caption = "The mean frequencies for each Acquisition block of requesting to watch the video demonstration and of those requests, the mean frequency of choosing the regular viewing speed.",
+    col.names = c(" ",
+                  "Block 1",
+                  "Block 2",
+                  "Block 3",
+                  "Block 4",
+                  "Block 5")
+    ) %>% 
+    kable_styling(position = "left",
+                  font_size = 10) %>% 
+    column_spec(1, width = "13em") %>% 
+    column_spec(2, width = "5em") %>% 
+    column_spec(3, width = "5em") %>% 
+    column_spec(4, width = "5em") %>% 
+    column_spec(5, width = "5em")
+
+```
+
 ### Acquisition phase
 
-Model frequency and the video speed request data are reported in Table \@ref(tab:table2).
+Model frequency and the video speed request data are reported in Table \@ref(tab:table3).
 The mean frequency of viewing the video demonstration during acquisition was $16.7\%$.
@@
 A 3 Group x 3 Time ANCOVA controlling for pre-test revealed non-significant effects for Group, $F(2,146) = 2.08$, $p = .129$, $\eta^2_{G} = .024$, Time, $F(1.68,245.73) = .563$, $p = .541$, $\eta^2_{G} = .001$, and the Group x Time interaction, $F(3.37,245.73) = .333$, $p = .824$, $\eta^2_{G} = .001$.
+
+(ref:fig2-caption) **Questionnaire data.** Groups means for perceived autonomy **(A)**, intrinsic motivation **(B)**, and perceived competence **(C)** after pre-test, trial 5, and trial 25 on Day 1, and before retention on Day 2.
+The Self-Controlled group is shown in red circles, the Traditional Yoked group is shown in blue triangles, and the Explicit Yoked group is shown in orange squares.
+Dots represent individual participants in each group.
+Scores could range from 1 (Strongly disagree) to 7 (Strongly agree).
+Error bars represent 95% confidence intervals.
+
+```{r fig2, echo = FALSE, fig.cap = "(ref:fig2-caption)", fig.align = "center", out.height = "72%"}
+knitr::include_graphics("../../figs/fig2.pdf")
+
+```
 
@@
 
-(ref:fig2-caption) Questionnaire data.
-Groups means for **A** perceived autonomy, **B** intrinsic motivation, and **C** perceived competence after pre-test, trial 5, and trial 25 on Day 1, and before retention on Day 2.
-The Self-Controlled group is shown in red circles, the Traditional Yoked group is shown in blue triangles, and the Explicit Yoked group is shown in orange squares.
-Dots represent individual participants in each group.
-Scores could range from 1 (Strongly disagree) to 7 (Strongly agree).
-Error bars represent 95% confidence intervals.
-
-```{r fig2, echo = FALSE, fig.cap = "(ref:fig2-caption)", fig.align = "center", out.height = "75%"}
-knitr::include_graphics("../../figs/fig2.pdf")
-
-```
-
 ### Equivalence tests
 
-To further probe our null effects [@harms2018] related to our main predictions, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure [@lakens2018; @schuirmann1987].
+Given our pre-registered analysis resulted in a non-significant finding, we performed two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times using the two one-sided test procedure [@lakens2018; @schuirmann1987].
+Equivalence tests are a statistical tool that researchers can use to support the absence of a meaningful effect and avoid incorrectly concluded no effect exists based on a non-significant finding [@harms2018].
 To establish our smallest effect size of interest [@lakens2021] we calculated the effect size our design had 33% power to detect [@simonsohn2015], which was $d_{s} = .31$.
@@
 It is worth noting that in some situations autonomy-support in and of itself might be a desired affective outcome [@ste-marie2020].
-In such circumstance, providing learners with choice opportunities may be a useful motivationally-protective outcome.
+In such circumstances, providing learners with choice opportunities may be a useful motivationally-protective outcome.
 However, such a tool should be used judiciously as it is typically motor outcomes in the form of relatively permanent performance changes that is the true goal of any motor learning intervention [@ste-marie2020].
-Ultimately, our results add to a growing body of evidence that questions whether autonomy-supportive manipulations directly affect learning.
+Ultimately, our results add to a growing body of evidence that questions whether autonomy-supportive manipulations directly affect motor learning.
 One explanation for this lack of replicability is that the *"true"* effect of such manipulations are much smaller than previously estimated [@mckay2021].
-Given the resources required (in terms of sample size) to reliably detect the tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either studying practice conditions that have much bigger effects or devising ways to reduce variability and increase power through clever experimental design [@mcclelland2000].
+Given the resources required (in terms of sample size) to reliably detect these tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either by adopting the use of sequential analyses [@lakens2021; @lakens2014; @wald1945] and/or multi-lab collaborations [@boland2017] or studying practice conditions that likely have much bigger effects on motor learning.
 
-\newpage
+\vfill
+
+# Contributions using CrediT (https://casrai.org/credit/)
+Conceptualization (LSG, KRL, MJC); Data curation (LSG, KRL, MJC); Formal analysis (LSG, KRL, MJC); Funding acquisition (MJC); Investigation - Performed Experiment (LSG, AW, NB, AP, OL); Methodology (LSG, KRL, MJC); Project administration (LSG, MJC); Resources (MJC); Software - Task Programming (LSG, MJC); Supervision (MJC); Validation (LSG, KRL, MJC); Visualization (LSG, MJC); Writing - Original Draft Preparation (LSG, AW, NB, KRL, MJC); Writing - Review & Editing (LSG, AW, NB, AP, OL, KRL, MJC)
+
+# Data, materials, and code availability
+\label{sec:sharing}
+All material, data, and scripts to reproduce our analyses and figures can be accessed here: https://github.com/cartermaclab/expt_explicit-yoked.
+The preregistration can be accessed here: https://aspredicted.org/ze8cj.pdf.
+
+# R packages used in this project
+`r cite_r("../r-references.bib")`.
 
@@
 # Funding
-This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC). LSG was also supported by an NSERC PGS-D scholarship.
-
-# Data and code availability
-All material, data, and scripts to reproduce our analyses and figures can be accessed here: https://github.com/cartermaclab/expt_explicit-yoked.
-
-# R packages used in this project
-`r cite_r("../r-references.bib")`.
+This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC).
+LSG was supported by an NSERC Postgraduate Scholarship.
+AW and AP were supported by NSERC Undergraduate Student Research Awards.
 

### 2021-12-28 docs/preprint/preprint.tex
update: accepted version

@@
   english,
-  jou]{apa7}
+  doc, donotrepeattitle,floatsintext]{apa7}
+\title{Increased perceptions of autonomy through choice over one's observation schedule fail to enhance motor skill retention}
+\author{Laura St.~Germain\textsuperscript{1}, Allison Williams\textsuperscript{1}, Noura Balbaa\textsuperscript{1}, Andrew Poskus\textsuperscript{1}, Olena Leshchyshen\textsuperscript{1}, Keith R.
+Lohse\textsuperscript{2}, \& Michael J.
+Carter\textsuperscript{1}}
+\date{}
+
 \usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \hypersetup{
-  pdftitle={Increased perceptions of autonomy through choice fail to enhance motor skill retention},
+  pdftitle={Increased perceptions of autonomy through choice over one's observation schedule fail to enhance motor skill retention},
   pdfauthor={Laura St.~Germain1, Allison Williams1, Noura Balbaa1, Andrew Poskus1, Olena Leshchyshen1, Keith R. Lohse2, \& Michael J. Carter1},
   pdflang={en-EN},
-  pdfkeywords={Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing},
+  pdfkeywords={Motor learning; Pre-registered; Self-controlled; Observation},
   hidelinks,
@@
 \makeatother
-\shorttitle{Autonomy-support does not benefit motor learning}
-\keywords{Motor learning; Pre-registered; Self-controlled; Observation; Equivalence testing}
-\usepackage{dblfloatfix}
 
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
+\keywords{Motor learning; Pre-registered; Self-controlled; Observation}
 \usepackage{csquotes}
+\usepackage{pdflscape}
 \raggedbottom
-\leftheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
-\rightheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
-\ifxetex
+\ifXeTeX
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 
-\addORCIDlink{Laura St. Germain}{0000-0002-5513-4183}; \addORCIDlink{Keith R. Lohse}{0000-0002-7643-3887}; \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
+\addORCIDlink{Laura St. Germain}{0000-0002-5513-4183}
 
-We have outlined author contributions using CRediT (Contributor Roles Taxonomy - \url{https://casrai.org/credit/}).
+\addORCIDlink{Keith R. Lohse}{0000-0002-7643-3887}
 
-The authors made the following contributions.
-Laura St.~Germain: Conceptualization, Data curation, Formal analysis, Investigation - Performed the experiment, Methodology, Project administration, Software - Task Programming, Validation, Visualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Allison Williams: Investigation - Performed the experiment, Writing - Original Draft Preparation, Writing - Review \& Editing; Noura Balbaa: Investigation - Performed the experiment, Writing - Original Draft Preparation, Writing - Review \& Editing; Andrew Poskus: Investigation - Performed the experiment, Writing - Review \& Editing; Olena Leshchyshen: Investigation - Performed the experiment, Writing - Review \& Editing; Keith R.
-Lohse: Conceptualization, Data curation, Formal analysis, Methodology, Validation, Writing - Original Draft Preparation, Writing - Review \& Editing; Michael J.
-Carter: Conceptualization, Data curation, Formal analysis, Funding acquisition, Methodology, Project administration, Resources, Software - Task Programming, Supervision, Validation, Visualization, Writing - Original Draft Preparation, Writing - Review \& Editing.
+\addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
+
+Preregistration: \url{https://aspredicted.org/ze8cj.pdf}
+
+Data, code, and materials: \url{https://github.com/cartermaclab/expt_explicit-yoked}
+
+PsyArXiv preprint: \url{https://doi.org/10.31234/osf.io/s34fg} \vspace{1em}
 
@@
 
-A popular recommendation in recent years for creating an effective environment for motor skill learning has been to allow the learner to take control over an element of their practice that is traditionally controlled by a coach, therapist, or teacher (Sanli et al., 2013; Ste-Marie et al., 2019).
+\vspace{-0.5em}
+
+\noindent
+
+\begin{center}
+\textcolor{blue}{Accepted for publication in \emph{Journal of Experimental Psychology: Human Perception \& Performance}}
+\end{center}
+
+\vspace{0.5em}
+
+A popular recommendation in recent years for creating an effective environment for motor skill learning has been to allow the learner to take control over an element of their practice that is traditionally controlled by a coach, therapist, or teacher (Sanli, Patterson, Bray, \& Lee, 2013; Ste-Marie, Carter, \& Yantha, 2019).
 This recommendation is based on the consistent finding that participants in a self-controlled (i.e., choice) group perform with higher proficiency compared to participants in a yoked (i.e., control) group on delayed retention and/or transfer tests.
@@
 Instead, they are linked to a self-controlled participant and experience this participant's self-selected practice schedule.
-This so-called self-controlled learning advantage has been shown when participants are given the opportunity to schedule task difficulty (e.g., Andrieux et al., 2012; Leiker et al., 2016), the order that multiple tasks are practiced (e.g., Wu \& Magill, 2011), the frequency of watching a modeled demonstration (e.g.
-Wulf et al., 2005), and when to receive augmented feedback (e.g., Janelle et al., 1997; Patterson \& Carter, 2010).
+This so-called self-controlled learning advantage has been shown when participants are given the opportunity to schedule task difficulty (e.g., Andrieux, Danna, \& Thon, 2012; Leiker et al., 2016), the order that multiple tasks are practiced (e.g., Wu \& Magill, 2011), the frequency of watching a modeled demonstration (e.g.
+Wulf, Raupach, \& Pfeiffer, 2005), and when to receive augmented feedback (e.g., Janelle, Barba, Frehlich, Tennant, \& Cauraugh, 1997; Patterson \& Carter, 2010).
 
-Over the years, this manipulation has been described using a variety of names (e.g., self- and/or learner-controlled; -regulated; -directed; -selected), but more recently it has been subsumed by autonomy-support.
-In fact, autonomy-support is considered such a robust learning variable that it is one of three key pillars in the recently proposed ``OPTIMAL'' theory of motor learning (Wulf \& Lewthwaite, 2016).
-Wulf and Lewthwaite (2016) argued that providing learners with opportunities for choice---considered an autonomy-supportive practice manipulation---can facilitate motor performance and learning by enhancing learner's expectancies for success, and by allowing the learner to maintain their attentional focus on the task by reducing the need for self-regulatory activity (Abdollahipour et al., 2017; Chua et al., 2018; Wulf et al., 2018).
-In other words, these psychological and attentional benefits, and concomitant increases in performance and learning are a by-product of exercising choice during practice.
-Overall, autonomy-support is seen as a means to efficient goal-action coupling (Wulf \& Lewthwaite, 2016) and also links the ``OPTIMAL'' theory with Self-Determination theory (Deci \& Ryan, 2000).
+Over the years, this manipulation has been described using a variety of names (e.g., self- and/or learner-controlled; -regulated; -directed; -selected), but more recently some researchers have adopted the term autonomy-support.
+Within their ``OPTIMAL'' theory of motor learning, Wulf and Lewthwaite (2016) argued that providing learners with opportunities for choice creates an autonomy-supportive practice environment, which facilitates motor performance and learning.
+Specifically, the authors predict that autonomy-support facilitates performance by enhancing expectancies (Prediction 3, p.~1404), that enhanced expectancies and autonomy support contribute to efficient goal-action coupling by readying the motor system for task execution (Prediction 2, p.~1404), and that enhanced expectancies and autonomy support facilitate motor learning by making dopamine available for memory consolidation and neural pathway development (Prediction 7, p.~1404).
+In other words, these psychological benefits of increased perceptions of autonomy and competence, and the resulting increases in performance and learning are a by-product of having choice itself.
+Overall, Wulf and Lewthwaite's (2016) ``OPTIMAL'' theory of motor learning provides a motivational explanation for the learning advantages of self-controlled practice conditions over yoked practice conditions.\footnote{It should be noted that other researchers have instead presented an information-processing explanation for the self-controlled learning advantages (see Ste-Marie et al., 2019 for a recent discussion of the motivational and information-processing explanations).
+We acknowledge this view here; however, unlike previous experiments (e.g., Barros, Yantha, Carter, Hussien, \& Ste-Marie, 2019; Carter, Carlsen, \& Ste-Marie, 2014; Carter \& Ste-Marie, 2017b, 2017a; Couvillion, Bass, \& Fairbrother, 2020; Woodard \& Fairbrother, 2020) the current experiment was not designed to test between explanations.
+We focused on the motivational explanation as this view has garnered more attention due the ``OPTIMAL'' theory of motor learning.}
 
-Despite its prominent role within the ``OPTIMAL'' theory of motor learning, there are numerous reasons to doubt the importance of autonomy-support through the provision of choice during practice.
-First, if the benefits are the result of having opportunities for choice then learning differences should not emerge between different self-controlled groups.
-However, in experiments where different groups of participants have choice over their feedback schedule, such learning differences have been found, but not limited to, when this choice is made \emph{after} rather than before a performance attempt (Carter et al., 2014; Chiviacowsky \& Wulf, 2005), when different criteria for success are provided to participants (Chiviacowsky et al., 2012), and when the absolute number of feedback choice opportunities are limited compared to unlimited at the outset of practice (Hansen et al., 2011; Patterson et al., 2011).
-Second, there has been little-to-no support for the notion that practicing in a self-controlled group is perceived as more autonomy-supportive than being in a yoked group.
-Ste-Marie et al.
-(2013), for example, had participants in the self-controlled and yoked groups complete the perceived choice subscale of the Intrinsic Motivation Inventory and failed to find the expected effect of higher self-reported scores during practice in the self-controlled group.
-Similar findings have been reported by others (Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020b).
-However, McKay and Ste-Marie (2020a) recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group.
-This increased perceived autonomy-support did not, however, translate into enhanced learning compared to the yoked group.
-Although the available literature does not provide substantial evidence that self-controlled practice is autonomy-supportive, this does not necessarily mean such a manipulation is not autonomy-supportive (Altman \& Bland, 1995).
-For instance, this effect may in fact be quite small and require much larger sample sizes to detect than those commonly used in motor learning experiments (Lohse et al., 2016).
+Despite its prominent role as a robust and generalizable learning variable in the ``OPTIMAL'' theory (p.~1393), there is considerable ambiguity surrounding whether the provision of choice is in fact an autonomy-supportive manipulation.
+First, the notion that practicing in a self-controlled group is actually more autonomy-supportive than a yoked group has primarily been assumed (e.g., Abdollahipour, Palomo Nieto, Psotta, \& Wulf, 2017; Chua, Wulf, \& Lewthwaite, 2018; Lewthwaite, Chiviacowsky, Drews, \& Wulf, 2015; Wulf, Lewthwaite, Cardozo, \& Chiviacowsky, 2018) rather than supported empirically.
+Second, when researchers have included measures related to perceptions of autonomy the data is mixed.
+For example, Ste-Marie, Vertes, Law, and Rymal (2013) did not find the expected effect of higher perceptions of autonomy during practice in a self-controlled group as compared to a yoked group.
+Similar outcomes have been reported by others (e.g., Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020a).
+In contrast, McKay and Ste-Marie (2020b) recently found that practicing in a self-controlled group was perceived as more autonomy-supportive than practicing the same task in a yoked group.
+However, despite their higher perceived autonomy scores the self-controlled group did not have significantly better motor performance and learning as predicted in the ``OPTIMAL'' theory.
+Although the majority of experiments that included a measure related to perceived autonomy reported no group differences, the \emph{absence of evidence is not evidence of absence} (Altman \& Bland, 1995).
+Thus, self-controlled practice conditions could be an autonomy-supportive manipulation but such an effect may actually be quite small and require much larger sample sizes to detect than those used in previous experiments (e.g., Barros et al., 2019; Ste-Marie et al., 2013) and in motor learning experiments in general (see Lohse, Buchanan, \& Miller, 2016 for a discussion).
+This argument of underpowered experimental designs is supported by the results of McKay and Ste-Marie (2020b) as these authors had one of the largest sample sizes to date in the self-controlled literature.
 
 There are at least two other methodological issues that warrant consideration.
-The first of these is that in self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component (e.g., feedback or when to watch a modeled demonstration) of their practice and participants in the yoked group are not given choice over this component.
-However, within the context of practice itself there are many other opportunities for choice that participants may explore, independent of their assigned group.
-Target-based tasks such as basketball free throws (e.g., Aiken et al., 2012) or bean-bag tossing (Grand et al., 2015) are a popular choice in motor learning experiments and have been used in self-controlled learning experiments.
-While a participant in the yoked group may not be permitted choice over their feedback schedule (or some other practice variable) in these experiments, this does not preclude them from opportunities for choice---and thus autonomy-support---when deciding to try different throwing techniques, speeds, and/or release points.
+In self-controlled motor learning experiments participants in the self-controlled group are usually given choice over a single component (e.g., feedback or when to watch a modeled demonstration) of their practice and participants in the yoked group are not given choice over this component.
+However, within the context of practice itself there are other opportunities for choice that participants may explore, independent of their assigned group.
+Past self-controlled learning experiments have used a variety of motor tasks, including but not limited to basketball free throws (e.g., Aiken, Fairbrother, \& Post, 2012) and bean-bag tossing (e.g., Grand et al., 2015).
+Although participants in a yoked group may not have choice over their feedback schedule (or some other practice variable) while learning such tasks, this does not preclude them from opportunities for choice---and thus autonomy-support---when choosing to try different throwing techniques, speeds, and/or release points.
 Thus, labeling yoked groups as being devoid of choice opportunities may be a misnomer.
-The other consideration relates to the instructions that are provided to participants in the yoked group.
+The other issue relates to the instructions that are provided to participants in a yoked group.
 In the context of feedback\footnote{While feedback is used in this example, this issue surrounding instructions is also relevant to other practice variables commonly used in self-controlled learning experiments.}, these participants are typically informed that during practice they may or may not receive feedback after a given trial (e.g., Chiviacowsky \& Wulf, 2002; Patterson \& Carter, 2010).
-This means that participants in yoked groups are not even aware that they have been denied an opportunity for choice, nor that their feedback schedule was created by another participant who was given choice over when feedback was or was not provided.
-Either of these in isolation, or both simultaneously could contribute to the consistent finding that participants in self-controlled and yoked groups report similar perceived autonomy scores when asked about their opportunities for choices with respect to the motor task (Ste-Marie et al., 2013) or about their practice environment in general (Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020b).
+This means that participants in yoked groups are not even aware that they have been denied an opportunity for choice, or that their feedback schedule was created by another participant who had choice over when feedback was or was not provided.
+These two methodological issues, either in isolation or simultaneously, may have contributed to the consistent finding in past research with self-controlled and yoked participants self-reporting numerically similar perceptions of autonomy when asked about opportunities for choice with respect to the motor task (e.g., Ste-Marie et al., 2013) or about their practice environment in general (e.g., Barros et al., 2019; Carter \& Ste-Marie, 2017b; McKay \& Ste-Marie, 2020a).
 
-\begin{table*}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:table1}Group specific instructions detailing the observation schedule that would be experienced during Acquisition.}
-
-\begin{tabular}{ll}
-\toprule
-  & Acquisition instructions\\
-\midrule
-Self-Controlled & Before each trial, you will be asked whether you wish to watch a modeled demonstration of the task.\\
- & If you choose YES, you will then be asked whether you want to watch the video in real-time or in\\
- & slow-motion.\\
-Traditional Yoked & Before each trial, you may or may not watch a modeled demonstration of the task based on a pre-\\
- & determined schedule. If you observe a model, it might be presented in real-time or in slow-motion\\
- & based on the pre-determined schedule.\\
-Explicit Yoked & Before each trial, you may or may not watch a modeled demonstration of the task based on the\\
- & schedule another participant selected. If you observe a model, it might be presented in real-time or in\\
- & slow-motion based on what that participant selected.\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table*}
-
-Here we investigated the effects of making participants in a yoked group explicitly aware of not only being denied opportunities for choice over their frequency of watching and the playback speed of video demonstrations, but also that the schedule they would experience during practice was created by another participant in the experiment.
-The addition of this novel yoked group allowed us to address one of the previously identified methodological limitations regarding experimental group instructions in past self-controlled research.
-We compared the performance of this explicit yoked group with traditional self-controlled and yoked groups on a speed cup-stacking task in practice and in a delayed retention test.
+Here, we addressed the methodological limitation of past self-controlled research where participants in the yoked group are unaware that a feature of their practice environment was created by another participant in the experiment.
+To this end, participants learned a speed cup-stacking task in either a self-controlled group, a traditional yoked group, or a novel explicitly aware yoked group.
+The self-controlled group has choice over the frequency of watching a video demonstration and the video playback speed (real-time or slow motion).
+Participants in the traditional and explicit yoked groups were matched to a participant in the self-controlled group and experienced the observation schedule selected by this participant.
+The key difference being that participants in the explicit yoked group were told that the observation schedule they would experience during practice was selected by another participant, whereas participants in the traditional yoked group were not aware of this.
+Motor learning was assessed using a delayed retention test.
+We predicted that the self-controlled group would have significantly faster stacking times in retention than the traditional yoked group.
+In other words, we expected to replicate the typical self-controlled learning advantage.
+If the self-controlled learning advantage results from choice being autonomy-supportive as argued in the ``OPTIMAL'' theory (Wulf \& Lewthwaite, 2016), then participants in the self-controlled group should also self-report significantly higher scores for perceptions of autonomy.
+Also based on the view that autonomy-support is the mechanism underlying the typical self-controlled learning advantage (Wulf \& Lewthwaite, 2016), we predicted that the explicit yoked group should have significantly slower stacking times in retention.
+Although we found significantly higher perceptions of autonomy in the self-controlled group, there were no significant group differences in stacking times during retention.
+Overall, these results do not support our predictions and are inconsistent with predictions 2, 3, and 7 in the ``OPTIMAL'' theory of motor learning (Wulf \& Lewthwaite, 2016).
 
@@
 
-One-hundred and fifty participants completed the experiment.
-Sample size was determined by an a priori power calculation based on our smallest comparison of interest.
-An early estimate for the effect of self-controlled over yoked practice was a Hedges' \(g = 0.63\) (McKay et al., 2014) and while planning this experiment this effect was estimated to be \(g = 0.52\) (Z.
+One-hundred and fifty university students participated in the experiment.
+Sample size was determined by an a priori power calculation based on our smallest comparison of interest using GLIMMPSE (\url{https://glimmpse.samplesizeshop.org/}).
+An early estimate for the effect of self-controlled over yoked practice was a Hedges' \emph{g} = 0.63 (McKay, Carter, \& Ste-Marie, 2014) and while planning this experiment this effect was estimated to be \emph{g} = 0.52 (Z.
 Yantha, personal communication, October 2019).
-Based on this effect, a positive correlation of \(r = 0.6\) between retention and pre-test as the covariate, and 80\% power to detect a difference between the self-controlled and traditional yoked groups, the required number of participants was 31 per group.
-Considering the novelty of our Explicit Yoked group, we assumed a smaller effect, \(g = 0.4\), between it and the Traditional Yoked group.
-With the same parameters as above, this resulted in our final sample of 50 participants per group.
+Based on this effect, a positive correlation of \emph{r} = 0.6 between retention and pre-test as the covariate, an alpha of 0.05, and 80\% power to detect a difference between the self-controlled and traditional yoked groups, the required number of participants was 31 per group.
+Considering the novelty of our Explicit Yoked group, we assumed a smaller effect, \emph{g} = 0.4, between it and the Traditional Yoked group.
+Using this effect and the same parameters as above, this resulted in our final sample of 50 participants per group.
 
-Participants completed the experiment in either the Self-Controlled group \((M_{age} = 18.0\), \emph{SD} = 0.34), the Traditional Yoked group \((M_{age} = 19.5\), \emph{SD} = 1.89), or the Explicit Yoked group \((M_{age} = 19.2\), \emph{SD} = 1.55).
+Participants completed the experiment in either the Self-Controlled group \((M_{age}\) = 18.0, \emph{SD} = 0.34; 32 females), the Traditional Yoked group \((M_{age}\) = 19.5, \emph{SD} = 1.89; 28 females), or the Explicit Yoked group \((M_{age}\) = 19.2, \emph{SD} = 1.55; 30 females).
 We collected the Self-Controlled group first as their self-selected observation schedule was required for the yoking procedure for the two other groups.
@@
 Session 2 consisted of a delayed retention test.
-At the start of each phase of the experiment, all participants received phase-specific instructions (see Data and code availability section).
+At the start of each phase of the experiment, all participants received phase-specific instructions \textbackslash hyperref{[}sec:sharing{]}\{(see Data, materials, and code availability section).
 Group specific instructions were provided prior to the acquisition phase (see Table \ref{tab:table1}).
@@
 Participants followed along as the instructions were read aloud by the researcher.
+\medskip
+
+\begin{table}
+
+\caption{\label{tab:table1}Group specific components from the instructions detailing the observation schedule that would be experienced during Acquisition.}
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{33em}}
+\toprule
+  & Acquisition instructions\\
+\midrule
+Self-Controlled & Before each trial, you will be asked whether you wish to watch a modeled demonstration of the task.
+If you choose YES, you will then be asked whether you want to watch the video in real-time or in slow-motion.\\
+\addlinespace
+Traditional Yoked & Before each trial, you may or may not watch a modeled demonstration of the task based on a pre-determined schedule.
+If you observe a model, it might be presented in real-time or in slow-motion based on the pre-determined schedule.\\
+\addlinespace
+Explicit Yoked & Before each trial, you may or may not watch a modeled demonstration of the task based on the schedule another participant selected.
+If you observe a model, it might be presented in real-time or in slow-motion based on what that participant selected.\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 
-To test predictions based on the ``OPTIMAL'' theory regarding the role of motivation, enhanced expectancies, and autonomy-support, participants completed the interest/enjoyment and perceived competence subscales from the Intrinsic Motivation Inventory (McAuley et al., 1989) and a custom scale regarding choice used in previous self-controlled motor learning experiments (Barros et al., 2019; Carter \& Ste-Marie, 2017b).
+To test predictions based on the ``OPTIMAL'' theory regarding the role of motivation, enhanced expectancies, and autonomy-support, participants completed the interest/enjoyment and perceived competence subscales from the Intrinsic Motivation Inventory (McAuley, Duncan, \& Tammen, 1989) and a custom scale regarding choice used in previous self-controlled motor learning experiments (Barros et al., 2019; Carter \& Ste-Marie, 2017b).
 The order of questions from each scale were randomized and each question was rated using a 7-point Likert scale.
 Participants answered these questions after the pre-test, after trials five and 25 of acquisition, and before the delayed retention test.
+The values for Cronbach's alpha for each questionnaire at each time point are reported in Table \ref{tab:table2}.
 
 A custom LabVIEW (National Instruments Inc.) program was created that controlled the presentation of all instructions, the video demonstrations, the timing of the experimental protocol, and recorded and stored the data for later analysis.
+
+\begin{table}
+
+\caption{\label{tab:table2}Cronbach's alpha for each questionnaire at each time point.}
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{7em}}
+\toprule
+  & After pre-test & After trial 5 & After trial 25 & Before retention\\
+\midrule
+Perceived autonomy & 0.62 & 0.79 & 0.79 & 0.84\\
+\addlinespace
+Perceived competence & 0.90 & 0.92 & 0.94 & 0.92\\
+\addlinespace
+Intrinsic motivation & 0.86 & 0.90 & 0.92 & 0.92\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 Our primary outcome measure was stacking time (i.e., response time) in seconds.
-Trials recorded as errors \((76/5250 = 1.45\%)\) during data collection were manually removed prior to data analysis.
+Trials recorded as errors (76/5250 = 1.45\%) during data collection were manually removed prior to data analysis.
 For each participant, pre-test and delayed retention trials were aggregated into one block of five trials and acquisition was aggregated into five blocks of five trials.
@@
 Post hoc comparisons were conducted using Holm's correction.
-A Cook's distance of \(\geq 1\) was used to identify any influential cases.
+A Cook's distance of \(\geq\) 1 was used to identify any influential cases and none were identified.
+Statistical tests are described below.
 
@@
 
-To test whether delayed retention (Figure \ref{fig:fig1}C) was differentially impacted by the experimental group (i.e., Self-Controlled, Traditional Yoked, Explicit Yoked) experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test.
+To test whether delayed retention (Figure \ref{fig:fig1}C) was differentially impacted by the experimental group experienced during acquisition, we performed a one-way ANCOVA controlling for pre-test.
 As can be seen, the Self-Controlled group \((M = 9.99\), \(95\%CI = [9.68,10.31])\), the Traditional Yoked group \((M = 10.18\), \(95\%CI = [9.86,10.50])\), and the Explicit Yoked group \((M = 10.12\), \(95\%CI = [9.81,10.44])\) all had similar stacking times in retention (means are shown as the adjusted means controlling for pre-test).
 The effect of Group was not significant, \(F(2,146) = .335\), \(p = .716\), \(\eta^2 = .002\).
-
-\begin{figure*}
-
-{\centering \includegraphics[width=1\linewidth,height=1\textheight]{../../figs/fig1}
-
-}
-
-\caption{Physical performance data of the experiment.
-The Self-Controlled group is shown in red with solid lines and/or circles, the Traditional Yoked group is shown in blue with dotted and/or triangles, and the Explicit Yoked group is shown in orange with dashed and/or squares.
-\textbf{A}.
-Trial-by-trial stacking time (s) data averaged across participants within each group (shaded area represents standard error).
-Splits between line segments denote the end of one phase and the start of the next.
-Pre-test (Trials 1 to 5) and Acquisition (Trials 6 to 30) occurred on Day 1 and Retention (Trials 31 to 35) occurred on Day 2, approximately 24-hours later.
-\textbf{B}.
-Mean stacking time (s) for each group was computed by averaging the data from \textbf{A} into 7 blocks of trials.
-Error bars represent 95\% confidence intervals.
-Splits between line segments denote the end of one phase and the start of the next.
-\textbf{C}.
-Mean stacking time (s) adjusted for pre-test for each group.
-Error bars represent 95\% confidence intervals.
-\textbf{D}.
-Scatterplot showing the relationship between each participant's mean stacking time (s) in pre-test and retention.}\label{fig:fig1}
-\end{figure*}
-
-\begin{table*}[t]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:table2}The mean frequencies for each acquisition block of requesting to watch the video demonstration and choosing the regular viewing speed.}
-
-\begin{tabular}{llllll}
-\toprule
-  & Block 1 & Block 2 & Block 3 & Block 4 & Block 5\\
-\midrule
-Model viewing frequency & 32.6\% & 16.9\% & 12.0\% & 12.9\% & 9.3\%\\
- &  &  &  &  & \\
-Regular speed frequency & 33.8\% & 38.1\% & 50.0\% & 34.4\% & 30.4\%\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table*}
 
@@
 
+\begin{figure}
+
+{\centering \includegraphics[height=0.51\textheight]{../../figs/fig1}
+
+}
+
+\caption{\textbf{Physical performance data of the experiment.} The Self-Controlled group is shown in red with solid lines and/or circles, the Traditional Yoked group is shown in blue with dotted and/or triangles, and the Explicit Yoked group is shown in orange with dashed and/or squares.
+\textbf{(A).} Trial-by-trial stacking time (s) data averaged across participants within each group (shaded area represents standard error).
+Splits between line segments denote the end of one phase and the start of the next.
+Pre-test (Trials 1 to 5) and Acquisition (Trials 6 to 30) occurred on Day 1 and Retention (Trials 31 to 35) occurred on Day 2, approximately 24-hours later.
+\textbf{(B).} Mean stacking time (s) for each group was computed by averaging the data from A into 7 blocks of trials.
+Error bars represent 95\% confidence intervals.
+Splits between line segments denote the end of one phase and the start of the next.
+\textbf{(C).} Mean stacking time (s) adjusted for pre-test for each group.
+Error bars represent 95\% confidence intervals.
+\textbf{(D).} Scatterplot showing the relationship between each participant's mean stacking time (s) in pre-test and retention.}\label{fig:fig1}
+\end{figure}
+
+\newpage
+
+\begin{table}
+
+\caption{\label{tab:table3}The mean frequencies for each Acquisition block of requesting to watch the video demonstration and of those requests, the mean frequency of choosing the regular viewing speed.}
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{13em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}l}
+\toprule
+  & Block 1 & Block 2 & Block 3 & Block 4 & Block 5\\
+\midrule
+Model viewing frequency & 32.6\% & 16.9\% & 12.0\%\% & 12.9\% & 9.3\%\\
+\addlinespace
+Regular speed frequency & 33.8\% & 38.1\% & 50.0\% & 34.4\% & 30.4\%\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \hypertarget{acquisition-phase}{%
@@
 
+\begin{figure}
+
+{\centering \includegraphics[height=0.72\textheight]{../../figs/fig2}
+
+}
+
+\caption{\textbf{Questionnaire data.} Groups means for perceived autonomy \textbf{(A)}, intrinsic motivation \textbf{(B)}, and perceived competence \textbf{(C)} after pre-test, trial 5, and trial 25 on Day 1, and before retention on Day 2.
+The Self-Controlled group is shown in red circles, the Traditional Yoked group is shown in blue triangles, and the Explicit Yoked group is shown in orange squares.
+Dots represent individual participants in each group.
+Scores could range from 1 (Strongly disagree) to 7 (Strongly agree).
+Error bars represent 95\% confidence intervals.}\label{fig:fig2}
+\end{figure}
+
 \hypertarget{perceived-competence}{%
@@
 
-To further probe our null effects (Harms \& Lakens, 2018) related to our main predictions, two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times were carried out using the two one-sided test procedure (Lakens et al., 2018; Schuirmann, 1987).
-To establish our smallest effect size of interest (Lakens, 2021) we calculated the effect size our design had 33\% power to detect (Simonsohn, 2015), which was \(d_{s} = .31\).
+Given our pre-registered analysis resulted in a non-significant finding, we performed two equivalence tests (Self-Controlled versus Traditional Yoked and Traditional Yoked versus Explicit Yoked) on pre-test adjusted retention stacking times using the two one-sided test procedure (Lakens, Scheel, \& Isager, 2018; Schuirmann, 1987).
+Equivalence tests are a statistical tool that researchers can use to support the absence of a meaningful effect and avoid incorrectly concluded no effect exists based on a non-significant finding (Harms \& Lakens, 2018).
+To establish our smallest effect size of interest (Lakens, Pahlke, \& Wassmer, 2021) we calculated the effect size our design had 33\% power to detect (Simonsohn, 2015), which was \(d_{s} = .31\).
 The Self-Controlled and Traditional Yoked groups were not statistically different, \(t(97.99) = -0.830\), \(p = 0.409\), and not statistically equivalent, \(t(97.99) = 0.720\), \(p = 0.237\), given equivalence bounds of \(-.355\) and \(.355\) (on a raw scale).
 Similarly, the Traditional Yoked and Explicit Yoked groups were not statistically different, \(t(97.99) = 0.262\), \(p = 0.794\), and not statistically equivalent, \(t(97.99) = -1.288\), \(p = 0.100\), given equivalence bounds of \(-.355\) and \(.355\) (on a raw scale).
-
-\begin{figure*}
-
-{\centering \includegraphics[width=0.85\linewidth,height=0.85\textheight]{../../figs/fig2}
-
-}
-
-\caption{Questionnaire data.
-Groups means for \textbf{A} perceived autonomy, \textbf{B} intrinsic motivation, and \textbf{C} perceived competence after pre-test, trial 5, and trial 25 on Day 1, and before retention on Day 2.
-The Self-Controlled group is shown in red circles, the Traditional Yoked group is shown in blue triangles, and the Explicit Yoked group is shown in orange squares.
-Dots represent individual participants in each group.
-Scores could range from 1 (Strongly disagree) to 7 (Strongly agree).
-Error bars represent 95\% confidence intervals.}\label{fig:fig2}
-\end{figure*}
 
@@
 The delayed retention results in the present experiment not only are inconsistent with numerous past experiments reporting a self-controlled motor learning benefit (for a review see Ste-Marie et al., 2019), but also the general consensus that the self-controlled learning advantage is a robust effect (Wulf \& Lewthwaite, 2016).
-Of late, however, there has been an increase in the number of papers reporting a failure to detect the so-called self-controlled learning advantage (e.g., Barros et al., 2019; Grand et al., 2017; McKay \& Ste-Marie, 2020a, 2020b).
+Of late, however, there has been an increase in the number of papers reporting a failure to detect the so-called self-controlled learning advantage (e.g., Barros et al., 2019; Grand, Daou, Lohse, \& Miller, 2017; McKay \& Ste-Marie, 2020b, 2020a).
 This recent lack of support may arise from the self-controlled learning advantage being a much smaller effect than originally estimated (\(g = 0.63\) by McKay et al.~2014).
-A more recent estimate of this effect from a meta-analysis using a weight-function model was \(g = .11, \,95\% CI = [.047, .18]\) (McKay et al., 2021).
+A more recent estimate of this effect from a meta-analysis using a weight-function model was \(g = .11, \,95\% CI = [.047, .18]\) (McKay, Yantha, Hussien, Carter, \& Ste-Marie, Accepted).
 This estimate was further reduced to \(g = .054\) after controlling for publication bias using the precision-effect estimate with standard error (PEESE) method.
@@
 Furthermore, we did not find evidence than an autonomy-supportive manipulation had any direct causal effect on learning and we also failed to replicate the typical self-controlled learning advantage.
-It is worth noting that in some situations autonomy-support in and of itself might be a desired affective outcome (Ste-Marie et al., 2020).
-In such circumstance, providing learners with choice opportunities may be a useful motivationally-protective outcome.
+It is worth noting that in some situations autonomy-support in and of itself might be a desired affective outcome (Ste-Marie, Lelievre, \& Germain, 2020).
+In such circumstances, providing learners with choice opportunities may be a useful motivationally-protective outcome.
 However, such a tool should be used judiciously as it is typically motor outcomes in the form of relatively permanent performance changes that is the true goal of any motor learning intervention (Ste-Marie et al., 2020).
-Ultimately, our results add to a growing body of evidence that questions whether autonomy-supportive manipulations directly affect learning.
-One explanation for this lack of replicability is that the \emph{``true''} effect of such manipulations are much smaller than previously estimated (McKay et al., 2021).
-Given the resources required (in terms of sample size) to reliably detect the tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either studying practice conditions that have much bigger effects or devising ways to reduce variability and increase power through clever experimental design (McClelland, 2000).
+Ultimately, our results add to a growing body of evidence that questions whether autonomy-supportive manipulations directly affect motor learning.
+One explanation for this lack of replicability is that the \emph{``true''} effect of such manipulations are much smaller than previously estimated (McKay et al., Accepted).
+Given the resources required (in terms of sample size) to reliably detect these tiny effects, we encourage motor learning scientists to invest their limited resources carefully---either by adopting the use of sequential analyses (Lakens, 2014; Lakens et al., 2021; Wald, 1945) and/or multi-lab collaborations (Boland, Karczewski, \& Tatonetti, 2017) or studying practice conditions that likely have much bigger effects on motor learning.
+
+\vfill
+
+\hypertarget{contributions-using-credit-httpscasrai.orgcredit}{%
+\section{\texorpdfstring{Contributions using CrediT (\url{https://casrai.org/credit/})}{Contributions using CrediT (https://casrai.org/credit/)}}\label{contributions-using-credit-httpscasrai.orgcredit}}
+
+Conceptualization (LSG, KRL, MJC); Data curation (LSG, KRL, MJC); Formal analysis (LSG, KRL, MJC); Funding acquisition (MJC); Investigation - Performed Experiment (LSG, AW, NB, AP, OL); Methodology (LSG, KRL, MJC); Project administration (LSG, MJC); Resources (MJC); Software - Task Programming (LSG, MJC); Supervision (MJC); Validation (LSG, KRL, MJC); Visualization (LSG, MJC); Writing - Original Draft Preparation (LSG, AW, NB, KRL, MJC); Writing - Review \& Editing (LSG, AW, NB, AP, OL, KRL, MJC)
+
+\hypertarget{data-materials-and-code-availability}{%
+\section{Data, materials, and code availability}\label{data-materials-and-code-availability}}
+
+\label{sec:sharing}
+All material, data, and scripts to reproduce our analyses and figures can be accessed here: \url{https://github.com/cartermaclab/expt_explicit-yoked}.
+The preregistration can be accessed here: \url{https://aspredicted.org/ze8cj.pdf}.
+
+\hypertarget{r-packages-used-in-this-project}{%
+\section{R packages used in this project}\label{r-packages-used-in-this-project}}
+
+R (Version 4.0.4; R Core Team, 2021) and the R-packages \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{jmv} (Version 2.0; Selker, Love, \& Dropmann, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{pwr} (Version 1.3.0; Champely, 2020), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), and \emph{TOSTER} (Version 0.4.0; Lakens, 2017).
 
@@
 
-This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC). LSG was also supported by an NSERC PGS-D scholarship.
-
-\hypertarget{data-and-code-availability}{%
-\section{Data and code availability}\label{data-and-code-availability}}
-
-All material, data, and scripts to reproduce our analyses and figures can be accessed here: \url{https://github.com/cartermaclab/expt_explicit-yoked}.
-
-\hypertarget{r-packages-used-in-this-project}{%
-\section{R packages used in this project}\label{r-packages-used-in-this-project}}
-
-R {[}Version 4.0.5; R Core Team (2021){]} and the R-packages \emph{cowplot} {[}Version 1.1.1; Wilke (2020){]}, \emph{jmv} {[}Version 1.2.23; Selker et al.
-(2020){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{pwr} {[}Version 1.3.0; Champely (2020){]}, \emph{tidyverse} {[}Version 1.3.1; Wickham et al.
-(2019){]}, and \emph{TOSTER} {[}Version 0.3.4; Lakens (2017){]}.
+This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC).
+LSG was supported by an NSERC Postgraduate Scholarship.
+AW and AP were supported by NSERC Undergraduate Student Research Awards.
 
@@
 
-\leavevmode\hypertarget{ref-button2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-boland2017}{}}%
+Boland, M.
+R., Karczewski, K.
+J., \& Tatonetti, N.
+P.
+(2017).
+Ten simple rules to enable multi-site collaborations through data sharing.
+\emph{PLOS Computational Biology}, \emph{13}, 1--12.
+\url{https://doi.org/10.1371/journal.pcbi.1005278}
+
+\leavevmode\vadjust pre{\hypertarget{ref-button2013}{}}%
 Button, K.
@@
 
-\leavevmode\hypertarget{ref-lakens2021}{}%
-Lakens, D. (2021). \emph{Sample size justification}. \url{https://doi.org/10.31234/osf.io/9d3yf}
+\leavevmode\vadjust pre{\hypertarget{ref-lakens2014}{}}%
+Lakens, D. (2014). Performing high-powered studies efficiently with sequential analyses. \emph{European Journal of Social Psychology}, \emph{44}(7), 701--710. \url{https://doi.org/10.1002/ejsp.2023}
 
-\leavevmode\hypertarget{ref-R-TOSTER}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-TOSTER}{}}%
 Lakens, D.
@@
 
-\leavevmode\hypertarget{ref-lakens2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lakens2021}{}}%
+Lakens, D., Pahlke, F., \& Wassmer, G. (2021). Group sequential designs: A tutorial. \emph{Psyarxiv}. \url{https://doi.org/10.31234/osf.io/x4azm}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lakens2018}{}}%
 Lakens, D., Scheel, A.
@@
 
-\leavevmode\hypertarget{ref-mcclelland2000}{}%
-McClelland, G.
-H.
-(2000).
-Increasing statistical power without increasing sample size.
-\emph{American Psychologist}, \emph{55}(8), 963--964.
-https://doi.org/\url{https://psycnet.apa.org/doi/10.1037/0003-066X.55.8.963}
+\leavevmode\vadjust pre{\hypertarget{ref-mckay2014}{}}%
+McKay, B., Carter, M. J., \& Ste-Marie, D. M. (2014). Self-controlled learning: A meta-analysis. \emph{Journal of sport \& exercise psychology,} \emph{36}, S43.
 
-\leavevmode\hypertarget{ref-mckay2014}{}%
-McKay, B., Carter, M. J., \& Ste-Marie, D. M. (2014). Self-controlledlearning: A meta-analysis. \emph{Journal of Sport \& Exercise Psychology,} \emph{36}, S43.
-
-\leavevmode\hypertarget{ref-mckay2020a}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mckay2020b}{}}%
 McKay, B., \& Ste-Marie, D.
@@
 M.
-(2021).
-\emph{Meta-analytic findings in the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value}.
+(Accepted).
+Meta-analytic findings in the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value.
+\emph{Meta-Psychology}.
 \url{https://doi.org/10.31234/osf.io/8d3nb}
 
-\leavevmode\hypertarget{ref-patterson2010}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-patterson2010}{}}%
 Patterson, J.
@@
 
-\leavevmode\hypertarget{ref-R-tidyverse}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-wald1945}{}}%
+Wald, A. (1945). Sequential tests of statistical hypotheses. \emph{The Annals of Mathematical Statistics}, \emph{16}(2), 117--186. \url{https://doi.org/10.1214/aoms/1177731118}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
 Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T.
-L., Miller, E., Bache, S.
-M., Müller, K., Ooms, J., Robinson, D., Seidel, D.
-P., Spinu, V., \ldots{} Yutani, H.
+D., François, R., \ldots{} Yutani, H.
 (2019).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
+Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
+
 \end{CSLReferences}

### 2021-12-28 docs/accepted/accepted_manuscript.tex
init

--- 2021-12-28 docs/preprint/preprint.tex
@@
   english,
-  doc, donotrepeattitle,floatsintext]{apa7}
-\title{Increased perceptions of autonomy through choice over one's observation schedule fail to enhance motor skill retention}
+  man, donotrepeattitle,floatsintext]{apa7}
+\title{Increased perceptions of autonomy through choice fail to enhance motor skill retention}
 \author{Laura St.~Germain\textsuperscript{1}, Allison Williams\textsuperscript{1}, Noura Balbaa\textsuperscript{1}, Andrew Poskus\textsuperscript{1}, Olena Leshchyshen\textsuperscript{1}, Keith R.
@@
 \hypersetup{
-  pdftitle={Increased perceptions of autonomy through choice over one's observation schedule fail to enhance motor skill retention},
+  pdftitle={Increased perceptions of autonomy through choice fail to enhance motor skill retention},
   pdfauthor={Laura St.~Germain1, Allison Williams1, Noura Balbaa1, Andrew Poskus1, Olena Leshchyshen1, Keith R. Lohse2, \& Michael J. Carter1},
@@
 {}{\PatchFailed}
-\keywords{Motor learning; Pre-registered; Self-controlled; Observation}
+\keywords{Motor learning; Pre-registered; Self-controlled; Observation\newline\indent Word count: 4585}
+\usepackage{lineno}
+
+\linenumbers
 \usepackage{csquotes}
 \usepackage{pdflscape}
+\pagewiselinenumbers
 \raggedbottom
@@
 
-PsyArXiv preprint: \url{https://doi.org/10.31234/osf.io/s34fg} \vspace{1em}
+PsyArXiv preprint: \url{https://doi.org/10.31234/osf.io/s34fg}
 
@@
 These findings add to a growing body of research that questions a causal role of autonomy-support on motor learning, and the robustness of the so-called self-controlled learning advantage.
+
+\noindent \textbf{\emph{Public Significance Statement}}\\
+The present study suggests that although university-aged students may experience a boost in feelings of autonomy when given choice over features of their learning environment, this boost may not enhance learning of a new motor skill.
+Our results also highlight the need for higher powered and pre-registered motor learning experiments if coaches and practictioners are to be provided with reliable recommendations for training and rehabilitation protocols.
 }
@@
 \maketitle
-
-\vspace{-0.5em}
-
-\noindent
-
-\begin{center}
-\textcolor{blue}{Accepted for publication in \emph{Journal of Experimental Psychology: Human Perception \& Performance}}
-\end{center}
-
-\vspace{0.5em}
 
@@
 \caption{\label{tab:table1}Group specific components from the instructions detailing the observation schedule that would be experienced during Acquisition.}
-\fontsize{10}{12}\selectfont
+\fontsize{11}{13}\selectfont
 \begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{33em}}
@@
 \caption{\label{tab:table2}Cronbach's alpha for each questionnaire at each time point.}
-\fontsize{10}{12}\selectfont
+\fontsize{11}{13}\selectfont
 \begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{7em}}
@@
 
-\hypertarget{non-pre-registered-analyses}{%
-\subsection{Non pre-registered analyses}\label{non-pre-registered-analyses}}
-
-\hypertarget{traditional-self-controlled-learning-advantage}{%
-\subsubsection{Traditional self-controlled learning advantage}\label{traditional-self-controlled-learning-advantage}}
-
-To investigate whether a traditional self-controlled learning advantage existed---that is a comparison between the Self-Controlled and Traditional Yoked groups---we analyzed the non-adjusted retention scores using a Welch's \emph{t}-test.
-The analysis revealed that the Self-Controlled group \((M = 9.77\), \(95\%CI = [9.55,9.99])\) and the Traditional Yoked group \((M = 10.20\), \(95\%CI = [9.92,10.49])\) were not statistically different, \(t(88.10) = 1.45\), \(p = .15\), \(g = .29\).
-
 \begin{figure}
@@
 
-\caption{\textbf{Physical performance data of the experiment.} The Self-Controlled group is shown in red with solid lines and/or circles, the Traditional Yoked group is shown in blue with dotted and/or triangles, and the Explicit Yoked group is shown in orange with dashed and/or squares.
-\textbf{(A).} Trial-by-trial stacking time (s) data averaged across participants within each group (shaded area represents standard error).
+\caption{Physical performance data of the experiment.
+The Self-Controlled group is shown in red with solid lines and/or circles, the Traditional Yoked group is shown in blue with dotted and/or triangles, and the Explicit Yoked group is shown in orange with dashed and/or squares.
+\textbf{A}.
+Trial-by-trial stacking time (s) data averaged across participants within each group (shaded area represents standard error).
 Splits between line segments denote the end of one phase and the start of the next.
 Pre-test (Trials 1 to 5) and Acquisition (Trials 6 to 30) occurred on Day 1 and Retention (Trials 31 to 35) occurred on Day 2, approximately 24-hours later.
-\textbf{(B).} Mean stacking time (s) for each group was computed by averaging the data from A into 7 blocks of trials.
+\textbf{B}.
+Mean stacking time (s) for each group was computed by averaging the data from \textbf{A} into 7 blocks of trials.
 Error bars represent 95\% confidence intervals.
 Splits between line segments denote the end of one phase and the start of the next.
-\textbf{(C).} Mean stacking time (s) adjusted for pre-test for each group.
+\textbf{C}.
+Mean stacking time (s) adjusted for pre-test for each group.
 Error bars represent 95\% confidence intervals.
-\textbf{(D).} Scatterplot showing the relationship between each participant's mean stacking time (s) in pre-test and retention.}\label{fig:fig1}
+\textbf{D}.
+Scatterplot showing the relationship between each participant's mean stacking time (s) in pre-test and retention.}\label{fig:fig1}
 \end{figure}
@@
 \caption{\label{tab:table3}The mean frequencies for each Acquisition block of requesting to watch the video demonstration and of those requests, the mean frequency of choosing the regular viewing speed.}
-\fontsize{10}{12}\selectfont
+\fontsize{11}{13}\selectfont
 \begin{tabular}[t]{>{\raggedright\arraybackslash}p{13em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}l}
@@
 
+\hypertarget{non-pre-registered-analyses}{%
+\subsection{Non pre-registered analyses}\label{non-pre-registered-analyses}}
+
+\hypertarget{traditional-self-controlled-learning-advantage}{%
+\subsubsection{Traditional self-controlled learning advantage}\label{traditional-self-controlled-learning-advantage}}
+
+To investigate whether a traditional self-controlled learning advantage existed---that is a comparison between the Self-Controlled and Traditional Yoked groups---we analyzed the non-adjusted retention scores using a Welch's \emph{t}-test.
+The analysis revealed that the Self-Controlled group \((M = 9.77\), \(95\%CI = [9.55,9.99])\) and the Traditional Yoked group \((M = 10.20\), \(95\%CI = [9.92,10.49])\) were not statistically different, \(t(88.10) = 1.45\), \(p = .15\), \(g = .29\).
+
 \hypertarget{acquisition-phase}{%
@@
 
-\begin{figure}
-
-{\centering \includegraphics[height=0.72\textheight]{../../figs/fig2}
-
-}
-
-\caption{\textbf{Questionnaire data.} Groups means for perceived autonomy \textbf{(A)}, intrinsic motivation \textbf{(B)}, and perceived competence \textbf{(C)} after pre-test, trial 5, and trial 25 on Day 1, and before retention on Day 2.
-The Self-Controlled group is shown in red circles, the Traditional Yoked group is shown in blue triangles, and the Explicit Yoked group is shown in orange squares.
-Dots represent individual participants in each group.
-Scores could range from 1 (Strongly disagree) to 7 (Strongly agree).
-Error bars represent 95\% confidence intervals.}\label{fig:fig2}
-\end{figure}
-
 \hypertarget{perceived-competence}{%
@@
 No significant effect of Group, \(F(2,146) = 2.65\), \(p = .074\), \(\eta^2_{G} = .028\), or Group x Time interaction, \(F(3.50,255.22) = .549\), \(p = .677\), \(\eta^2_{G} = .002\), was found.
+
+\begin{figure}
+
+{\centering \includegraphics[height=0.72\textheight]{../../figs/fig2}
+
+}
+
+\caption{Questionnaire data.
+Groups means for \textbf{A} perceived autonomy, \textbf{B} intrinsic motivation, and \textbf{C} perceived competence after pre-test, trial 5, and trial 25 on Day 1, and before retention on Day 2.
+The Self-Controlled group is shown in red circles, the Traditional Yoked group is shown in blue triangles, and the Explicit Yoked group is shown in orange squares.
+Dots represent individual participants in each group.
+Scores could range from 1 (Strongly disagree) to 7 (Strongly agree).
+Error bars represent 95\% confidence intervals.}\label{fig:fig2}
+\end{figure}
 
@@
 AW and AP were supported by NSERC Undergraduate Student Research Awards.
-
-\newpage
 

### 2021-12-28 docs/accepted/accepted_manuscript.Rmd
init

--- 2021-12-28 docs/preprint/preprint.Rmd
@@
 ---
-title             : "Increased perceptions of autonomy through choice over one's observation schedule fail to enhance motor skill retention"
+title             : "Increased perceptions of autonomy through choice fail to enhance motor skill retention"
 shorttitle        : "Autonomy-support does not benefit motor learning"
@@
 
-  PsyArXiv preprint: https://doi.org/10.31234/osf.io/s34fg \vspace{1em}
+  PsyArXiv preprint: https://doi.org/10.31234/osf.io/s34fg
 
@@
 
+  \noindent \textbf{\emph{Public Significance Statement}}  
+  The present study suggests that although university-aged students may experience a boost in feelings of autonomy when given choice over features of their learning environment, this boost may not enhance learning of a new motor skill.
+Our results also highlight the need for higher powered and pre-registered motor learning experiments if coaches and practictioners are to be provided with reliable recommendations for training and rehabilitation protocols.
+
 keywords          : "Motor learning; Pre-registered; Self-controlled; Observation"
-#wordcount         : ""
+wordcount         : "4585"
 bibliography      : ["../references.bib", "../r-references.bib"]
@@
 documentclass     : "apa7"
-classoption       : "doc, donotrepeattitle" # man for manuscript & jou for journal
+classoption       : "man, donotrepeattitle" # man for manuscript & jou for journal
 output            : papaja::apa6_pdf
@@
   - \usepackage{pdflscape}
-  # - \pagewiselinenumbers
+  - \pagewiselinenumbers
   - \raggedbottom
@@
 ```
-
-\vspace{-0.5em}
-\noindent
-\begin{center}
-\textcolor{blue}{Accepted for publication in \emph{Journal of Experimental Psychology: Human Perception \& Performance}}
-\end{center}
-
-\vspace{0.5em}
 
@@
   kable_styling(position = "left",
-                font_size = 10) %>% 
+                font_size = 11) %>% 
   column_spec(1, width = "8em") %>% 
@@
     kable_styling(position = "left",
-                  font_size = 10) %>% 
+                  font_size = 11) %>% 
     column_spec(1, width = "10em") %>% 
@@
 
-## Non pre-registered analyses
-
-### Traditional self-controlled learning advantage
-
-To investigate whether a traditional self-controlled learning advantage existed---that is a comparison between the Self-Controlled and Traditional Yoked groups---we analyzed the non-adjusted retention scores using a Welch's *t*-test.
-The analysis revealed that the Self-Controlled group $(M = 9.77$, $95\%CI = [9.55,9.99])$ and the Traditional Yoked group $(M = 10.20$, $95\%CI = [9.92,10.49])$ were not statistically different, $t(88.10) = 1.45$, $p = .15$, $g = .29$.
-
-(ref:fig1-caption) **Physical performance data of the experiment.** The Self-Controlled group is shown in red with solid lines and/or circles, the Traditional Yoked group is shown in blue with dotted and/or triangles, and the Explicit Yoked group is shown in orange with dashed and/or squares.
-**(A).** Trial-by-trial stacking time (s) data averaged across participants within each group (shaded area represents standard error).
+(ref:fig1-caption) Physical performance data of the experiment.
+The Self-Controlled group is shown in red with solid lines and/or circles, the Traditional Yoked group is shown in blue with dotted and/or triangles, and the Explicit Yoked group is shown in orange with dashed and/or squares.
+**A**.
+Trial-by-trial stacking time (s) data averaged across participants within each group (shaded area represents standard error).
 Splits between line segments denote the end of one phase and the start of the next.
 Pre-test (Trials 1 to 5) and Acquisition (Trials 6 to 30) occurred on Day 1 and Retention (Trials 31 to 35) occurred on Day 2, approximately 24-hours later.
-**(B).** Mean stacking time (s) for each group was computed by averaging the data from A into 7 blocks of trials.
+**B**.
+Mean stacking time (s) for each group was computed by averaging the data from **A** into 7 blocks of trials.
 Error bars represent 95% confidence intervals.
 Splits between line segments denote the end of one phase and the start of the next.
-**(C).** Mean stacking time (s) adjusted for pre-test for each group.
+**C**.
+Mean stacking time (s) adjusted for pre-test for each group.
 Error bars represent 95% confidence intervals.
-**(D).** Scatterplot showing the relationship between each participant's mean stacking time (s) in pre-test and retention.
+**D**.
+Scatterplot showing the relationship between each participant's mean stacking time (s) in pre-test and retention.
 
@@
     kable_styling(position = "left",
-                  font_size = 10) %>% 
+                  font_size = 11) %>% 
     column_spec(1, width = "13em") %>% 
@@
 ```
+
+## Non pre-registered analyses
+
+### Traditional self-controlled learning advantage
+
+To investigate whether a traditional self-controlled learning advantage existed---that is a comparison between the Self-Controlled and Traditional Yoked groups---we analyzed the non-adjusted retention scores using a Welch's *t*-test.
+The analysis revealed that the Self-Controlled group $(M = 9.77$, $95\%CI = [9.55,9.99])$ and the Traditional Yoked group $(M = 10.20$, $95\%CI = [9.92,10.49])$ were not statistically different, $t(88.10) = 1.45$, $p = .15$, $g = .29$.
 
@@
 
-(ref:fig2-caption) **Questionnaire data.** Groups means for perceived autonomy **(A)**, intrinsic motivation **(B)**, and perceived competence **(C)** after pre-test, trial 5, and trial 25 on Day 1, and before retention on Day 2.
+### Perceived competence
+
+The scores from the perceived competence subscale at each time point are displayed in Figure \@ref(fig:fig2)C.
+As can be seen, perceived competence scores showed a modest increase over time followed by a slight decrease before the delayed retention test.
+A 3 Group x 3 Time ANCOVA controlling for pre-test showed an effect of Time, $F(1.75,255.22) = 10.60$, $p < .001$, $\eta^2_{G} = .015$.
+Post hoc tests on adjusted means revealed that scores were rated as significantly higher at the end of acquisition $(M = 3.98$, $95\%CI = [3.67,3.89])$ and before retention $(M = 3.78$, $95\%CI = [3.67,3.89])$ compared to after trial 5 $(M = 3.60$, $95\%CI = [3.49,3.71])$.
+However, perceived competence was significantly lower before retention compared to the end of acquisition.
+No significant effect of Group, $F(2,146) = 2.65$, $p = .074$, $\eta^2_{G} = .028$, or Group x Time interaction, $F(3.50,255.22) = .549$, $p = .677$, $\eta^2_{G} = .002$, was found.
+
+(ref:fig2-caption) Questionnaire data.
+Groups means for **A** perceived autonomy, **B** intrinsic motivation, and **C** perceived competence after pre-test, trial 5, and trial 25 on Day 1, and before retention on Day 2.
 The Self-Controlled group is shown in red circles, the Traditional Yoked group is shown in blue triangles, and the Explicit Yoked group is shown in orange squares.
@@
 ```
-
-### Perceived competence
-
-The scores from the perceived competence subscale at each time point are displayed in Figure \@ref(fig:fig2)C.
-As can be seen, perceived competence scores showed a modest increase over time followed by a slight decrease before the delayed retention test.
-A 3 Group x 3 Time ANCOVA controlling for pre-test showed an effect of Time, $F(1.75,255.22) = 10.60$, $p < .001$, $\eta^2_{G} = .015$.
-Post hoc tests on adjusted means revealed that scores were rated as significantly higher at the end of acquisition $(M = 3.98$, $95\%CI = [3.67,3.89])$ and before retention $(M = 3.78$, $95\%CI = [3.67,3.89])$ compared to after trial 5 $(M = 3.60$, $95\%CI = [3.49,3.71])$.
-However, perceived competence was significantly lower before retention compared to the end of acquisition.
-No significant effect of Group, $F(2,146) = 2.65$, $p = .074$, $\eta^2_{G} = .028$, or Group x Time interaction, $F(3.50,255.22) = .549$, $p = .677$, $\eta^2_{G} = .002$, was found.
 
@@
 
-\newpage
-
 # References
